### 2022-09-28 article_system.tex
update

% Ltex language=en
% \documentclass[12pt, 1p, review, number]{elsarticle}
\documentclass[3p,twocolumn,preprint]{elsarticle}
%\documentclass[10pt,a4paper,3p,twocolumn]{elsarticle}
% \documentclass[5p,preprint,twocolumn]{elsarticle}
%----------------------------------------------------------------------
%                     Loading of packages
%----------------------------------------------------------------------

% for cutting words
\usepackage[utf8]{inputenc}
% a font close to that chosen by Elsevier
\usepackage[bitstream-charter]{mathdesign}
\usepackage{mathtools, cuted}
% for accentuated characters
%\usepackage[T1]{fontenc}
\geometry{top=2cm,left=1.5cm,bottom=2cm,right=1.5cm}
\usepackage{multicol}
% For treating ps:
\usepackage{psfrag}
% For subfigures
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{placeins}
% For tables
\usepackage{array}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{tabulary}
\usepackage{etoolbox}
% For citations
\usepackage[numbers]{natbib}
%\biboptions{longnamesfirst,angle,semicolon}
%\citetstyle{nature}
% For color
\usepackage{color}
\usepackage{xcolor}
% For spacing
\usepackage{setspace}
%\doublespacing
\singlespacing
%\onehalfspacing
% For maths
\usepackage{amsmath, amsfonts}
\usepackage[squaren,ashgrey]{SIunits}
% For Line numbering
\usepackage[pagewise,modulo]{lineno}
%\linenumbers
% For special characters
\usepackage{pifont}
%
\usepackage[pagebackref,colorlinks=True]{hyperref}
\usepackage{wasysym}
\usepackage{color}
\usepackage{cleveref}
\crefformat{figure}{(Fig.~#2#1#3)}
\usepackage{hyperref}
\usepackage[hyperpageref]{backref}
\usepackage{lipsum}
\usepackage{booktabs} % To thicken table lines
% \usepackage{widetext}
\usepackage{float}
\usepackage{empheq}

%----------------------------------------------------------------------
%                     Commands
%----------------------------------------------------------------------
\renewcommand*{\overrightarrow}[1]{\vbox{\halign{##\cr \tiny\rightarrowfill\cr\noalign{\nointerlineskip\vskip1pt}$#1\mskip2mu$\cr}}}
%% Degree character
\DeclareTextSymbol{\degr}{T1}{6}
\newcommand{\degre}[0]{\degr C}
\DeclareUnicodeCharacter{2212}{-}
% MPam^0.5 character
\newcommand{\mpa}[0]{\mbox{MPa}\sqrt{\mbox{m}}}
%mettre de nouilles sous les tenseurs
\newcommand{\ve}[1]{{\underline{#1}}}
\def\ten#1{\oalign{$#1$\crcr\hidewidth$\scriptscriptstyle\sim$\hidewidth}} 
% derivee seconde
\newcommand{\fda}[2]{\displaystyle \frac{\partial\,{#1}}{\partial\, {#2}}}
% et al. for citations
\newcommand{\etal}[0]{{\em et al.}}
\renewcommand*\contentsname{\large{Table of contents}}
\def \hfillx {\hspace*{ -\linewidth} \hfill} % remplir espacement horizontal entre deux sous-figures de façon à remplir toute la largeur du texte.
%----------------------------------------------------------------------
%                     Colors
%----------------------------------------------------------------------
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
%----------------------------------------------------------------------
%                     Pre-Document
%----------------------------------------------------------------------
\journal{Applied Energy}
%----------------------------------------------------------------------
%                     Document
%----------------------------------------------------------------------
\begin{document}

\tableofcontents

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Ear canal dynamic motion piezoelectric energy harvester using a bistable oscillator cycled by coupled hydraulic switches made of collapsed flexible tubes.}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\address[symme]{Laboratoire SYMME - Université Savoie Mont Blanc, 7 Chemin de Bellevue, 74940, Annecy}
\address[critias]{Laboratoire Critias - École de Technologie Supérieure, 1100 Rue Notre-Dame Ouest, Montréal, QC, H3C 1K3}

\author[symme]{Tigran AVETISSIAN}
\author[symme]{Fabien FORMOSA}
\author[symme]{Adrien BADEL}

\author[critias]{Michel DEMUYNCK}
\author[critias]{Aidin DELNAVAZ}
\author[critias]{Jérémy VOIX}

\begin{abstract}
%% Text of abstract
\end{abstract}

\begin{keyword}
%% Keywords
\end{keyword}

\end{frontmatter}

%\linenumbers

%% main text
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{INTRODUCTION}
\label{INTRODUCTION} % Ltex language=en
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress on the energy consumption of mobile devices around the human body. Energy harvesting methods have also been studied on purpose, in order to complement their power supply and enhance the autonomy of the batteries. In-ear devices such as hearing aids and cochlear implants are powered by disposable fuel cells or rechargeable batteries. The energy consumption of the best integrated devices in the literature converges around $17$J for a 10 hours daily use \cite{Scherer2019,Yip2015,Kulah2022}. Woodruff \emph{et al.} showed that patients using hearing aids sometimes struggle to change and select batteries for their devices \cite{Woodruff2021}. Another statistical study revealed that the majority of hearing aid and cochlear implants users prefer disposable batteries for the long autonomy, but would have liked rechargeable solutions if the battery cycle was sufficient to complete the day \cite{PracticesAudiology2016}. Also, the long term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable fuels. These arguments motivate the development of energy harvesting systems to enhance the autonomy of the batteries in order to prevent the premature discharge of in-ear devices.\\
The common sources are ambient such as solar or wind energy but their availability in the low size environment of the application context makes them not suitable for exploitation.
The activities of the human body generate a considerable amount of energy of different natures. Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, the kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, the body heat thermal energy \cite{Kim2014}, the strain energy from the skin deformation \cite{Jin2021} could be harvested for in-ear applications. The most relevant energy source for cochlear implants or hearing aids is the ear canal mechanical deformation as it is directly located in the area of the application. Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes de ear canal geometry during mastication. The figure \ref{fig:TMJ_on_earcanal} schematizes the mechanical interaction between the temporomandibular joint and the ear canal when the jaw is opened and when it is closed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={21cm 0cm 0cm 11.2cm},clip, width=0.9\linewidth]{figures/TMJ_on_earcanal.pdf}
	\caption{Mechanical interaction between the temporomandibular joint and the ear canal during jaw movements \cite{Delnavaz2012}}
	\label{fig:TMJ_on_earcanal}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Carioli \emph{et al.} used a personalized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016} (fig. \ref{fig:molding}). These two mechanical deformations represent an available energy source that can be exploited. This study first quantified the flexion energy amount to $5$mJ per mastication with a standard deviation of $4.9$mJ. The radial compression energy was also estimated to $1.3$mJ with $1.5$mJ of standard deviation. Besides this work, the literature exposes two technological solutions adapted to the extraction of the mechanical deformation energy in the ear canal. \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={6cm 0cm 0cm 10cm},clip, width=0.6\linewidth]{figures/molding.pdf}
	\caption{(a) Earcanal in two extreme positions showing a global bending movement of the earcanal (b) Earcanal sectional view in two extreme positions showing a local compression area of the earcanal. \cite{Carioli2016}}
	\label{fig:molding}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Delnavaz \emph{et al.} first developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013} (fig. \ref{fig:critias_piezo}). The earplug has been melted on the subject in order to maximize the contact surface with the ear canal. The harvester is capable of exploiting both the flexion and the compression energy sources. The experimental prototype presented on figure \ref{fig:critias_piezo} was able to extract $44$µJ from a normal mastication cycle. The soft materials facilitate the bio-integration of the harvester but the PVDF low electromechanical coupling coefficient results in an energy conversion efficiency below $1\%$. A hydroelectromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}. The figure \ref{fig:critias_emag} shows the harvester components and experimental test setup. The energy is extracted by a liquid filled earplug whose internal volume and pressure vary as a result of the radial compression of the ear canal internal walls during the jaw movements. These variations put into motion a moving magnet translating in a water column surrounded by a copper coil. The energy was harvested by electromagnetic induction and experimentally evaluated at 0.2µJ per mastication cycle. The hydraulic energy extraction limits the energy source to the radial compression as the ear canal global flexion does not generate any volume variation in the earplug. The low conversion efficiency ($<1\%$) is a consequence of the use of electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}. However, the hydraulic transmission interface allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume. The table \ref{tab:harvesters_ear} summarizes the existing harvesters that exploit the ear canal mechanical deformation energy. \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={18cm 0cm 0cm 8.7cm},clip, width=\linewidth]{figures/critias_piezo.pdf}
	\caption{Piezoelectric energy harvester. Experimental setup (dimensions are in mm). (a) Flattened PVDF layer. (b) PVDF layer. (c) Prototype of piezo-earpiece. (d) Piezo-earpiece mounted on the headset. (e) Measuring setup. \cite{Delnavaz2013}}  
	\label{fig:critias_piezo}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={18cm 0cm 0cm 8.75cm},clip, width=\linewidth]{figures/critias_emag.pdf}
	\caption{Hydroelectromagnetic energy harvester. (a) Test setup. (b) Energy harvesting module. \cite{Delnavaz2012}} 
	\label{fig:critias_emag}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\resizebox{\linewidth}{!}{%
	\begin{tabular}{ l  c  c  c}
		\toprule
		\multicolumn{1}{l}{\textbf{Harvester}}                        &
		\multicolumn{1}{c}{\textbf{Harvested energy per mastication}} &
		\multicolumn{1}{c}{\textbf{Reference}}                        \\
		\midrule
		Piezo earpiece        & $44$µJ 		 & \cite{Delnavaz2013} \\
	    Hydroelectromagnetic  & $0.2$µJ      & \cite{Delnavaz2012} \\
		Piezo sensor          & $0.1$µJ      & \cite{Carioli2018}  \\
		\bottomrule
	\end{tabular}}
	\caption{Existing harvesters exploiting the ear canal deformation energy}
	\label{tab:harvesters_ear}
\end{table}
%%%%%%%%%%%%%%%%%%%%%  
Based on the literature, we propose a new technological solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion. The next section states on the energy source characterization and on the harvesting strategy we adopted. Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle. Section \ref{sec:SYSTEM MODELING AND SIMULATIONS} shows the global system  modeling and the numerical simulation on its behavior. Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS} then exposes the experimental validation performed on the harvester critical components and section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model. Section \ref{sec:ANALYZE AND DISCUSSION} discusses this work major contributions and the harvester potential. Finally, a conclusion is stated in the last section.

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{ENERGY SOURCE AND HARVESTING STRATEGY}
\label{sec:THE ENERGY SOURCE AND HARVESTING STRATEGY}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The energy source}	
	\label{The energy source}
    %/////////////////////////////////////////////
The ear canal deflection energy is not a usual source because of the soft tissues and the low frequency of mastication. Thus, the traditional transducing methods are not suitable enough for the application.

On one hand, the ear canal global bending energy is 5 times higher than the local compression energy. To date, the literature proposes only one way to harvest the bending energy from the ear canal wall, which is to use of soft materials as the piezoelectric earplug previously introduced \cite{Delnavaz2013}. The very low mechanical impedance of the soft tissue in fact limits the use of more effective rigid piezoelectric materials.

On the other hand, the hydraulic extraction strategy proposed in \cite{Delnavaz2012} only exploits the local compression energy. However, it allows to transmit the energy outside the ear canal and benefit so from larger effective space. The latter is in fact essential as it becomes then possible to implement an impedance adaption stage and more effective transducing methods that could not fit directly inside the ear canal restricted volume. The present work is then based on the exploitation of the ear canal by a liquid filled earplug. As energy source, the latter can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$. In order to optimize the energy extraction, the earplug must fit the ear canal wall. Turcot \emph{et al.} demonstrated that the initial pressurization must be at a minimum of 14kPa to achieve a good fit. Bouchard-Roy \emph{et al.} studied the dynamic pressure variation inside the earplug for different initial pressurization levels \cite{Bouchard-Roy2020}. A maximum of $\text{max}(\Delta p_{ear})=12$kPa of dynamic pressure variation , with a $28$kPa of initial pressurization, has been noted during the mastication for seven subjects. Besides, the temporal evolution of the volume variation $\Delta V_{ear}$ has been estimated in \cite{Delnavaz2012} and the result for one mastication cycle is presented on figure \ref{fig:deltaV_ear}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={20.5cm 0cm 0cm 10.8cm},clip, width=0.4\textwidth]{figures/deltaV_ear.pdf}
	\caption{Ear canal volume variation for one mastication cycle \cite{Delnavaz2012}}
	\label{fig:deltaV_ear}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The earplug operation characteristic behavior has not been studied yet. Thus, the evolution of the volume variation $\Delta V_{ear}$ is not well known as a function of the pressure variation $\Delta p_{ear}$. However, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with a 28kPa pressurized earplug and a maximum volume variation of $\Delta V_{ear,m}=60$mm$^3$. $p_c$ stands for the comfort pressure by estimating that the user could feel discomfort if $\Delta p_{ear}>p_c$. The energy estimation assumes that the earplug is a perfect flow rate source, which is an optimistic hypothesis leading to $0.9$mJ available from one mastication. Based on 2200 mastication cycles per day, according to \cite{Goll2011}, there would be $2$mJ available per day, per ear. This amount of energy could theoretically enhance supply 23.5\% of the 17J of needed for the state of the art of cochlear implants \cite{Kulah2022}. Further research in both domains related to hearing aids and energy harvesting could lead to fully autonomous devices in the future.
\begin{align}
	\text{max}(E_{hyd}) = p_c \cdot \Delta V_{ear,m} = 0.9\text{mJ}
	\label{eq:max_hydraulic_energy}
\end{align}

    %///////////////////////////////////////////// 
	\subsection{The harvesting strategy}	
	\label{The harvesting strategy}
    %/////////////////////////////////////////////
The application is not suitable for magnetic interactions for two major reasons. Magnetic fields admit high non-linear properties at small scales and their effectiveness decreases as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}. The piezoelectric ceramics yet appear like good candidates, but they can not be easily used because of their high stiffness. For this reason, and also because of the higher conversion efficiency of resonant structures, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021}. These structures are commonly used for broadband energy harvesting. A majority of the papers with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}. Stoppers however dissipate energy and demand maintenance with time, in order to replace rubbing parts. To overcome this drawback, alternative solutions use mechanically bistable oscillators (BO) to perform frequency-up without any rubbing parts \cite{Vocca2012}. Recent advances 
led to the development and optimization of  bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}. They show enhanced performances due to high electromechanical coupling and broadband efficiency.
Preliminary calculations based on the Duffing equation defining the BO mechanical behavior \cite{Tseng1971}, and the linearity of piezoelectric beams, offer a comparison tool to determine the best technological approach to maximize the harvested energy from the hydraulic source. Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced. To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer. The hydraulic-mechanic interface is chosen to be a hydraulic cylinder. On one hand, the best linear spring is capable of storing/extracting a maximum of $0.5\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$) if actuated by the source through a hydraulic cylinder. On the other hand, a BO type non-linear spring is inherently capable of extracting more than $65\%$ from the same source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
	\caption{Hydraulic source exploitation depending on the mechanical load}
	\label{fig:OB_vs_LINEAR}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BO as a promising solution for our application. 
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
\label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the ear canal geometry variation} 
	\label{fig:system_presentation}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system. It uses a liquid filled earplug to transmit the energy outside the ear canal and benefit so from larger effective space. To maximize the efficiency, the system integrates a frequency-up conversion stage performed by a bistable oscillator (BO). The latter implements an amplified piezoelectric generator (APG) made of a flextensional elastic APX4 steel structure containing stacked lead zirconate titanate (PZT) ceramics (fig. \ref{fig:APG}). The electromechanical converter composed of the BO and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Guo2019}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htb]
	\begin{center}
		\begin{subfigure}[t]{0.6\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={16cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/APG_schema.pdf}
			\caption{Detailed schema}
			\label{fig:APG_schema}
		\end{subfigure}
		\hfillx
		\begin{subfigure}[t]{0.29\linewidth}
			\captionsetup{justification=centering}
			\includegraphics[trim={29.5cm 0cm 0cm 8cm},clip,width=0.65\linewidth]{figures/APG_photo.pdf}
			\caption{Picture}
			\label{fig:APG_photo}
		\end{subfigure}
		\caption{The APG presentation}
		\label{fig:APG}
	\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The electromechanical converter is actuated, by two hydraulic cylinders (HC), with the hydraulic energy transmitted from the liquid filled earplug, through a pressure separator, a hydraulic amplifier and two hydraulic valves (HV).

To maximize the mechanical energy transfer between the ear canal and the earplug, the latter is lightly pressurized. A minimum of 14kPa is needed in order to fit the earplug to the ear canal wall \cite{Delnavaz2013}. The pressure separator ensures that this initial pressurization does not interfere on the system operation. Then, during a mastication cycle, the TMJ compresses the ear canal wall and expels so the fluid outside the earplug. The HVs ensure to led the fluid alternatively to each HC in order to actuate the BO mass back and forward. The hydraulic amplifier adapts the cylinders stroke to the available earplug flow rate and also adapts the mechanical impedance of the BO to the mechanical impedance of the ear canal wall.

The BO mass has two stable equilibrium positions, $x_m = x_0$ and $x_m = -x_0$. The harvester operates on two major phases. The first consists on the BO mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$. During the second phase the mass goes oscillate around the opposite stable equilibrium position until it stops, while a portion of the oscillatory energy is converted in electricity by the GPA. The mass then moves backward during the next mastication, completing so the harvester cycle.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={20cm 0cm 0cm 10.75cm},clip, width=\linewidth]{figures/HV_actuation_detail.pdf}
	\caption{Contact detail between a HV and the BO mass} 
	\label{fig:HV_actuation_detail}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to maximize the harvested energy we must minimize the energy consumed by the HVs. A technological solution for this role is to use a flexible tube buckled by bending. The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BO environment. The valve is composed of a flexible tube connected between a rigid part of the hydraulic circuit and a fixed one. The BO mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube. Consequently, a pressure loss is generated through the valve in buckled position. Thus, a HV is considered closed when the BO mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$. Two HVs symmetrically placed on each side of the $\vec{x}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BO mass position. The HV technological choice is motivated by three major arguments. First, the absence of electromechanical transduction minimizes the energy losses for the valve operation. Then, the post-buckling softening of the bent tube minimizes the mechanical impact on the BO mass dynamic operation. Finally, it is well adapted at the millimetric application scale.

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{SYSTEM GLOBAL MODELING AND SIMULATIONS}
\label{sec:SYSTEM MODELING AND SIMULATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
The harvester is a multyphisic system composed of hydraulic, mechanical, and electrical components. This section presents a global multiphysic model describing the theoretical system operation. Two coupled subsystems are considered. The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BO + APG) under the mechanical influence of a HV and a HC. Then, the subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug. Finally, the section \ref{subsec:Global model simulation} exposes the numerical simulation of the designed multiphysic coupled model.

    %///////////////////////////////////////////// 
	\subsection{Modeling of the electromechanical converter}	
	\label{subsec:The electromechanical converter}
    %/////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{figures/schema_cinematique1.pdf}
	\caption{Cinematic schema of the of the electromechanical converter under the mechanical influence of a HV and a HC}
	\label{fig:schema_cinematique1}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The figure \ref{fig:schema_cinematique1} shows the cinematic schema of the electromechanical converter under the mechanical influence of a HV and a HC. The different schematized rigid bodies all designated in the table \ref{tab:Designation of rigid bodies}. The BO is represented by 4 identical arms articulated by 8 hinges and a central mass. The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, indicative of the piezoelectric transduction, expressed by the equation \ref{eq:k2_def}.\\
The model is based on the following hypotheses:
\begin{itemize}
	\item The only mass considered is the BO mass (2).
	\item All parts are infinitely rigid beside the APG (4).
	\item The hinges are considered elastic. They are defined by their rotational stiffness $K_{\varphi}$ and their mechanical damping is included in the global viscous damping coefficient $\mu$.
	\item The contact between the BO mass (2) and the HC piston head (5) is considered permanent.
	\item We assume the small-angle approximation with \mbox{$x_0<<L$}. 
\end{itemize}
\begin{equation}
	k^2 = \dfrac{\alpha^2}{\alpha^2 +  K C_p}
	\label{eq:k2_def}
\end{equation}
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
	\begin{tabular}{ c | c }
		\toprule
		\multicolumn{1}{c}{\textbf{Num}}  &
		\multicolumn{1}{c}{\textbf{Name}}  \\
		\midrule
		0	& Fixed frame      	  	\\  
		1	& BO arm      	  	\\  
		2	& BO mass     	\\
		3	& HC piston head	\\
		4	& APG     	\\
		5	& Simplified HV mechanical model     	\\
		\bottomrule
	\end{tabular}
	\caption{Designation of rigid bodies}
\label{tab:Designation of rigid bodies}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

By isolating the BO mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium with respect to the different external forces. The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA} where the provenance of the different terms is highlighted. The BO mechanical equilibrium took aside contains the mass inertial term, a non-linear stiffness depending on $x_m$, the hinges stiffness and viscous losses. This expression has also been demonstrated by the Lagrange method in past works \cite{Liu2013}. The first term introduced by the HV is related to its rotationnal stiffness and the second term is related to the friction losses at the contact point $T$ (fig. \ref{fig:HV_actuation_detail}). A dry friction model is choose to describe the nature of the contact between the two components. Thus, $F_f$ will depend on a dry friction coefficient $\mu_f$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$ (eq. \ref{eq:Dry_friction}). The force $F_{pis}$ induced by the piston head of the HC on the OB mass will depend on hydraulic parameters. The hydro-mechanical coupling is highlighted later by the equation \ref{eq:equilibre_dynamique_piston_ouvert}.
\begin{equation}
	F_f = \mu_f \text{sign}(\dot{x}_m)
	\label{eq:Dry_friction}
\end{equation}

The electrical power generated by the APG is dissipated in a load resistor $R_{ch}$ calculated with an adaptive impedance matching expressed by the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
\begin{equation}
	R_{ch} = \dfrac{1}{C_p w_0}
	\label{eq:R_ch_adaptive_imp}
\end{equation}
Thus, the equation governing the electrical behavior of the APG is :
\begin{equation}
	\dfrac{U_p}{R_{ch}} = 
	-\alpha\dfrac{d}{dt}\biggl(2\sqrt{{l_0}^2-x_m^2}\biggr)
	- C_p\dot{U_p}
	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U_p}
\end{equation}
Consequently, the generated power $P_e$ expression is :
\begin{equation}
	P_e = \frac{{U_p}^2}{R_{ch}} 
	\label{eq:P_e}
\end{equation} 
With the small-angle approximation, the system equation \ref{eq:OB+GPA+VH+piston} defines the electromechanical behavior of the harvester. The HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BO mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.

%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{equation}
\overbrace{\ m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) 
							-\mu \dot{x}_m
							-\frac{4K_{\varphi}\varphi}{L}\ }^{OB}
			\underbrace{\ -2\alpha U_p \tan(\varphi)\ }_{APG}		 
			\overbrace{\ -\dfrac{K_{HV}\theta}{a} - F_f\ }^{HV}
			\underbrace{\ -F_{pis}\ }_{HC}
\label{eq:OB-GPA}
\end{equation}
\end{figure*}
% \FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{equation}
% \begin{small}
	\begin{dcases}
\ddot{x}_m = - \frac{2K{x_0}^2}{mL^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)
			   x_m - \frac{\mu}{m}\dot{x}_m - \frac{2\alpha U_p\ x_m}{mL}
			-\frac{K_{VH}(x_m)\theta(x_m)}{ma}
			-\frac{F_f}{m}
			-\frac{F_{pis}}{m} \\
\dfrac{U_p}{R_{ch}} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p
	\end{dcases}
	\label{eq:OB+GPA+VH+piston}	
% \end{small}
\end{equation}
\end{figure*}
% \FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%
    %///////////////////////////////////////////// 
	\subsection{Modeling of the hydraulic circuit}	
	\label{subsec:The hydraulic circuit}
    %/////////////////////////////////////////////
This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves. In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}. Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier. These hydraulic components will rather be considered on further work.

In order to model the coupled behavior of the two hydraulic branches, we will use the index "$o$" for the open branch and the index "$c$" for the closed one. The following hypotheses will be considered :
\begin{itemize}
	\item The fluid is incompressible and Newtonian.
	\item The hydraulic circuit is non-deformable (no volume change) and there is no leakage.
	\item The hydraulic actuation is considered quasi-static (QS) in front
	the oscillation frequency of the BO.
\end{itemize}
The projection on the $\vec{x}$ axis of the Newtons 2$^{nd}$ law applied respectively to each HC moving piston gives us their mechanical equilibrium as follows :
\begin{align}
	\text{Opened cylinder ~}& \left\{~
	-F_{pis} - p_{oc}\ S_{c} - \lambda_{c}\ \dot{x}_{oc} = 0
	\right.
	\label{eq:equilibre_dynamique_piston_ouvert}\\
	\text{Closed cylinder ~}& \left\{~
	p_{cc}\ S_{c} - \lambda_{c}\ \dot{x}_{cc} = 0
	\right.
	\label{eq:equilibre_dynamique_piston_ferme}
\end{align}
Where $p_c$ is the HC chamber pressure and $x_c$ its moving piston position. $F_{pis}$ accounts for the OB counter-reaction on the HC. Thus, with the QS assumption, it can be derived from equation \ref{eq:OB+GPA+VH+piston} and expressed as follows : 
\begin{align}
	-F_{pis} & = F_{bo}\\
	-F_{pis} & = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr) - F_f
	\label{eq:F_OB_xxxxxx}
\end{align}
Then, by juxtaposing the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
\begin{align}
	\text{Opened branch ~}& \left\{~
	p_{ear} = p_{in} + \dfrac{1}{a_h}\biggl(p_{oc} + Cf_0 {q_0}^2 \biggr)
	\right.
	\label{eq:Bernoulli_piston_ouvert}\\
	\text{Closed branch ~}& \left\{~
	p_{ear} = p_{in} + \dfrac{1}{a_h}\biggl(p_{cc} + Cf(x_m) {q_f}^2 \biggr)
	\right.
	\label{eq:Bernoulli_piston_ferme}
\end{align}
Where $p_{in}$ is the initial pressurization, $a_h$ is the hydraulic amplification ratio, $q$ the flow rate and $Cf$ the pressure loss coefficient of a HV. The latter will depend on the HV bending angle $\theta$ and therefore on the BO mass position $x_m$ (fig. \ref{fig:HV_actuation_detail}). $Cf$ will be as more important as the $x_m$ increases. It is minimal when the HV is unbent and worth $Cf_0$.

Also, the no leakage assumption imposes that all the outgoing fluid from the earplug is contained in the two hydraulic branches (eq. \ref{eq:conservation_masse}).
\begin{equation}
	q_{ear} = q_o + q_f
	\label{eq:conservation_masse}
\end{equation}
Moreover, the same previous hypothese requires that all the fluid entering the HC results on a piston displacement (eqs \ref{eq:conservation_masse_ouvert},\ref{eq:conservation_masse_ferme}).
\begin{align}
	\text{Opened cylinder ~}& \left\{~
	q_o = S_{hc} \dot{x}_{oc}
	\right.
	\label{eq:conservation_masse_ouvert}\\
	\text{Closed cylinder ~}& \left\{~
	q_c = S_{hc} \dot{x}_{cc}
	\right.
	\label{eq:conservation_masse_ferme}
\end{align}

    %///////////////////////////////////////////// 
	\subsection{Preliminary dimensioning}	
	\label{subsec:Preliminar dimensionning}
    %/////////////////////////////////////////////
The dimensioning starts by setting technological choices in order to experimentally validate the multiphysic coupled model. Therefore, the APG is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator, setting so the stiffness $K$. Then, the MQP4-10S HC from SMC will ensure the hydraulic to mechanical interface, setting then the cylinder piston section $S_{hc}$. Next, the hydraulic commutation of the two parallel branches is driven by two HVs made of collapsed flexible tubes, setting then $Cf(x_m)$. Finally, the \mbox{$L=16mm$ }parameter is chosen to be consistent with the application scale.

The maximum energy extractable with the BO through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ }to \mbox{$x_m=0$}. Knowing that it is equal to 65\% of the upper limit of the available hydraulic energy (eq. \ref{eq:max_hydraulic_energy} $\&$ fig. \ref{fig:OB_vs_LINEAR}), we can set the BO buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}. The harvester is thus optimized depending on the energy source.
\begin{equation}
	E_{pb} = \dfrac{K x_0^4}{3L^2}=0.65p_c \Delta V_{ear,m}
	\label{eq:Ep_bar}
\end{equation}
Two additional coupled requirements allow the system operation by setting the amplification level $a_h$. First, the available fluid must be enough to ensure the HC stroke from its equilibrium position until the BO mass reaches \mbox{$x_m=0$} (eq. \ref{eq:contrainte_course}). Then, the BO mechanical impedance on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}. At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to ensure the user comfort. If not, $\epsilon$ must be decreased, decreasing the extracted energy for the benefit of comfort.
\begin{empheq}[left=\empheqlbrace]{align} 
	\Delta V_{ear,m} = a_h\ S_{hc}\  x_{c0}
	\label{eq:contrainte_course}\\
	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0^3}{3\sqrt{3}L^2}
	\label{eq:contrainte_confort}
\end{empheq}

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\label{NUMERICAL MODEL AND SIMULATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

	%///////////////////////////////////////////// 
	\subsection{HV hydraulic targeted behavior}	
	\label{subsec:HV hydraulic targeted behavior}
	%/////////////////////////////////////////////
A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs. The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation. In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. So we introduce $r_{Cf}$ as follows:
\begin{equation}
	r_{Cf} = \dfrac{\text{Closed HV}}{\text{Opened HV}}	= \dfrac{Cf_c}{Cf_0}	
	\label{eq:r_Cf_definition}
\end{equation}
Where $Cf_f=Cf(\pm x_0)$. The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube. Therefore, we preliminarily assume that it is linear and defined as follows :
\begin{align}
	Cf(x_m) & = Cf_0 + \dfrac{Cf_f - Cf_0}{x_0}\ x_m  \notag \\
			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
			\label{eq:Cf(x_m)_linear}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={9.5cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_debit_Cf_pression_1CYCLE.pdf}
	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
	\label{fig:simu_pos_debit_Cf_pression_1CYCLE}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={10cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_Up_puissances_energie_1CYCLE.pdf}
	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
	\label{fig:simu_pos_Up_puissances_energie_1CYCLE}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{EXPERIMENTAL CHARACTERIZATIONS}
\label{sec:EXPERIMENTAL CHARACTERIZATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter}	
	\label{The electromechanical converter}
    %/////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
\begin{center}
\captionsetup{justification=centering}
	\begin{subfigure} [h!]{0.49\textwidth}
		\includegraphics[trim={1.4cm 0cm 0cm 0cm},clip,width=\textwidth]{figures/monobloc+GPA_face.pdf}
		\caption{aaa} 
		\label{fig:/monobloc+GPA_face}
	\end{subfigure}
	%\hfill
	\begin{subfigure}[h!]{0.49\textwidth}
		\includegraphics[trim={6cm 3cm 7.5cm 2.6cm},clip, width=\textwidth]{figures/monobloc+GPA_iso.pdf}
		\caption{aaa}  
		\label{fig:/monobloc+GPA_iso}
	\end{subfigure}
	\caption{aaa}
\end{center}
\label{fig:/monobloc+GPA_face}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

    %///////////////////////////////////////////// 
	\subsection{The HV hydraulic behavior}	
	\label{The hydraulic valves}
    %/////////////////////////////////////////////
	\subsubsection{Test bench presentation}
	\subsubsection{Results and discussion}

\begin{figure*}[!htb]
\begin{center}
	\captionsetup{justification=centering} 
	\includegraphics[trim={8cm 0cm 0cm 5cm},clip,width=0.8\textwidth]{figures/BDT_hydraulique_VH.pdf}
	\caption{Banc d'essai pour la caractérisations hydrauliques de VH}
	\label{fig:BDT_hydraulique_VH}
\end{center}	
\end{figure*}    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure*}[!htb]
\begin{center}
	\captionsetup{justification=centering} 
	\includegraphics[trim={2cm 0cm 0cm 10cm},clip,width=\textwidth]{figures/essais_hydraulique_VH.pdf}
	\caption{Essais de caractérisations hydrauliques de VH}
	\label{fig:essais_hydraulique_VH}
\end{center}	
\end{figure*}    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htb]
\begin{center}
	\captionsetup{justification=centering} 
	\includegraphics[trim={2cm 0cm 0cm 4cm},clip,width=0.49\textwidth]{figures/fabrication_tube_experimental.pdf}
	\caption{Méthode de fabrication de la VH}
	\label{fig:fabrication_tube_experimental}
\end{center}	
\end{figure}    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
\begin{center}
	\captionsetup{justification=centering}
	\includegraphics[trim={10cm 0cm 0cm 0cm},clip,width=0.49\textwidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
	\caption{$Cf_{VH}$ calculé à partir des essais pour 7 incréments d'angles}
	\label{fig:resultats_essais_hydraulique_VH_D1mm}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%
	%/////////////////////////////////////////////
	\subsection{The HV mechanical influence on the electromechanical converter (théorique = x0 réduit donc faut compenser)}	
	\label{The mechanical influence of the valve on the electromechanical converter}
	%/////////////////////////////////////////////
Theoretically...

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
\label{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
	%/////////////////////////////////////////////
	\subsubsection{Free release trials}
	%/////////////////////////////////////////////

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\begin{figure}[!htbp]
	\begin{center}
		\captionsetup{justification=centering}
		\includegraphics[trim={4cm 0cm 0cm 9.5cm},clip,width=0.7\textwidth]{figures/contact_M_VH_lachers.pdf}
		\caption{Image de la VH$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,vh}$)}
		\label{fig:contact_M_VH_lachers}
	\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	%/////////////////////////////////////////////
	\subsubsection{Recalibrated model}
	%/////////////////////////////////////////////

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
	\centering
	% \resizebox{\textwidth}{!}{%
		\begin{tabular}[t]{c|c|c}
\toprule
\multicolumn{1}{c}{\textbf{Paramètre}}	&
\multicolumn{1}{c}{\textbf{Valeur OB}} 	& 
\multicolumn{1}{c}{\textbf{Valeur OBVH}}  \\
\midrule
$D_g$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
$\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& \textcolor{red}{{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
$K_{T100p}(\theta_f)$ [Nmm/rad] & \cellcolor{ashgrey}  		&  0.27 					\\ \hline
$a$ [mm]         			    & \cellcolor{ashgrey}  		&  2.24				 	 	\\ \hline
$\mu_{fs}$ [~~] 				& \cellcolor{ashgrey}  		&  0.42  					\\ \hline
$K$ [N/m] 						&	84480			  	 	&  84480  					\\ \hline
$x_0$ [mm] 						& \textcolor{red}{0.59}		& \textcolor{red}{0.50}  	\\ \hline
$v_0$ [mm/s] 					& \textcolor{red}{10}		& \textcolor{red}{65}  		\\ \hline
$Q$	[~~] 						& 		24.0		 		& 5.0     					\\ \hline
$k^2_{sys}$ [\%] 				& 		1.25		 		& \textcolor{red}{1.25}   	\\ \hline
$\eta_{ob}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
$R_{ch}$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
$m$	[g]						    &	\textcolor{red}{5.88}	& 9.00   					\\ \hline	
$f_0$ [Hz]						&		32.9				& 27.9   					\\
\bottomrule	
	\end{tabular}
        \caption{Valeur des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
        \label{tab:parametres lacher tube}
\end{table}        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{ANALYZE AND DISCUSSION}
\label{sec:ANALYZE AND DISCUSSION}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{CONCLUSION}
\label{sec:CONCLUSION}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%\begin{thebibliography}{00}
\bibliography{biblioArticle1.bib}
\bibliographystyle{elsarticle-num}
%\bibliographystyle{unsrt} 
%\end{thebibliography}

\end{document}
\endinput

### 2022-09-29 article_system.tex
update

@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{SYSTEM GLOBAL MODELING AND SIMULATIONS}
-\label{sec:SYSTEM MODELING AND SIMULATIONS}
+\section{SYSTEM GLOBAL MODELING}
+\label{sec:SYSTEM MODELING}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{NUMERICAL MODEL AND SIMULATIONS}
 \label{NUMERICAL MODEL AND SIMULATIONS}
@@
 	%///////////////////////////////////////////// 
-	\subsection{HV hydraulic targeted behavior}	
+	\subsection{Targeted hydraulic behavior of the HVs}	
 	\label{subsec:HV hydraulic targeted behavior}
@@
 \begin{equation}
-	r_{Cf} = \dfrac{\text{Closed HV}}{\text{Opened HV}}	= \dfrac{Cf_c}{Cf_0}	
+	r_{Cf} = \dfrac{Cf(\text{Closed HV})}{Cf(\text{Opened HV})}	= \dfrac{Cf_c}{Cf_0}	
 	\label{eq:r_Cf_definition}
 \end{equation}
-Where $Cf_f=Cf(\pm x_0)$.
+Where $Cf_c=Cf(\pm x_0)$.
 The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube.
@@
 \begin{align}
-	Cf(x_m) & = Cf_0 + \dfrac{Cf_f - Cf_0}{x_0}\ x_m  \notag \\
-			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
+	Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m  \notag \\
+			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{Cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
 			\label{eq:Cf(x_m)_linear}
 \end{align}
+Regarding the BO symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
+
+	%///////////////////////////////////////////// 
+	\subsection{Simulation results}	
+	\label{subsec:Simulation results}
+	%/////////////////////////////////////////////
+The numerical model aims to demonstrate the theoretical operation of the new concept of harvester.
+By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
+\ref{fig:deltaV_ear}), the numerical model must give the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
+
+The ratio $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the opened HV.
+The mastication cycle is identically quadrupled in order to test the system cycling robustness.
+Also, the earplug is assumed as a perfect flow rate source.
+
+Figure \ref{fig:positions+DeltaV_debits_pear} presents the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
+The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), knowing that the gravity influence is not considered.
+The same figure shows a focused view on the two main phases of the harvester operation during the actuation by the \emph{"bottom"} HC.
+The simulation begins with the following initial conditions:
+\begin{itemize}
+	\item The mass is at the $-x_0$ equilibrium position.
+	\item The \emph{"top"} HV is closed ($Cf_{top} = Cf_c$) and the \emph{"bottom"} side HV is opened ($Cf_{bot} = Cf_0$).
+	\item There is no contact between the mass and the HCs.
+	\item A mastication occurs.
+\end{itemize}
+
+The first phase consists on pushing on the BO mass to store potential energy, until the mass reaches $x=0$.
+During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BO counter-reaction force.
+The second phase begins after the mass crosses the $x_m=0$ position.
+The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$).
+The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent.
+The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG.
+The cycling of the hydraulic branches is possible when $r_{Cf} =(r_{Cf})_{min}=26$.
 
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={9.5cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_debit_Cf_pression_1CYCLE.pdf}
-	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
-	\label{fig:simu_pos_debit_Cf_pression_1CYCLE}
+	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
+	\caption{}
+	\label{fig:positions+DeltaV_debits_pear}
 \end{figure*}
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={10cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_Up_puissances_energie_1CYCLE.pdf}
-	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
-	\label{fig:simu_pos_Up_puissances_energie_1CYCLE}
+	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
+	\caption{}
+	\label{fig:positions_Up_puissances_energies}
 \end{figure*}
@@
     %/////////////////////////////////////////////
+
+	%/////////////////////////////////////////////
 	\subsubsection{Test bench presentation}
+	 %/////////////////////////////////////////////
+
+	%/////////////////////////////////////////////
 	\subsubsection{Results and discussion}
+    %/////////////////////////////////////////////
 

### 2022-09-30 article_system.tex
update

@@
 In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
-So we introduce $r_{Cf}$ as follows:
+So we introduce the hydraulic restriction coefficient $r_{Cf}$ defined as follows :
 \begin{equation}
@@
 Also, the earplug is assumed as a perfect flow rate source.
+The calculated and the resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
 
@@
 The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG.
-The cycling of the hydraulic branches is possible when $r_{Cf} =(r_{Cf})_{min}=26$.
+The flow rate goes toward the right piston when $r_{Cf}$ is set at a minimum value of \mbox{$(r_{Cf})_{min}=26$}.
+
+Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
+The theoretical global efficiency of the harvester is evaluated at $\eta_g=67.1$\% with 20µJ harvested from one mastication.
+The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}.
+The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e.
+a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
+The harvester efficiency could lead to a theoretical maximum of $342$µJ extractable from the ear canal.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
+\begin{table}	
+	\centering
+	\begin{tabular}{c|c|c}
+\toprule
+\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
+\midrule
+$K$					&	0.256			& [$N/\mu m$]			\\ \hline
+$x_0$				&	0.49			& [$mm$] 				\\ \hline
+$L$					&	16.0			& [$mm$] 				\\ \hline
+$m$					&	5.88			& [$g$] 				\\ \hline
+$x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
+$R_{ch}$			&	15.5			& [$k\Omega$] 			\\ \hline
+$\alpha$			&   0.105			& [$N/V$] 				\\ \hline
+$C_0$	   			&	0.25			& [$\mu F$]				\\ \hline
+$Q$ 				&	50				& [-] 					\\ \hline
+$\eta_g$			& 	67.1			& [$\%$]		\\ 
+\bottomrule
+	\end{tabular}
+	\caption{Electromechanical parameters}
+	\label{tab:parametres électromécaniques}
+\end{table}
+\begin{table}
+	\centering
+	\begin{tabular}{c|c|c}
+\toprule
+\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
+\midrule
+$D_{hc}$  	   				&	4				& [$mm$]			\\ \hline
+$a_h$					&	7.2				& [-]				\\ \hline
+$p_c$					&	1				& [$kPa$]			\\ \hline
+$\Delta V{ear,m}$		& 60				& [$mm^3$]			\\ \hline
+$Cf_0$					&	0.21e17			&[$Pa.s^2m^{-6}$]	\\ \hline
+$Cf_c$					&	5.46e17			&[$Pa.s^2m^{-6}$]	\\
+\bottomrule 
+	\end{tabular}
+	\caption{Hydraulic parameters}
+	\label{tab:parametres_hydrauliques}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BO mass.
+Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
+
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{EXPERIMENTAL CHARACTERIZATIONS}
-\label{sec:EXPERIMENTAL CHARACTERIZATIONS}
+\section{EXPERIMENTAL CHARACTERIZATION OF THE \mbox{ELECTROMECHANICAL} CONVERTER}
+\label{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
     %///////////////////////////////////////////// 
-	\subsection{The electromechanical converter}	
-	\label{The electromechanical converter}
+	\subsection{The electromechanical converter presentation}	
+	\label{The electromechanical converter presentation}
     %/////////////////////////////////////////////
+The device heart is the electromechanical converter composed of the BO implementing the APG and therefore, they have been designed with respect to space requirements.
+We opted for a monobloc structure with blades in order to optimize the oscillator quality factor by avoiding screw assemblies.
+Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM).
+The 8 hinges are assured by 4 buckled blades (BB) and a vertical guide blade (GB) ensures the APG mounting.
+The efficient part composed of the blades and the central mass are $1.2$mm think.
+The external rigid 6mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs.
+The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}.
+The following sections describe the design method that led to the values of the different parameters, depending on our needs.
+%%%%%%%%%%%%%%%%%
+\begin{table}[!htbp]
+	\centering
+    \resizebox{\linewidth}{!}{%
+		\begin{tabular}{l|c|c}
+			\toprule
+\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Valeur [Unit]} \\
+\midrule
+APX4 steel Young's modulus     & $E$                       & 211 [GPa]  \\
+APX4 steel elastic resistance  & $Re_{APX4}$               & 955[MPa]    \\
+Dimensions of a buckled blade  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
+Dimensions of the guide blade  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
+% Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
+Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [Nm/rad] \\
+Stiffness of the guide blade along $\vec{z}$  & $K_{gb}$   & 190 [N/m] \\
+Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
+Stiffness of the APG along $\vec{z}$          & $K$        & 252  [kN/m]\\
+			\bottomrule
+		\end{tabular}}
+	\caption{Definitions and values of the fabricated BO}
+	\label{tab:parametres_lames}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%% 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!htbp]
-\begin{center}
+\begin{figure}[!htbp]
+\centering
 \captionsetup{justification=centering}
-	\begin{subfigure} [h!]{0.49\textwidth}
-		\includegraphics[trim={1.4cm 0cm 0cm 0cm},clip,width=\textwidth]{figures/monobloc+GPA_face.pdf}
-		\caption{aaa} 
-		\label{fig:/monobloc+GPA_face}
-	\end{subfigure}
-	%\hfill
-	\begin{subfigure}[h!]{0.49\textwidth}
-		\includegraphics[trim={6cm 3cm 7.5cm 2.6cm},clip, width=\textwidth]{figures/monobloc+GPA_iso.pdf}
-		\caption{aaa}  
-		\label{fig:/monobloc+GPA_iso}
-	\end{subfigure}
-	\caption{aaa}
-\end{center}
-\label{fig:/monobloc+GPA_face}
-\end{figure*}
+	\includegraphics[trim={19.2cm 0cm 0cm 5cm},clip,width=.7\linewidth]{figures/monobloc_face.pdf}
+	\caption{Face transparency view of the monobloc BO CAO}
+\label{fig:monobloc_face}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %///////////////////////////////////////////// 
+	\subsection{The electromechanical converter presentation}	
+	\label{The electromechanical converter presentation}
+    %/////////////////////////////////////////////
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \toprule
-\multicolumn{1}{c}{\textbf{Paramètre}}	&
-\multicolumn{1}{c}{\textbf{Valeur OB}} 	& 
-\multicolumn{1}{c}{\textbf{Valeur OBVH}}  \\
+\multicolumn{1}{c}{\textbf{Parameter}}	&
+\multicolumn{1}{c}{\textbf{Value OB}} 	& 
+\multicolumn{1}{c}{\textbf{Value OBVH}}  \\
 \midrule
@@
 	\end{tabular}
-        \caption{Valeur des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
+        \caption{Value des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
         \label{tab:parametres lacher tube}

### 2022-10-03 article_system.tex
update

@@
 The efficient part composed of the blades and the central mass are $1.2$mm think.
-The external rigid 6mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs.
+The external rigid $6$mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs.
 The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}.
@@
     %///////////////////////////////////////////// 
-	\subsection{The electromechanical converter presentation}	
-	\label{The electromechanical converter presentation}
-    %/////////////////////////////////////////////
+	\subsection{BO blades design}	
+	\label{subsec:BO blades design}
+    %/////////////////////////////////////////////
+The harvesting occurs during the free oscillation phase.
+The main issue is to maximize the energy conversion efficiency $\eta_{ob}$ of this stage.
+Richards \emph{et al.} demonstrated that for the piezoelectric transduction at the resonance frequency, it can be approximated with the equation \ref{eq:eta_ob} \cite{Richards2004}.
+This expression is valid for an electric extraction based on the adaptive impedance matching strategy.
+\begin{equation}
+	\eta_{ob} = \dfrac{k^2_{sys}\ Q}{k^2_{sys}\ Q + 2}
+	\label{eq:eta_ob}
+\end{equation}
+Where $k^2_{sys}$ is the electromechanical coupling of the harvesting system.
+The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the respective blades (tab.
+\ref{tab:parametres_lames}) as follows :
+% \begin{equation}
+% 	k^2_{sys} = \dfrac{ K_{bb}^2 \alpha^2 }
+% 					  { \biggr(Cp(K+K_{bb} + 
+% 						\dfrac{K_{bb}^2 \alpha^2}{K_{bb} + K_{gb} + K} \biggl)
+% 						 (K_{bb} + K_{gb} + K)^2}
+% 	\label{eq:k2_sys}
+% \end{equation}
+
+\begin{equation}
+	k^2_{sys} = \dfrac{\alpha^2_{eq}}{\alpha^2_{eq} + (K+K_{gb})C_p}
+	\label{eq:k2_sys}
+\end{equation}
+Where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by equation \ref{eq:alpha_eq}.
+It depends on the initial PFF of the APG alone and the and ratio between the equivalent stiffness $K_{eq}$ (eq.
+\ref{eq:K_eq}) of the structure on the $\vec{x}$ axis and the equivalent stiffness of the APG mounted on the GB.
+\begin{equation}
+	\alpha_{eq} = \alpha\ \dfrac{K_{eq}}{K + K_{gb}} 
+	\label{eq:alpha_eq}
+\end{equation}
+\begin{equation}
+	K_{eq} = \dfrac{K_{bb}(K + K_{gb})}{K_{bb} + K_{gb} + K}
+	\label{eq:K_eq}
+\end{equation}
+Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
+If the condition is respected, then $K_{eq}$ can be assimilated to $K$.
+
+On the architecture presented on figure \ref{fig:monobloc_face} the deformation of the GB is similar to the standard case of a fixed-ended beam undergoing a single concentrated load applied at midspan.
+Using structural analysis formulas for this load case, we can express $K_{gb}$ as follows \cite{Leet1993} :
+\begin{equation}
+	K_{gb} = \dfrac{2EI_{gb}el_v^3}{L_v^3}
+	\label{eq:Kgb_definition}
+\end{equation}
+$I_{gb}$ is the second moment of area along $\vec{y}$ axis.
+According the material properties and GB dimensions (tab.
+\ref{tab:parametres_lames}) $K_{gb} = 4.0e2$, which is negligible before $K=0.2e6$.
+
+$K_{bb}$ is for its part verified through a FEM generated with the BO CAD on ANSYS Workbench.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+\centering
+\captionsetup{justification=centering}
+	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
+	\caption{BO finit element model}
+\label{fig:fem_statique}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-04 article_system.tex
update

@@
 $Q$ 				&	50				& [-] 					\\ \hline
-$\eta_g$			& 	67.1			& [$\%$]		\\ 
+$\eta_g$			& 	76				& [$\%$]		\\ 
 \bottomrule
@@
 The external rigid $6$mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs.
+The local thickenings at the midspan of the blades are intended to facilitate the fabrication and also to maximize the BB compression stiffness that maximizes the electromechanical coupling of the harvester, as we show in the following sections.
 The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}.
-The following sections describe the design method that led to the values of the different parameters, depending on our needs.
+The following sections describe the design method that led to the dimensions of the blades that depend on our needs.
 %%%%%%%%%%%%%%%%%
@@
 Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [Nm/rad] \\
-Stiffness of the guide blade along $\vec{z}$  & $K_{gb}$   & 190 [N/m] \\
+Stiffness of the guide blade along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
 Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
@@
 According the material properties and GB dimensions (tab.
-\ref{tab:parametres_lames}) $K_{gb} = 4.0e2$, which is negligible before $K=0.2e6$.
+\ref{tab:parametres_lames}) \mbox{$K_{gb} = 190N/m$}, which is negligible before \mbox{$K=252kN/m$}.
 
 $K_{bb}$ is for its part verified through a FEM generated with the BO CAD on ANSYS Workbench.
-
+Figure \ref{fig:fem_statique} presents the model and the initial and boundary conditions used for the study.
+The fixed frame is replaced by three rigid fixed points in order to minimize the number of elements and reduce the calculation time.
+The APG elastic force is modeled by the load $F_{st}$ applied at the right end of the structure and the transducer is replaced by a rigid mobile part in order to isolate the stiffness of the BBs.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+By imposing incrementally increasing $F_{st}$ and measuring the displacement $z_{st}$ of the moving structure in small displacement condition, we can determine $K_{bb}$ (tab.
+\ref{tab:parametres_lames}) with equation \ref{eq:Kbb_definition}.
+\begin{equation}
+	K_{bb} = \dfrac{F_{st}}{z_{st}}
+	\label{eq:Kbb_definition}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (\ref{tab:parametres électromécaniques}).
 

### 2022-10-05 article_system.tex
update

@@
 \usepackage{empheq}
+\usepackage{textcomp}
 
@@
 \def \hfillx {\hspace*{ -\linewidth} \hfill} % remplir espacement horizontal entre deux sous-figures de façon à remplir toute la largeur du texte.
+% \renewcommand{\degree}[1]{${#1}^\circ$} % °
+
 %----------------------------------------------------------------------
@@
 Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at $\eta_g=67.1$\% with 20µJ harvested from one mastication.
+The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with 20µJ harvested from one mastication.
 The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}.
@@
 a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
-The harvester efficiency could lead to a theoretical maximum of $342$µJ extractable from the ear canal.
+The harvester efficiency could lead to a theoretical maximum of $684$µJ extractable from the ear canal.
 
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 1cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
 	\caption{}
@@
 $x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
-$R_{ch}$			&	15.5			& [$k\Omega$] 			\\ \hline
+$R_{ch}$			&	6.39			& [$k\Omega$] 			\\ \hline
 $\alpha$			&   0.105			& [$N/V$] 				\\ \hline
@@
 $D_{hc}$  	   			&	4				& [$mm$]			\\ \hline
-$a_h$					&	7.2				& [-]				\\ \hline
+$a_h$					&	29				& [-]				\\ \hline
 $p_c$					&	1				& [$kPa$]			\\ \hline
@@
 Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM).
-The 8 hinges are assured by 4 buckled blades (BB) and a vertical guide blade (GB) ensures the APG mounting.
+The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations.
 The efficient part composed of the blades and the central mass are $1.2$mm think.
@@
 	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
-	\caption{BO finit element model}
+	\caption{BO finit element model with initial and boundary conditions for a static study}
 \label{fig:fem_statique}
@@
 \ref{tab:parametres_lames}) with equation \ref{eq:Kbb_definition}.
+The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (tab.
+\ref{tab:parametres électromécaniques}).
 \begin{equation}
@@
 
-The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (\ref{tab:parametres électromécaniques}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
-	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
-	électromécanique.}
+In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BO operation.
+Based on the precedent FEM static model (fig.
+\ref{fig:fem_statique}), a buckling study has been performed for the purpose.
+When the mass crosses the unstable \mbox{$x_m=0$} position, the compression stress on the blades is in fact at its maximum.
+With the same boundary conditions as in figure \ref{fig:fem_statique}, the buckling study imposes the force $F_{st} = F_{z,0}$ modeling the APG elastic counter reaction on $\vec{z}$ axis at $x_m = 0$.
+$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement} relying on figure \ref{fig:schema_cinematique1} :
+\begin{equation}
+	F_{z,0} = 2K \biggl( \sqrt{x_0^2+L^2}-L \biggr)
+	\label{eq:Fz0_flambement}
+\end{equation}
+
+The fundamental buckling mode of the BBs leads to the wanted structural buckling generating the bistable equilibrium positions $\pm x_0$ for the mass.
+The buckling study reveals that $F_{z,0}=0.61$N when the useful buckling mode appears (fig.
+\ref{fig:buckling_fundamental}).
+However, the first secondary undesirable mode illustrated on figure \ref{fig:buckling_secondary} appears for $F_{z,0}=6.4$N.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
+\begin{figure}[!htb]
+	\begin{center}
+		\begin{subfigure}[t]{0.48\linewidth}
+			\captionsetup{justification=centering}
+			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_fundamental.pdf}
+			\caption{Fundamental = useful}
+			\label{fig:buckling_fundamental}
+		\end{subfigure}
+		\hfillx
+		\begin{subfigure}[t]{0.48\linewidth}
+			\captionsetup{justification=centering}
+			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_secondary.pdf}
+			\caption{Secondary = undesirable}
+			\label{fig:buckling_secondary}
+		\end{subfigure}
+		\caption{Deformed shape of the first appearing buckling modes}
+		\label{fig:Buckling_deformed_shapes}
+	\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity.
+Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BO, as presented on figure \ref{fig:buckling_limit}.
+The preliminary simulated case presented in the previous section is well located in the preferable domain where there is no undesirable buckling modes.
+Moreover, the force absorbed by the APG is well under the maximal limit of 18N from which the device could be damaged.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={17.9cm 0cm 0cm 10cm},clip,width=0.9\linewidth]{figures/buckling_limit.pdf}
+	\caption{APG elastic counter reaction on $\vec{z}$ axis at $x_m=0$, depending on the initial structural buckling height $x_0$}
+	\label{fig:buckling_limit}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Ltex language=en
+
+    %///////////////////////////////////////////// 
+	\subsection{Experimental characterizations}	
+	\label{subsec:Experimental characterizations}
+    %/////////////////////////////////////////////
+The BO has been fabricated and mounted and the APG has been implemented on it.
+The experimental test bench for the electromechanical characterizations of the resultant converter is presented on figure \ref{fig:BDT_OB+GPA}.
+An additional blade is mounted with the APG in order to prevent its rotation around any axis.
+A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$µm).
+The bearing decouples the rotation of the screw with the rotation of the blade structure in order to prevent unwanted torsional stress.
+Two symmetrically mounted masses are added on the initial central mass with a 45\degree{} machined plane.
+The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$µm).
+The APG power is dissipated in the $R_{ch}$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
+Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={2cm 0cm 0cm 5.5cm},clip,width=\linewidth]{figures/BDT_OB+GPA.pdf}
+	\caption{Test bench of the electromechanical converter}
 	\label{fig:BDT_OB+GPA}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behavior.
+The test protocol consisted on recreating the operation conditions as close as possible to real-life operation.
+The mass is guided from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then it goes oscillate around the opposite stable equilibrium position.
+The experimental data was then used to identify and recalibrate the following electromechanical parameters of the harvester through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
+\ref{tab:parametres_lacher_free}).
+The correlations were made with iterative simulations of the global model by minimizing the error on these parameters.
+The converter experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{bo}$ have also been extracted from the recalibrated model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={17cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/correlation_simu-exp_OB+GPA.pdf}
+	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres_lacher_free}.}
+	\label{fig:BDT_OB+GPA}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%
@@
 		$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
-	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
+		${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
 		$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\

### 2022-10-06 article_system.tex
update

@@
 
-The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress on the energy consumption of mobile devices around the human body.
-Energy harvesting methods have also been studied on purpose, in order to complement their power supply and enhance the autonomy of the batteries.
-In-ear devices such as hearing aids and cochlear implants are powered by disposable fuel cells or rechargeable batteries.
-The energy consumption of the best integrated devices in the literature converges around $17$J for a 10 hours daily use \cite{Scherer2019,Yip2015,Kulah2022}.
-Woodruff \emph{et al.} showed that patients using hearing aids sometimes struggle to change and select batteries for their devices \cite{Woodruff2021}.
-Another statistical study revealed that the majority of hearing aid and cochlear implants users prefer disposable batteries for the long autonomy, but would have liked rechargeable solutions if the battery cycle was sufficient to complete the day \cite{PracticesAudiology2016}.
-Also, the long term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable fuels.
-These arguments motivate the development of energy harvesting systems to enhance the autonomy of the batteries in order to prevent the premature discharge of in-ear devices.\\
-The common sources are ambient such as solar or wind energy but their availability in the low size environment of the application context makes them not suitable for exploitation.
+The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress on the energy consumption of mobile devices on the human body environment.
+Energy harvesting methods have been studied in order to complement their power supply and enhance the autonomy of the batteries.
+In-ear devices such as hearing aids and cochlear implants are powered by disposable cells or rechargeable batteries.
+The energy consumption of the best integrated devices in the literature rises up to $17$J for a 10 hours daily use \cite{Scherer2019,Yip2015,Kulah2022}.
+Woodruff \emph{et al.} underlined that patients using hearing aids sometimes struggle to change and select batteries for their devices \cite{Woodruff2021}.
+Another statistical study revealed that the majority of hearing aids and cochlear implants users prefer disposable batteries for the long autonomy, but would have liked rechargeable solutions if the battery cycle was sufficient to complete the day \cite{PracticesAudiology2016}.
+Also, the long term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable cells.
+These arguments motivated the development of energy harvesting systems.
+
+The common energy sources are solar or wind energy but their availability in the low size environment of the application context makes them not suitable for exploitation.
 The activities of the human body generate a considerable amount of energy of different natures.
 Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, the kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, the body heat thermal energy \cite{Kim2014}, the strain energy from the skin deformation \cite{Jin2021} could be harvested for in-ear applications.
-The most relevant energy source for cochlear implants or hearing aids is the ear canal mechanical deformation as it is directly located in the area of the application.
+An interesting energy source for cochlear implants or hearing aids appears to be the ear canal mechanical deformation as it is directly located in the area of the application.
 Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes de ear canal geometry during mastication.
-The figure \ref{fig:TMJ_on_earcanal} schematizes the mechanical interaction between the temporomandibular joint and the ear canal when the jaw is opened and when it is closed.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={21cm 0cm 0cm 11.2cm},clip, width=0.9\linewidth]{figures/TMJ_on_earcanal.pdf}
-	\caption{Mechanical interaction between the temporomandibular joint and the ear canal during jaw movements \cite{Delnavaz2012}}
-	\label{fig:TMJ_on_earcanal}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Carioli \emph{et al.} used a personalized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016} (fig.
+Carioli \emph{et al.} then used a personalized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016} (fig.
 \ref{fig:molding}).
 These two mechanical deformations represent an available energy source that can be exploited.
-This study first quantified the flexion energy amount to $5$mJ per mastication with a standard deviation of $4.9$mJ.
-The radial compression energy was also estimated to $1.3$mJ with $1.5$mJ of standard deviation.
 Besides this work, the literature exposes two technological solutions adapted to the extraction of the mechanical deformation energy in the ear canal.
-\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The experimental prototype presented on figure \ref{fig:critias_piezo} was able to extract $44$µJ from a normal mastication cycle.
-The soft materials facilitate the bio-integration of the harvester but the PVDF low electromechanical coupling coefficient results in an energy conversion efficiency below $1\%$.
-A hydroelectromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
-The figure \ref{fig:critias_emag} shows the harvester components and experimental test setup.
+The soft materials facilitate the bio-integration of the harvester but the PVDF low electromechanical coupling coefficient could have led to poor energy conversion efficiency.
+A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
 The energy is extracted by a liquid filled earplug whose internal volume and pressure vary as a result of the radial compression of the ear canal internal walls during the jaw movements.
@@
 The energy was harvested by electromagnetic induction and experimentally evaluated at 0.2µJ per mastication cycle.
-The hydraulic energy extraction limits the energy source to the radial compression as the ear canal global flexion does not generate any volume variation in the earplug.
-The low conversion efficiency ($<1\%$) is a consequence of the use of electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}.
+The prototype appeared to be less efficient than the PVDF earplug.
+This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}.
 However, the hydraulic transmission interface allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume.
@@
 \ref{tab:parametres_lacher_free}).
-The correlations were made with iterative simulations of the global model by minimizing the error on these parameters.
-The converter experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{bo}$ have also been extracted from the recalibrated model.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={17cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/correlation_simu-exp_OB+GPA.pdf}
-	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres_lacher_free}.}
-	\label{fig:BDT_OB+GPA}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+The correlations were made with iterative simulations of the global model by minimizing the error between the simulated and the experimental parameters.
+The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{bo}$ of the converter have also been extracted from the recalibrated model.
+The simulation with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA}.
+The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
 %%%%%%%%%%%%%%%%%
@@
 	${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
-		$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
+	$\eta_{bo}$               & 75 \%                 & 12.9 \%   		\\
 	\bottomrule
@@
 %%%%%%%%%%%%%%%%%%%%%  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={17cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/correlation_simu-exp_OB+GPA.pdf}
+	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres_lacher_free}.}
+	\label{fig:BDT_OB+GPA}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    %///////////////////////////////////////////// 
+	\subsection{Analyze and summary}	
+	\label{subsec:Analyze and summary}
+    %/////////////////////////////////////////////
+
+According to figure \ref{fig:BDT_OB+GPA}, the experimental dynamics of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
+However, the performances of the experimental prototype proved to be below the values theoretically predicted (tab.
+\ref{tab:parametres électromécaniques}) even if the efficiency drop is consistent with the quality factor and the electromechanical coupling coefficient drop (eq.
+\ref{eq:eta_ob}).
+We identified two main factors that could have led to such results.
+
+First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw. 
+Then, small undulations have been observed on the BBs after fabrication, and they could also have gotten worse during the manipulation.
+
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{EXPERIMENTAL APPROACH FOR THE HV \mbox{DESIGN}}
+\label{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
 

### 2022-10-10 article_system.tex
update

@@
 
-\title{Ear canal dynamic motion piezoelectric energy harvester using a bistable oscillator cycled by coupled hydraulic switches made of collapsed flexible tubes.}
+\title{Ear canal dynamic motion piezoelectric energy harvester using a bistable resonator cycled by coupled hydraulic switches made of collapsed flexible tubes.}
 
@@
 Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes de ear canal geometry during mastication.
-Carioli \emph{et al.} then used a personalized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016} (fig.
-\ref{fig:molding}).
-These two mechanical deformations represent an available energy source that can be exploited.
-Besides this work, the literature exposes two technological solutions adapted to the extraction of the mechanical deformation energy in the ear canal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={6cm 0cm 0cm 10cm},clip, width=0.6\linewidth]{figures/molding.pdf}
-	\caption{(a) Earcanal in two extreme positions showing a global bending movement of the earcanal (b) Earcanal sectional view in two extreme positions showing a local compression area of the earcanal.
-\cite{Carioli2016}}
-	\label{fig:molding}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Delnavaz \emph{et al.} first developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013} (fig.
-\ref{fig:critias_piezo}).
-The earplug has been melted on the subject in order to maximize the contact surface with the ear canal.
+Carioli \emph{et al.} then used a customized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016}.
+These two mechanical deformations represent a potential energy source that can be exploited.
+
+Delnavaz \emph{et al.} developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013}.
+The earplug has been molded on the subject in order to maximize the contact surface with the ear canal.
 The harvester is capable of exploiting both the flexion and the compression energy sources.
-The experimental prototype presented on figure \ref{fig:critias_piezo} was able to extract $44$µJ from a normal mastication cycle.
+The experimental prototype was able to extract $44$µJ from a mastication cycle.
 The soft materials facilitate the bio-integration of the harvester but the PVDF low electromechanical coupling coefficient could have led to poor energy conversion efficiency.
 A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
-The energy is extracted by a liquid filled earplug whose internal volume and pressure vary as a result of the radial compression of the ear canal internal walls during the jaw movements.
-These variations put into motion a moving magnet translating in a water column surrounded by a copper coil.
-The energy was harvested by electromagnetic induction and experimentally evaluated at 0.2µJ per mastication cycle.
+The energy is extracted by a liquid filled earplug whose internal volume vary as a result of the radial compression of the ear canal internal walls during the jaw movements.
+This variation put into motion a moving magnet translating in a water column surrounded by a coil.
+The generated energy experimentally amounts to 0.2µJ per mastication cycle.
 The prototype appeared to be less efficient than the PVDF earplug.
 This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}.
-However, the hydraulic transmission interface allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume.
-The table \ref{tab:harvesters_ear} summarizes the existing harvesters that exploit the ear canal mechanical deformation energy.
-\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={18cm 0cm 0cm 8.7cm},clip, width=\linewidth]{figures/critias_piezo.pdf}
-	\caption{Piezoelectric energy harvester.
-Experimental setup (dimensions are in mm).
-(a) Flattened PVDF layer.
-(b) PVDF layer.
-(c) Prototype of piezo-earpiece.
-(d) Piezo-earpiece mounted on the headset.
-(e) Measuring setup.
-\cite{Delnavaz2013}}
-	\label{fig:critias_piezo}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={18cm 0cm 0cm 8.75cm},clip, width=\linewidth]{figures/critias_emag.pdf}
-	\caption{Hydroelectromagnetic energy harvester. (a) Test setup. (b) Energy harvesting module. \cite{Delnavaz2012}} 
-	\label{fig:critias_emag}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%
-\begin{table}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\resizebox{\linewidth}{!}{%
-	\begin{tabular}{ l  c  c  c}
-		\toprule
-		\multicolumn{1}{l}{\textbf{Harvester}}                        &
-		\multicolumn{1}{c}{\textbf{Harvested energy per mastication}} &
-		\multicolumn{1}{c}{\textbf{Reference}}                        \\
-		\midrule
-		Piezo earpiece        & $44$µJ 		 & \cite{Delnavaz2013} \\
-	    Hydroelectromagnetic  & $0.2$µJ      & \cite{Delnavaz2012} \\
-		Piezo sensor          & $0.1$µJ      & \cite{Carioli2018}  \\
-		\bottomrule
-	\end{tabular}}
-	\caption{Existing harvesters exploiting the ear canal deformation energy}
-	\label{tab:harvesters_ear}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%  
-Based on the literature, we propose a new technological solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion.
-The next section states on the energy source characterization and on the harvesting strategy we adopted.
+However, the hydraulic transmission allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume.
+
+Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion.
+The next section states on the hydraulic energy source characterization and on the harvesting strategy we adopted.
 Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle.
@@
     %/////////////////////////////////////////////
-The ear canal deflection energy is not a usual source because of the soft tissues and the low frequency of mastication.
+Human tissue requires soft flexible materials in order to extract the ear canal deflection energy without causing discomfort.
+However, flexible transducers admit low energy conversion efficiency as a part of the extracted energy is dissipated in the elastic non-active material.
+Additionally, the low frequency of mastication makes it difficult to use resonant structures that generally admit better conversion efficiencies than low frequency solutions \cite{Ashraf2011}.
 Thus, the traditional transducing methods are not suitable enough for the application.
 
-On one hand, the ear canal global bending energy is 5 times higher than the local compression energy.
-To date, the literature proposes only one way to harvest the bending energy from the ear canal wall, which is to use of soft materials as the piezoelectric earplug previously introduced \cite{Delnavaz2013}.
-The very low mechanical impedance of the soft tissue in fact limits the use of more effective rigid piezoelectric materials.
-
-On the other hand, the hydraulic extraction strategy proposed in \cite{Delnavaz2012} only exploits the local compression energy.
-However, it allows to transmit the energy outside the ear canal and benefit so from larger effective space.
+To date, the best solution proposed in the literature consists on using soft materials as the piezoelectric PVDF earplug previously introduced \cite{Delnavaz2013}.
+The low mechanical impedance of the soft tissue in fact limits the use of more effective rigid piezoelectric materials.
+
+The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but allows to transmit the energy outside the ear canal and benefit so from larger effective space.
 The latter is in fact essential as it becomes then possible to implement an impedance adaption stage and more effective transducing methods that could not fit directly inside the ear canal restricted volume.
+In fact, Marin \emph{et al.} demonstrated that the power generated by piezoelectric or electromagnetic transducers is as much better as the effective volume of transducing material is high \cite{Marin2011}.
 The present work is then based on the exploitation of the ear canal by a liquid filled earplug.
-As energy source, the latter can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
+As energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
 In order to optimize the energy extraction, the earplug must fit the ear canal wall.
-Turcot \emph{et al.} demonstrated that the initial pressurization must be at a minimum of 14kPa to achieve a good fit.
+Turcot \emph{et al.} demonstrated that the initial pressurization must reach a minimum of $14$kPa to achieve a good fit \cite{TURCOT2011}.
 Bouchard-Roy \emph{et al.} studied the dynamic pressure variation inside the earplug for different initial pressurization levels \cite{Bouchard-Roy2020}.
-A maximum of $\text{max}(\Delta p_{ear})=12$kPa of dynamic pressure variation , with a $28$kPa of initial pressurization, has been noted during the mastication for seven subjects.
-Besides, the temporal evolution of the volume variation $\Delta V_{ear}$ has been estimated in \cite{Delnavaz2012} and the result for one mastication cycle is presented on figure \ref{fig:deltaV_ear}.
+A maximum of $\text{max}(\Delta p_{ear})=12$kPa of dynamic pressure variation, with a $28$kPa of initial pressurization, has been noted during the mastication for seven subjects.
+Besides, the temporal evolution of the volume variation $\Delta V_{ear}$ has been estimated in \cite{Delnavaz2012} and the result for a mastication cycle is presented on figure \ref{fig:deltaV_ear}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\includegraphics[trim={20.5cm 0cm 0cm 10.8cm},clip, width=0.4\textwidth]{figures/deltaV_ear.pdf}
-	\caption{Ear canal volume variation for one mastication cycle \cite{Delnavaz2012}}
+	\caption{Ear canal volume variation for one mastication cycle}
 	\label{fig:deltaV_ear}
@@
 Thus, the evolution of the volume variation $\Delta V_{ear}$ is not well known as a function of the pressure variation $\Delta p_{ear}$.
-However, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with a 28kPa pressurized earplug and a maximum volume variation of $\Delta V_{ear,m}=60$mm$^3$.
-$p_c$ stands for the comfort pressure by estimating that the user could feel discomfort if $\Delta p_{ear}>p_c$.
-The energy estimation assumes that the earplug is a perfect flow rate source, which is an optimistic hypothesis leading to $0.9$mJ available from one mastication.
+Then, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with the maximum values of $\Delta p_{ear}$ et $\Delta V_{ear}$ that have been recorded, i.e.
+$p_c=12kPa$ and $\Delta V_{ear,m}=60$mm$^3$.
+$p_c$ stands for the comfort pressure by assuming that the user could feel discomfort if $\Delta p_{ear}>p_c$.
+The energy estimation presumes that the earplug is a perfect flow rate source, which is a theoretical hypothesis leading to $0.9$mJ available from one mastication.
 Based on 2200 mastication cycles per day, according to \cite{Goll2011}, there would be $2$mJ available per day, per ear.
-This amount of energy could theoretically enhance supply 23.5\% of the 17J of needed for the state of the art of cochlear implants \cite{Kulah2022}.
+This amount of energy could theoretically enhance supply $23.5$\% of the $17$J of needed for the state of the art of cochlear implants \cite{Kulah2022}.
 Further research in both domains related to hearing aids and energy harvesting could lead to fully autonomous devices in the future.
@@
     %/////////////////////////////////////////////
-The application is not suitable for magnetic interactions for two major reasons.
-Magnetic fields admit high non-linear properties at small scales and their effectiveness decreases as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
-The piezoelectric ceramics yet appear like good candidates, but they can not be easily used because of their high stiffness.
-For this reason, and also because of the higher conversion efficiency of resonant structures, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021}.
-These structures are commonly used for broadband energy harvesting.
-A majority of the papers with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
-Stoppers however dissipate energy and demand maintenance with time, in order to replace rubbing parts.
-To overcome this drawback, alternative solutions use mechanically bistable oscillators (BO) to perform frequency-up without any rubbing parts \cite{Vocca2012}.
-Recent advances
-led to the development and optimization of  bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}.
-They show enhanced performances due to high electromechanical coupling and broadband efficiency.
-Preliminary calculations based on the Duffing equation defining the BO mechanical behavior \cite{Tseng1971}, and the linearity of piezoelectric beams, offer a comparison tool to determine the best technological approach to maximize the harvested energy from the hydraulic source.
-Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced.
+Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources.
+In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
+Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.
+Thus, piezoelectric ceramics appear like good candidates, but they can not be easily used because of their high stiffness and their high resonance frequencies (>$1.57$Hz).
+Therefore, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of piezoelectric ceramic transducers.
+A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
+Stoppers however dissipate energy.
+Alternative solutions use mechanically bistable resonators (BR) to perform frequency-up \cite{Vocca2012}.
+Recent works led to the development and optimization of  bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}.
+They show enhanced performances due to high electromechanical coupling.
+
+We can estimate the best choice maximizing the energy extraction from the hydraulic source.
+Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
 To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer.
-The hydraulic-mechanic interface is chosen to be a hydraulic cylinder.
-On one hand, the best linear spring is capable of storing/extracting a maximum of $0.5\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$) if actuated by the source through a hydraulic cylinder.
-On the other hand, a BO type non-linear spring is inherently capable of extracting more than $65\%$ from the same source.
+The hydraulic-mechanic interface can be a hydraulic cylinder.
+In this way, the best linear resonator can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
+Furthermore, BR usually admit non-linear elastic behavior.
+For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BO as a promising solution for our application. 
+Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BR as a promising solution for our application. 
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 It uses a liquid filled earplug to transmit the energy outside the ear canal and benefit so from larger effective space.
-To maximize the efficiency, the system integrates a frequency-up conversion stage performed by a bistable oscillator (BO).
+To maximize the efficiency, the system integrates a frequency-up conversion stage performed by a bistable resonator (BR).
 The latter implements an amplified piezoelectric generator (APG) made of a flextensional elastic APX4 steel structure containing stacked lead zirconate titanate (PZT) ceramics (fig.
 \ref{fig:APG}).
-The electromechanical converter composed of the BO and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Guo2019}.
+The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Guo2019}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 Then, during a mastication cycle, the TMJ compresses the ear canal wall and expels so the fluid outside the earplug.
-The HVs ensure to led the fluid alternatively to each HC in order to actuate the BO mass back and forward.
-The hydraulic amplifier adapts the cylinders stroke to the available earplug flow rate and also adapts the mechanical impedance of the BO to the mechanical impedance of the ear canal wall.
-
-The BO mass has two stable equilibrium positions, $x_m = x_0$ and $x_m = -x_0$.
+The HVs ensure to led the fluid alternatively to each HC in order to actuate the BR mass back and forward.
+The hydraulic amplifier adapts the cylinders stroke to the available earplug flow rate and also adapts the mechanical impedance of the BR to the mechanical impedance of the ear canal wall.
+
+The BR mass has two stable equilibrium positions, $x_m = x_0$ and $x_m = -x_0$.
 The harvester operates on two major phases.
-The first consists on the BO mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$.
-During the second phase the mass goes oscillate around the opposite stable equilibrium position until it stops, while a portion of the oscillatory energy is converted in electricity by the GPA.
+The first consists on the BR mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$.
+During the second phase the mass goes oscillate around the opposite stable equilibrium position until it stops, while a portion of the resonatory energy is converted in electricity by the GPA.
 The mass then moves backward during the next mastication, completing so the harvester cycle.
@@
 	\includegraphics[trim={20cm 0cm 0cm 10.75cm},clip, width=\linewidth]{figures/HV_actuation_detail.pdf}
-	\caption{Contact detail between a HV and the BO mass} 
+	\caption{Contact detail between a HV and the BR mass} 
 	\label{fig:HV_actuation_detail}
@@
 A technological solution for this role is to use a flexible tube buckled by bending.
-The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BO environment.
+The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment.
 The valve is composed of a flexible tube connected between a rigid part of the hydraulic circuit and a fixed one.
-The BO mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
+The BR mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
 Consequently, a pressure loss is generated through the valve in buckled position.
-Thus, a HV is considered closed when the BO mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
-Two HVs symmetrically placed on each side of the $\vec{x}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BO mass position.
+Thus, a HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
+Two HVs symmetrically placed on each side of the $\vec{x}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position.
 The HV technological choice is motivated by three major arguments.
 First, the absence of electromechanical transduction minimizes the energy losses for the valve operation.
-Then, the post-buckling softening of the bent tube minimizes the mechanical impact on the BO mass dynamic operation.
+Then, the post-buckling softening of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
 Finally, it is well adapted at the millimetric application scale.
@@
 Two coupled subsystems are considered.
-The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BO + APG) under the mechanical influence of a HV and a HC.
+The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
 Then, the subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.
@@
 The different schematized rigid bodies all designated in the table \ref{tab:Designation of rigid bodies}.
-The BO is represented by 4 identical arms articulated by 8 hinges and a central mass.
+The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
 The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, indicative of the piezoelectric transduction, expressed by the equation \ref{eq:k2_def}.\\
@@
 \begin{itemize}
-	\item The only mass considered is the BO mass (2).
+	\item The only mass considered is the BR mass (2).
 	\item All parts are infinitely rigid beside the APG (4).
 	\item The hinges are considered elastic. They are defined by their rotational stiffness $K_{\varphi}$ and their mechanical damping is included in the global viscous damping coefficient $\mu$.
-	\item The contact between the BO mass (2) and the HC piston head (5) is considered permanent.
+	\item The contact between the BR mass (2) and the HC piston head (5) is considered permanent.
 	\item We assume the small-angle approximation with \mbox{$x_0<<L$}. 
@@
 		0	& Fixed frame      	  	\\  
-		1	& BO arm      	  	\\  
-		2	& BO mass     	\\
+		1	& BR arm      	  	\\  
+		2	& BR mass     	\\
 		3	& HC piston head	\\
@@
 
-By isolating the BO mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium with respect to the different external forces.
+By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium with respect to the different external forces.
 The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA} where the provenance of the different terms is highlighted.
-The BO mechanical equilibrium took aside contains the mass inertial term, a non-linear stiffness depending on $x_m$, the hinges stiffness and viscous losses.
+The BR mechanical equilibrium took aside contains the mass inertial term, a non-linear stiffness depending on $x_m$, the hinges stiffness and viscous losses.
 This expression has also been demonstrated by the Lagrange method in past works \cite{Liu2013}.
@@
 With the small-angle approximation, the system equation \ref{eq:OB+GPA+VH+piston} defines the electromechanical behavior of the harvester.
-The HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BO mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.
+The HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.
 
@@
 	\item The hydraulic actuation is considered quasi-static (QS) in front
-	the oscillation frequency of the BO.
+	the oscillation frequency of the BR.
 \end{itemize}
@@
 \begin{align}
-	-F_{pis} & = F_{bo}\\
+	-F_{pis} & = F_{br}\\
 	-F_{pis} & = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr) - F_f
@@
 Where $p_{in}$ is the initial pressurization, $a_h$ is the hydraulic amplification ratio, $q$ the flow rate and $Cf$ the pressure loss coefficient of a HV.
-The latter will depend on the HV bending angle $\theta$ and therefore on the BO mass position $x_m$ (fig.
+The latter will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
 \ref{fig:HV_actuation_detail}).
@@
 
-The maximum energy extractable with the BO through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ }to \mbox{$x_m=0$}.
+The maximum energy extractable with the BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ }to \mbox{$x_m=0$}.
 Knowing that it is equal to 65\% of the upper limit of the available hydraulic energy (eq.
 \ref{eq:max_hydraulic_energy} $\&$ fig.
-\ref{fig:OB_vs_LINEAR}), we can set the BO buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}.
+\ref{fig:OB_vs_LINEAR}), we can set the BR buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}.
 The harvester is thus optimized depending on the energy source.
@@
 Two additional coupled requirements allow the system operation by setting the amplification level $a_h$.
-First, the available fluid must be enough to ensure the HC stroke from its equilibrium position until the BO mass reaches \mbox{$x_m=0$} (eq.
+First, the available fluid must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
 \ref{eq:contrainte_course}).
-Then, the BO mechanical impedance on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
+Then, the BR mechanical impedance on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
 At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to ensure the user comfort.
@@
 \end{align}
-Regarding the BO symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
+Regarding the BR symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
 
@@
 
-The first phase consists on pushing on the BO mass to store potential energy, until the mass reaches $x=0$.
-During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BO counter-reaction force.
+The first phase consists on pushing on the BR mass to store potential energy, until the mass reaches $x=0$.
+During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BR counter-reaction force.
 The second phase begins after the mass crosses the $x_m=0$ position.
@@
 The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent.
-The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG.
+The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the resonatory mechanical energy is converted in electricity by the APG.
 The flow rate goes toward the right piston when $r_{Cf}$ is set at a minimum value of \mbox{$(r_{Cf})_{min}=26$}.
@@
 The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with 20µJ harvested from one mastication.
-The energy losses are mostly located in the BO stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BO architectures \cite{Liu2013}.
+The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
 The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e.
@@
 
-The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BO mass.
+The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BR mass.
 Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
@@
     %/////////////////////////////////////////////
-The device heart is the electromechanical converter composed of the BO implementing the APG and therefore, they have been designed with respect to space requirements.
-We opted for a monobloc structure with blades in order to optimize the oscillator quality factor by avoiding screw assemblies.
-Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable oscillator CAD that has been fabricated by electrical discharge machining (EDM).
+The device heart is the electromechanical converter composed of the BR implementing the APG and therefore, they have been designed with respect to space requirements.
+We opted for a monobloc structure with blades in order to optimize the resonator quality factor by avoiding screw assemblies.
+Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable resonator CAD that has been fabricated by electrical discharge machining (EDM).
 The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations.
@@
 The local thickenings at the midspan of the blades are intended to facilitate the fabrication and also to maximize the BB compression stiffness that maximizes the electromechanical coupling of the harvester, as we show in the following sections.
-The geometrical and mechanical parameters of the BO are referenced in table \ref{tab:parametres_lames}.
+The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
 The following sections describe the design method that led to the dimensions of the blades that depend on our needs.
@@
 		\end{tabular}}
-	\caption{Definitions and values of the fabricated BO}
+	\caption{Definitions and values of the fabricated BR}
 	\label{tab:parametres_lames}
@@
 	\includegraphics[trim={19.2cm 0cm 0cm 5cm},clip,width=.7\linewidth]{figures/monobloc_face.pdf}
-	\caption{Face transparency view of the monobloc BO CAO}
+	\caption{Face transparency view of the monobloc BR CAO}
 \label{fig:monobloc_face}
@@
     %///////////////////////////////////////////// 
-	\subsection{BO blades design}	
-	\label{subsec:BO blades design}
+	\subsection{BR blades design}	
+	\label{subsec:BR blades design}
     %/////////////////////////////////////////////
@@
 
-$K_{bb}$ is for its part verified through a FEM generated with the BO CAD on ANSYS Workbench.
+$K_{bb}$ is for its part verified through a FEM generated with the BR CAD on ANSYS Workbench.
 Figure \ref{fig:fem_statique} presents the model and the initial and boundary conditions used for the study.
@@
 	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
-	\caption{BO finit element model with initial and boundary conditions for a static study}
+	\caption{BR finit element model with initial and boundary conditions for a static study}
 \label{fig:fem_statique}
@@
 
-In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BO operation.
+In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BR operation.
 Based on the precedent FEM static model (fig.
@@
 The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity.
-Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BO, as presented on figure \ref{fig:buckling_limit}.
+Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BR, as presented on figure \ref{fig:buckling_limit}.
 The preliminary simulated case presented in the previous section is well located in the preferable domain where there is no undesirable buckling modes.
@@
     %/////////////////////////////////////////////
-The BO has been fabricated and mounted and the APG has been implemented on it.
+The BR has been fabricated and mounted and the APG has been implemented on it.
 The experimental test bench for the electromechanical characterizations of the resultant converter is presented on figure \ref{fig:BDT_OB+GPA}.
@@
 The correlations were made with iterative simulations of the global model by minimizing the error between the simulated and the experimental parameters.
-The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{bo}$ of the converter have also been extracted from the recalibrated model.
+The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ of the converter have also been extracted from the recalibrated model.
 The simulation with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA}.
@@
 	${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
-	$\eta_{bo}$               & 75 \%                 & 12.9 \%   		\\
+	$\eta_{br}$               & 75 \%                 & 12.9 \%   		\\
 	\bottomrule

### 2022-10-11 article_system.tex
update

@@
 To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer.
-The hydraulic-mechanic interface can be a hydraulic cylinder.
-In this way, the best linear resonator can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
-Furthermore, BR usually admit non-linear elastic behavior.
+The hydraulic-mechanic interface can be a hydraulic cylinder (HC).
+It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication.
+Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.6\linewidth]{figures/hydraulic_mechanic_interface.pdf}
+	\caption{Hydraulic source exploitation depending on the mechanical load}
+	\label{fig:hydraulic_mechanic_interface}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The potential energy then stored in a linear resonator can be expressed as follows :
+\begin{equation}
+	Ep_{lin} = \dfrac{K_{lin}\ x_{hc}^2}{2}
+\end{equation}
+Where $K_{lin}$ models the linear resonator stiffness and $x_{hc}$ the HC piston stroke.
+During the actuation, the forces applied on each side of the HC are equal, which models the hydraulic-mechanic interface (eq.
+\ref{eq:hydraulic-mechanic_interface}).
+\begin{equation}
+	\Delta p_{ear}\ S_{hc} = K_{lin}\ x_{hc}
+	\label{eq:hydraulic-mechanic_interface}
+\end{equation}
+theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
+Yest, BRs usually admit non-linear elastic behavior.
 For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.

### 2022-10-11 article_system.tex
update

--- 2022-10-10 article_system.tex
@@
 We can estimate the best choice maximizing the energy extraction from the hydraulic source.
-Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
 To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer.
-The hydraulic-mechanic interface can be a hydraulic cylinder.
-In this way, the best linear resonator can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
-Furthermore, BR usually admit non-linear elastic behavior.
+The hydraulic-mechanic interface can be a hydraulic cylinder (HC).
+It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication.
+Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$.
+During the low frequency actuation, the forces applied on each side of the HC piston are equal.
+Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+	\Delta p_{ear}\ S_{hc} = K_{s}\ x_{m}
+	\label{eq:hydraulic-mechanic_interface}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+	\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.7\linewidth]{figures/hydraulic_mechanic_interface.pdf}
+	\caption{Hydraulic source exploitation depending on the mechanical load}
+	\label{fig:hydraulic_mechanic_interface}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
+\begin{equation}
+	Ep_{lin} = \dfrac{K_s\ x_{m}^2}{2} = \dfrac{\Delta p_{ear} \Delta V_{ear}}{2}
+\end{equation}
+Thus, the linear solution can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
+
+Yet, BRs usually admit non-linear elastic behavior.
 For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
-	\caption{Hydraulic source exploitation depending on the mechanical load}
-	\label{fig:OB_vs_LINEAR}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Hence, the absence of rubbing parts and the optimal energy extraction shed light on a BR as a promising solution for our application. 
+Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
+
+% Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!htbp]
+% 	\centering
+% 	\captionsetup{justification=centering}
+% 	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
+% 	\caption{Hydraulic source exploitation depending on the mechanical load}
+% 	\label{fig:OB_vs_LINEAR}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system.
-It uses a liquid filled earplug to transmit the energy outside the ear canal and benefit so from larger effective space.
-To maximize the efficiency, the system integrates a frequency-up conversion stage performed by a bistable resonator (BR).
-The latter implements an amplified piezoelectric generator (APG) made of a flextensional elastic APX4 steel structure containing stacked lead zirconate titanate (PZT) ceramics (fig.
+It uses a liquid filled earplug to transmit the energy outside the ear canal.
+To maximize the efficiency, the system integrates a frequency-up conversion stage obtained by a BR.
+The latter is associated with an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure containing stacked lead zirconate titanate (PZT) ceramics (fig.
 \ref{fig:APG}).
-The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Guo2019}.
+The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 
-The electromechanical converter is actuated, by two hydraulic cylinders (HC), with the hydraulic energy transmitted from the liquid filled earplug, through a pressure separator, a hydraulic amplifier and two hydraulic valves (HV).
-
-To maximize the mechanical energy transfer between the ear canal and the earplug, the latter is lightly pressurized.
-A minimum of 14kPa is needed in order to fit the earplug to the ear canal wall \cite{Delnavaz2013}.
-The pressure separator ensures that this initial pressurization does not interfere on the system operation.
-Then, during a mastication cycle, the TMJ compresses the ear canal wall and expels so the fluid outside the earplug.
+The electromechanical converter is actuated, by two hydraulic cylinders (HC), with the hydraulic energy transmitted from the liquid filled earplug, through a hydraulic amplifier (HA) and two hydraulic valves (HV).
+
+During a mastication cycle, the TMJ compresses the ear canal wall and expels so the fluid outside the earplug.
 The HVs ensure to led the fluid alternatively to each HC in order to actuate the BR mass back and forward.
@@
 \centering
+\resizebox{0.8\linewidth}{!}{%
 	\begin{tabular}{ c | c }
@@
 		\bottomrule
-	\end{tabular}
+	\end{tabular}}
 	\caption{Designation of rigid bodies}

### 2022-10-12 article_system.tex
update

@@
 	\begin{center}
-		\begin{subfigure}[t]{0.6\linewidth}
-			\captionsetup{justification=centering}
-			\includegraphics[trim={16cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/APG_schema.pdf}
+		\begin{subfigure}[t]{0.5\linewidth}
+			\captionsetup{justification=centering}
+			\includegraphics[trim={13cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/APG_schema.pdf}
 			\caption{Detailed schema}
@@
 		\hfillx
-		\begin{subfigure}[t]{0.29\linewidth}
+		\begin{subfigure}[t]{0.21\linewidth}
 			\captionsetup{justification=centering}
@@
 
-During a mastication cycle, the TMJ compresses the ear canal wall and expels so the fluid outside the earplug.
-The HVs ensure to led the fluid alternatively to each HC in order to actuate the BR mass back and forward.
-The hydraulic amplifier adapts the cylinders stroke to the available earplug flow rate and also adapts the mechanical impedance of the BR to the mechanical impedance of the ear canal wall.
-
-The BR mass has two stable equilibrium positions, $x_m = x_0$ and $x_m = -x_0$.
+During a mastication cycle, the TMJ compresses the ear canal wall and expels the fluid out of the earplug.
+The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth.
+The HA adapts the both cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig.
+\ref{fig:system_presentation}).
+
+The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$x_m = -x_0$}.
 The harvester operates on two major phases.
 The first consists on the BR mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$.
-During the second phase the mass goes oscillate around the opposite stable equilibrium position until it stops, while a portion of the resonatory energy is converted in electricity by the GPA.
-The mass then moves backward during the next mastication, completing so the harvester cycle.
+During the second phase the mass reaches and oscillates around the opposite stable equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the GPA.
+The mass will move backward when the next mastication will occur and complete the harvester cycle.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={20cm 0cm 0cm 10.75cm},clip, width=\linewidth]{figures/HV_actuation_detail.pdf}
+	\includegraphics[trim={20.5cm 0cm 0cm 11.5cm},clip, width=0.8\linewidth]{figures/HV_actuation_detail.pdf}
 	\caption{Contact detail between a HV and the BR mass} 
@@
 
-In order to maximize the harvested energy we must minimize the energy consumed by the HVs.
-A technological solution for this role is to use a flexible tube buckled by bending.
+A technological solution for the HV is to use a flexible tube buckled by bending.
 The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment.
-The valve is composed of a flexible tube connected between a rigid part of the hydraulic circuit and a fixed one.
-The BR mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
+The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed parts.
+It is in contact with the mass at the T point.
+The mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
 Consequently, a pressure loss is generated through the valve in buckled position.
-Thus, a HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
-Two HVs symmetrically placed on each side of the $\vec{x}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position.
+The HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
+This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
+Two HVs symmetrically placed on each side of the $\vec{z}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position.
 The HV technological choice is motivated by three major arguments.
-First, the absence of electromechanical transduction minimizes the energy losses for the valve operation.
-Then, the post-buckling softening of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
-Finally, it is well adapted at the millimetric application scale.
+First, the absence of electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
+Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
+Finally, it seems well adapted for integration purpose for millimetric application scale.
 
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-The harvester is a multyphisic system composed of hydraulic, mechanical, and electrical components.
-This section presents a global multiphysic model describing the theoretical system operation.
+The harvester is a multiphysic system composed of hydraulic, mechanical, and electrical components.
+This section presents the global multiphysic model describing the system theoretical operation.
 Two coupled subsystems are considered.
 The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
-Then, the subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.
-Finally, the section \ref{subsec:Global model simulation} exposes the numerical simulation of the designed multiphysic coupled model.
+Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.
+
+This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves.
+In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
+Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier.
+These hydraulic components will rather be considered on further work.
 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{figures/schema_cinematique1.pdf}
-	\caption{Cinematic schema of the of the electromechanical converter under the mechanical influence of a HV and a HC}
+	\caption{Kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC}
 	\label{fig:schema_cinematique1}
@@
 
-The figure \ref{fig:schema_cinematique1} shows the cinematic schema of the electromechanical converter under the mechanical influence of a HV and a HC.
-The different schematized rigid bodies all designated in the table \ref{tab:Designation of rigid bodies}.
+The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC.
+The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
 The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
-The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, indicative of the piezoelectric transduction, expressed by the equation \ref{eq:k2_def}.\\
+The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction, defined by the equation \ref{eq:k2_def}.\\
 The model is based on the following hypotheses:
@@
 	\item The only mass considered is the BR mass (2).
-	\item All parts are infinitely rigid beside the APG (4).
-	\item The hinges are considered elastic. They are defined by their rotational stiffness $K_{\varphi}$ and their mechanical damping is included in the global viscous damping coefficient $\mu$.
-	\item The contact between the BR mass (2) and the HC piston head (5) is considered permanent.
-	\item We assume the small-angle approximation with \mbox{$x_0<<L$}. 
+	\item All parts are infinitely rigid except for the APG (4).
+	\item The hinges are considered elastic: They are defined by their rotational stiffness $K_{\varphi}$
+	\item The mechanical damping of the hinges is included in the global viscous damping coefficient $\mu$.
+	\item The contact between the BR mass (2) and the HC piston head (5) is considered permanent for $0 < x < x_0$.
+	\item \mbox{$x_0 \ll L$}. 
 \end{itemize}
@@
 \centering
-\resizebox{0.8\linewidth}{!}{%
+\resizebox{0.6\linewidth}{!}{%
 	\begin{tabular}{ c | c }
@@
 	\end{tabular}}
-	\caption{Designation of rigid bodies}
+\caption{Definition of figure \ref{fig:schema_cinematique1} bodies}
 \label{tab:Designation of rigid bodies}
@@
 
-By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium with respect to the different external forces.
-The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA} where the provenance of the different terms is highlighted.
-The BR mechanical equilibrium took aside contains the mass inertial term, a non-linear stiffness depending on $x_m$, the hinges stiffness and viscous losses.
-This expression has also been demonstrated by the Lagrange method in past works \cite{Liu2013}.
-The first term introduced by the HV is related to its rotationnal stiffness and the second term is related to the friction losses at the contact point $T$ (fig.
+By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium.
+The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}.
+The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses.
+The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (fig.
 \ref{fig:HV_actuation_detail}).
-A dry friction model is choose to describe the nature of the contact between the two components.
-Thus, $F_f$ will depend on a dry friction coefficient $\mu_f$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$ (eq.
-\ref{eq:Dry_friction}).
-The force $F_{pis}$ induced by the piston head of the HC on the OB mass will depend on hydraulic parameters.
-The hydro-mechanical coupling is highlighted later by the equation \ref{eq:equilibre_dynamique_piston_ouvert}.
-\begin{equation}
-	F_f = \mu_f \text{sign}(\dot{x}_m)
-	\label{eq:Dry_friction}
-\end{equation}
-
-The electrical power generated by the APG is dissipated in a load resistor $R_{ch}$ calculated with an adaptive impedance matching expressed by the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
+A dry friction model is chosen to describe the dissipation effect of the contact.
+The rubbing efforts depend on a dry friction coefficient $\nu_f$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
+The pressure $p_{ac}$ induces the HC hydraulic force and the coefficient $\mu_c$ models the viscous friction at the sealing gasket.
+The hydro-mechanical coupling will be detailed later.
+
+The electrical power generated by the APG is dissipated in a load resistor $R_{ch}$ calculated with an adaptive impedance matching expressed in the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
 \begin{equation}
@@
 \end{equation}
-Thus, the equation governing the electrical behavior of the APG is :
+Thus, the electrical equation of the APG is :
 \begin{equation}
@@
 \end{equation} 
-With the small-angle approximation, the system equation \ref{eq:OB+GPA+VH+piston} defines the electromechanical behavior of the harvester.
-The HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.
-
+Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup.
+Also, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{equation}
-\overbrace{\ m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) 
-							-\mu \dot{x}_m
-							-\frac{4K_{\varphi}\varphi}{L}\ }^{OB}
-			\underbrace{\ -2\alpha U_p \tan(\varphi)\ }_{APG}		 
-			\overbrace{\ -\dfrac{K_{HV}\theta}{a} - F_f\ }^{HV}
-			\underbrace{\ -F_{pis}\ }_{HC}
+\begin{figure*}[!htb]
+\begin{equation}
+ m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
+				\ -2\alpha U_p \tan(\varphi)
+				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - \nu_f \text{sign}(\dot{x}_m)
+				\  - p_{ac}\ S_{hc} - \mu_{c}\ \dot{x}_m
 \label{eq:OB-GPA}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{equation}
-% \begin{small}
-	\begin{dcases}
-\ddot{x}_m = - \frac{2K{x_0}^2}{mL^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)
-			   x_m - \frac{\mu}{m}\dot{x}_m - \frac{2\alpha U_p\ x_m}{mL}
-			-\frac{K_{VH}(x_m)\theta(x_m)}{ma}
-			-\frac{F_f}{m}
-			-\frac{F_{pis}}{m} \\
-\dfrac{U_p}{R_{ch}} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p
-	\end{dcases}
-	\label{eq:OB+GPA+VH+piston}	
-% \end{small}
-\end{equation}
-\end{figure*}
-% \FloatBarrier
+\begin{equation}
+x_m = \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
+				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr)
+\label{eq:theta_fonction_de_xm}
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure*}
+% \begin{equation}
+% % \begin{small}
+% 	\begin{dcases}
+% \ddot{x}_m = - \frac{2K{x_0}^2}{mL^2}\Biggl[\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr )+ \dfrac{8K_{\varphi}}{L^2}\Biggr]x_m 
+% 			 - \frac{K_{VH}(x_m)\theta(x_m)}{ma}
+% 			 - \frac{\mu+\mu_c}{m}\dot{x}_m  - \nu_f \text{sign}(\dot{x}_m)
+% 			 - \frac{2\alpha U_p\ x_m}{mL}
+% 			 - p_{ac}\ S_{hc} \\
+% x_m = \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
+% 				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr)\\
+% \dfrac{U_p}{R_{ch}} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p 
+% 	\end{dcases}
+% 	\label{eq:OB+GPA+VH+piston}	
+% % \end{small}
+% \end{equation}
+% \end{figure*}
+% % \FloatBarrier
+% %%%%%%%%%%%%%%%%%%%%%%%
     %///////////////////////////////////////////// 
@@
     %/////////////////////////////////////////////
-This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves.
-In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
-Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier.
-These hydraulic components will rather be considered on further work.
-
-In order to model the coupled behavior of the two hydraulic branches, we will use the index "$o$" for the open branch and the index "$c$" for the closed one.
+
+In order to model the coupled behavior of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
 The following hypotheses will be considered :
 \begin{itemize}
-	\item The fluid is incompressible and Newtonian.
-	\item The hydraulic circuit is non-deformable (no volume change) and there is no leakage.
-	\item The hydraulic actuation is considered quasi-static (QS) in front
-	the oscillation frequency of the BR.
+	\item The flow is incompressible and Newtonian.
+	\item The hydraulic circuit is rigid (no volume change) and there is no leakage.
+	\item The hydraulic actuation is considered quasi-static considering the oscillation frequency of the BR.
 \end{itemize}
-The projection on the $\vec{x}$ axis of the Newtons 2$^{nd}$ law applied respectively to each HC moving piston gives us their mechanical equilibrium as follows :
+The mechanical equilibrium is :
 \begin{align}
-	\text{Opened cylinder ~}& \left\{~
-	-F_{pis} - p_{oc}\ S_{c} - \lambda_{c}\ \dot{x}_{oc} = 0
+	\text{Active cylinder ~}& \left\{~
+	F_{br} - p_{ac}\ S_{hc} - \mu_{c}\ \dot{x}_m = 0
 	\right.
 	\label{eq:equilibre_dynamique_piston_ouvert}\\
-	\text{Closed cylinder ~}& \left\{~
-	p_{cc}\ S_{c} - \lambda_{c}\ \dot{x}_{cc} = 0
+	\text{Inactive cylinder ~}& \left\{~
+	p_{ic}\ S_{hc} - \mu_{c}\ \dot{x}_{ic} = 0
 	\right.
@@
 \end{align}
-Where $p_c$ is the HC chamber pressure and $x_c$ its moving piston position.
-$F_{pis}$ accounts for the OB counter-reaction on the HC.
-Thus, with the QS assumption, it can be derived from equation \ref{eq:OB+GPA+VH+piston} and expressed as follows :
+Where $p_c$ is the HC chamber pressure and $x_{ic}$ the piston position of the inactive HC piston.
+$F_{br}$ accounts for the OB counter-reaction on the HC.
+With the QS actuation assumption, it can be derived from equation \ref{eq:OB-GPA} and expressed as follows :
 \begin{align}
-	-F_{pis} & = F_{br}\\
-	-F_{pis} & = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr) - F_f
+	F_{br} = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr)
 	\label{eq:F_OB_xxxxxx}
 \end{align}
-Then, by juxtaposing the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
+The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
+\ref{fig:HV_actuation_detail}).
+$Cf$ will be as more important as $x_m$ increases.
+It is minimal when the HV is unbent and worth $Cf_0$.
+The literature does not provide the constitutive relation between $x_m$ and $Cf$, thus we preliminarily assume that it is linear and defined as follows :
 \begin{align}
-	\text{Opened branch ~}& \left\{~
-	p_{ear} = p_{in} + \dfrac{1}{a_h}\biggl(p_{oc} + Cf_0 {q_0}^2 \biggr)
+Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m 
+\label{eq:Cf(x_m)_linear}
+\end{align}
+Where $Cf_c=Cf(\pm x_0)$. Regarding the BR symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
+
+By the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
+\begin{align}
+	\text{Active branch ~}& \left\{~
+	p_{ear} = \dfrac{1}{a_h}\biggl(p_{ac} + Cf_0 {q_a}^2 \biggr)
 	\right.
 	\label{eq:Bernoulli_piston_ouvert}\\
-	\text{Closed branch ~}& \left\{~
-	p_{ear} = p_{in} + \dfrac{1}{a_h}\biggl(p_{cc} + Cf(x_m) {q_f}^2 \biggr)
+	\text{Inactive branch ~}& \left\{~
+	p_{ear} = \dfrac{1}{a_h}\biggl(p_{ic} + Cf(x_m) {q_i}^2 \biggr)
 	\right.
@@
 \end{align}
-Where $p_{in}$ is the initial pressurization, $a_h$ is the hydraulic amplification ratio, $q$ the flow rate and $Cf$ the pressure loss coefficient of a HV.
-The latter will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
-\ref{fig:HV_actuation_detail}).
-$Cf$ will be as more important as the $x_m$ increases.
-It is minimal when the HV is unbent and worth $Cf_0$.
-
-Also, the no leakage assumption imposes that all the outgoing fluid from the earplug is contained in the two hydraulic branches (eq. \ref{eq:conservation_masse}).
-\begin{equation}
-	q_{ear} = q_o + q_f
+Where $a_h$ is the hydraulic amplification ratio and $q$ the flow rate.
+
+The no leakage assumption imposes that all the fluid exiting the earplug is contained in the two hydraulic branches (eq. \ref{eq:conservation_masse}).
+\begin{equation}
+	q_{ear} = \dot{\Delta V_{ear}} = q_a + q_i
 	\label{eq:conservation_masse}
 \end{equation}
-Moreover, the same previous hypothese requires that all the fluid entering the HC results on a piston displacement (eqs \ref{eq:conservation_masse_ouvert},\ref{eq:conservation_masse_ferme}).
+Moreover, the fluid entering the HC necessarily results on a piston displacement (eqs. \ref{eq:conservation_masse_ouvert},\ref{eq:conservation_masse_ferme}).
 \begin{align}
-	\text{Opened cylinder ~}& \left\{~
-	q_o = S_{hc} \dot{x}_{oc}
+	\text{Active cylinder ~}& \left\{~
+	q_a = S_{hc} \dot{x}_m
 	\right.
 	\label{eq:conservation_masse_ouvert}\\
-	\text{Closed cylinder ~}& \left\{~
-	q_c = S_{hc} \dot{x}_{cc}
+	\text{Inactive cylinder ~}& \left\{~
+	q_i = S_{hc} \dot{x}_{ic}
 	\right.
@@
 \end{align}
-
-    %///////////////////////////////////////////// 
-	\subsection{Preliminary dimensioning}	
-	\label{subsec:Preliminar dimensionning}
-    %/////////////////////////////////////////////
-The dimensioning starts by setting technological choices in order to experimentally validate the multiphysic coupled model.
-Therefore, the APG is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator, setting so the stiffness $K$.
-Then, the MQP4-10S HC from SMC will ensure the hydraulic to mechanical interface, setting then the cylinder piston section $S_{hc}$.
-Next, the hydraulic commutation of the two parallel branches is driven by two HVs made of collapsed flexible tubes, setting then $Cf(x_m)$.
-Finally, the \mbox{$L=16mm$ }parameter is chosen to be consistent with the application scale.
-
-The maximum energy extractable with the BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ }to \mbox{$x_m=0$}.
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{NUMERICAL MODEL AND SIMULATIONS}
+\label{NUMERICAL MODEL AND SIMULATIONS}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+    %///////////////////////////////////////////// 
+	\subsection{The harvester setting}	
+	\label{subsec:The harvester setting}
+    %/////////////////////////////////////////////
+The system parameters are set to maximize the exploited energy.
+The maximum theoretical energy in a BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ } to \mbox{$x_m=0$}.
 Knowing that it is equal to 65\% of the upper limit of the available hydraulic energy (eq.
-\ref{eq:max_hydraulic_energy} $\&$ fig.
-\ref{fig:OB_vs_LINEAR}), we can set the BR buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}.
+\ref{eq:max_hydraulic_energy}), we can set the BR buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}.
 The harvester is thus optimized depending on the energy source.
@@
 \end{equation}
-Two additional coupled requirements allow the system operation by setting the amplification level $a_h$.
-First, the available fluid must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
+Two coupled requirements allow the system operation by setting the amplification level $a_h$ and the BR buckling level $\epsilon$.
+First, the available swept volume must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
 \ref{eq:contrainte_course}).
-Then, the BR mechanical impedance on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
-At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to ensure the user comfort.
-If not, $\epsilon$ must be decreased, decreasing the extracted energy for the benefit of comfort.
+Then, the BR mechanical force on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
+At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to guarantee the pressure limit.
+If not, $\epsilon$ can be decreased, diminishing the extracted energy.
 \begin{empheq}[left=\empheqlbrace]{align} 
@@
 
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{NUMERICAL MODEL AND SIMULATIONS}
-\label{NUMERICAL MODEL AND SIMULATIONS}
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+starts by setting technological choices in order to experimentally validate the multiphysic coupled model.
+Therefore, the APG is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator, setting so the stiffness $K$.
+Then, the MQP4-10S HC from SMC will ensure the hydraulic to mechanical interface, setting then the cylinder piston section $S_{hc}$.
+Next, the hydraulic commutation of the two parallel branches is driven by two HVs made of collapsed flexible tubes, setting then $Cf(x_m)$.
+Finally, the \mbox{$L=16mm$ }parameter is chosen to be consistent with the application scale.
 
@@
 The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs.
-The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation.
-In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
+The ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
 So we introduce the hydraulic restriction coefficient $r_{Cf}$ defined as follows :
@@
 \end{equation}
-Where $Cf_c=Cf(\pm x_0)$.
-The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube.
-Therefore, we preliminarily assume that it is linear and defined as follows :
-\begin{align}
-	Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m  \notag \\
-			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{Cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
-			\label{eq:Cf(x_m)_linear}
-\end{align}
-Regarding the BR symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
+The numerical resolution of the differential equations can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
 

### 2022-10-12 article_system.tex
update

@@
 	Ep_{lin} = \dfrac{K_s\ x_{m}^2}{2} = \dfrac{\Delta p_{ear} \Delta V_{ear}}{2}
+	\label{eq:best_linear_soution}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-\begin{equation}
-x_m = \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
-				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr)
+
+\begin{equation}
+\resizebox{.9\linewidth}{!}{$	
+x_m = \Biggl[ \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
+				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr) \Biggr]
+				$}
 \label{eq:theta_fonction_de_xm}
 \end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 % \ddot{x}_m = - \frac{2K{x_0}^2}{mL^2}\Biggl[\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr )+ \dfrac{8K_{\varphi}}{L^2}\Biggr]x_m 
-% 			 - \frac{K_{VH}(x_m)\theta(x_m)}{ma}
+% 			 - \frac{K_{HV}(x_m)\theta(x_m)}{ma}
 % 			 - \frac{\mu+\mu_c}{m}\dot{x}_m  - \nu_f \text{sign}(\dot{x}_m)
@@
     %///////////////////////////////////////////// 
-	\subsection{The harvester setting}	
+	\subsection{The harvester parameters setting}	
 	\label{subsec:The harvester setting}
     %/////////////////////////////////////////////
-The system parameters are set to maximize the exploited energy.
-The maximum theoretical energy in a BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ } to \mbox{$x_m=0$}.
-Knowing that it is equal to 65\% of the upper limit of the available hydraulic energy (eq.
-\ref{eq:max_hydraulic_energy}), we can set the BR buckling level \mbox{$\epsilon = x_0/L$} through the equation \ref{eq:Ep_bar}.
-The harvester is thus optimized depending on the energy source.
-\begin{equation}
-	E_{pb} = \dfrac{K x_0^4}{3L^2}=0.65p_c \Delta V_{ear,m}
+The energy system combines many variable parameters. In order to determine them, it is first necessary to identify the fixed technological elements: 
+\begin{itemize}
+	\item The transducer is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
+Regarding the low forces level in the ear canal, we chose a product with low stiffness $K$.
+Subsequently, by changing the buckling level $\epsilon$, we will be able to manage the BR energy depending on $\text{max}(E_{hyd})$.
+	\item The friction in the HCs must be minimized.
+However, at the application scale, it is difficult to seal the pistons while providing low operating pressures For the experimental validations purpose, the actuation is therefore ensured by the SMC MQP4-10S HCs which admit operates at 1kPa pressure \cite{SMC2022}.
+The HC internal diameter $D_{hc}$ is $4$mm.
+	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale. $\epsilon$ can still be adjusted with $x_0$.
+\end{itemize}
+
+The maximum theoretical energy in a BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ } to \mbox{$x_m=0$} (eq.
+\ref{eq:Ep_bar}).
+It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
+\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
+\begin{equation}
+	E_{pb} = \dfrac{K x_0^4}{3L^2} = n(p_c \cdot \Delta V_{ear,m})
 	\label{eq:Ep_bar}
 \end{equation}
-Two coupled requirements allow the system operation by setting the amplification level $a_h$ and the BR buckling level $\epsilon$.
+The system is designed by setting the two coupled requirements allowing the system operation.
 First, the available swept volume must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
@@
 \end{empheq}
-
-starts by setting technological choices in order to experimentally validate the multiphysic coupled model.
-Therefore, the APG is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator, setting so the stiffness $K$.
-Then, the MQP4-10S HC from SMC will ensure the hydraulic to mechanical interface, setting then the cylinder piston section $S_{hc}$.
-Next, the hydraulic commutation of the two parallel branches is driven by two HVs made of collapsed flexible tubes, setting then $Cf(x_m)$.
-Finally, the \mbox{$L=16mm$ }parameter is chosen to be consistent with the application scale.
-
+Equations \ref{eq:contrainte_course} and \ref{eq:contrainte_confort} set the amplification level $a_h$ and the BR buckling level $\epsilon$.
+Regarding the technological choices and the system operation requirements, we can evaluate $n=65\%$.
+This value can be compared to the best theoretical linear energy extraction solution described in \ref{eq:best_linear_soution}.
 	%///////////////////////////////////////////// 
@@
 The numerical resolution of the differential equations can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
-
 	%///////////////////////////////////////////// 
@@
 By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
-\ref{fig:deltaV_ear}), the numerical model must give the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
-
-The ratio $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the opened HV.
+\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
+
+$r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the active HV.
 The mastication cycle is identically quadrupled in order to test the system cycling robustness.
-Also, the earplug is assumed as a perfect flow rate source.
-The calculated and the resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
-
-Figure \ref{fig:positions+DeltaV_debits_pear} presents the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
+The earplug is assumed to be a perfect flow rate source.
+The fixed, designed and resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
+
+Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
 The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), knowing that the gravity influence is not considered.
@@
 	\includegraphics[trim={8cm 0cm 0cm 5cm},clip,width=0.8\textwidth]{figures/BDT_hydraulique_VH.pdf}
-	\caption{Banc d'essai pour la caractérisations hydrauliques de VH}
+	\caption{Banc d'essai pour la caractérisations hydrauliques de HV}
 	\label{fig:BDT_hydraulique_VH}
@@
 	\includegraphics[trim={2cm 0cm 0cm 10cm},clip,width=\textwidth]{figures/essais_hydraulique_VH.pdf}
-	\caption{Essais de caractérisations hydrauliques de VH}
+	\caption{Essais de caractérisations hydrauliques de HV}
 	\label{fig:essais_hydraulique_VH}
@@
 	\includegraphics[trim={2cm 0cm 0cm 4cm},clip,width=0.49\textwidth]{figures/fabrication_tube_experimental.pdf}
-	\caption{Méthode de fabrication de la VH}
+	\caption{Méthode de fabrication de la HV}
 	\label{fig:fabrication_tube_experimental}
@@
 	\includegraphics[trim={10cm 0cm 0cm 0cm},clip,width=0.49\textwidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
-	\caption{$Cf_{VH}$ calculé à partir des essais pour 7 incréments d'angles}
+	\caption{$Cf_{HV}$ calculé à partir des essais pour 7 incréments d'angles}
 	\label{fig:resultats_essais_hydraulique_VH_D1mm}
@@
 		\includegraphics[trim={4cm 0cm 0cm 9.5cm},clip,width=0.7\textwidth]{figures/contact_M_VH_lachers.pdf}
-		\caption{Image de la VH$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,vh}$)}
+		\caption{Image de la HV$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,HV}$)}
 		\label{fig:contact_M_VH_lachers}

### 2022-10-13 article_system.tex
update

@@
 \usepackage{textcomp}
+\usepackage{multicol}
 
@@
 %% main text
+ % Ltex language=en
+\begin{table*}
+\begin{large}
+	\begin{center}
+		Nomenclature	\\
+		\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
+	\end{center}
+\end{large}		
+% \end{table*}
+\begin{minipage}{.5\textwidth}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{table}[!h]
+	\begin{tabular}{ c  m{6cm} }
+		\textbf{Subscripts}      &                                                         \\
+		APG                      & Amplified piezoelectric generator                       \\
+		BB                       & Buckled blade                                           \\
+		BR                       & Bistable resonator                                      \\
+		GB                       & Guide blade                                             \\
+		HA                       & Hydraulic amplifier                                     \\
+		HC                       & Hydraulic Cylinder                                      \\
+		HV                       & Hydraulic valve                                         \\
+		\textbf{Roman letters}   &                                                         \\
+		$a$                      & HV bending lever arm                                    \\
+		$a_h$ [-]                & Hydraulic amplification level                           \\
+		$Cf$ [Pam$^3$/s]         & Pressure loss coefficient                               \\
+		$Cf_0$ [Pam$^3$/s]       & Opened HV pressure loss coefficient                     \\
+		$Cf_c$ [Pam$^3$/s]       & Closed HV pressure loss coefficient                     \\
+		$C_p$ [F]                & APG internal capacity                                   \\
+		$D_h$ [m]                & Hydraulic diameter of the HV                            \\
+		$D_{hc}$ [m]             & Hydraulic cylinder internal diameter                    \\
+		$D_r$ [m]                & HV rigid sheath diameter                                \\
+		$E_d$ [J]                & Global dissipated energy                                \\
+		$E_e$ [J]                & Harvested electric energy                               \\
+		$E_{hyd}$ [J]            & Available hydraulic energy from earplug                 \\
+		$F_{br}$ [N]             & BR counter reaction force                               \\
+		$f_0$ [Hz]				 &	BR natural resonance frequency						   \\
+		$K$ [N/m]                & APG stiffness                                           \\
+		$K_{bb}$ [N/m]           & 8 BB's stiffness                                        \\
+		$K_{eq}$ [N/m]           & Equivalent stiffness seen from the APG                  \\
+		$K_{gb}$ [N/m]           & GB stiffness                                            \\
+		$K_{HV}$ [Nm/rad]        & HV stiffness                                            \\
+		$K_s$ [N/m]              & Spring stiffness                                        \\
+		$K_{\varphi}$ [Nm/rad]   & Single hinge stiffness                                  \\
+		$k^2$ [-]                & APG electromechanical coupling coefficient              \\
+		$k_{sys}^2$ [-]          & Global electromechanical coupling coefficient           \\
+\end{tabular}
+% \end{table}
+\end{minipage}
+\begin{minipage}{.5\textwidth}
+% \begin{table}[!h]
+\begin{tabular}{ c  m{6cm} }
+		$L$ [m]                  & Distance between 2 BR adjacent hinges                   \\
+		$l_0$ [m]                & Distance between 2 BR adjacent hinges on $\vec{x}$ axis \\
+		$m$ [kg]			     & BR dynamic mass 										   \\
+		$p_c$ [Pa]               & comfort pressure                                        \\
+		$p_{hc}$ [Pa]            & Hydraulic cylinder internal pressure                    \\
+		$S_{hc}$ [Pa]            & Hydraulic cylinder internal section                     \\
+		$q$ [m$^3$/s]            & Flow rate                                               \\
+		$R_l$ [$\Omega$]         & Load resistance                                         \\
+		$P_e$ [W]                & Harvested electric power                                \\
+		$Q$                      & BR quality factor                                       \\
+		$r_{Cf}$ [-]             & Hydraulic restriction coefficient                       \\
+		$x_m$ [m]                & BR mass position                                        \\
+		$x_{hc}$ [m]             & HC piston position                                      \\
+		$x_m$ [m]                & BR mass position                                        \\
+		$U_p$ [V]                & APG tension                                             \\
+		\textbf{Greek letters}   &                                                         \\
+		$\alpha$ [N/V]           & piezoelectric force coefficient                         \\
+		$\Delta p_{ear}$ [Pa]    & Earplug pressure variation                              \\
+		$\Delta V_{ear}$ [m$^3$] & Earplug volume variation                                \\
+		$\epsilon$ [-]           & BR buckling level                                       \\
+		$\eta_{br}$ [-]          & BR energy conversion efficiency                         \\
+		$\eta_g$ [-]             & Harvester energy conversion efficiency                  \\
+		$\theta$ [rad]           & HV bending angle                                        \\
+		$\mu$ [Ns/m]             & Air dynamic viscosity                                   \\
+		$\mu_{hc}$ [Ns/m]        & HC viscous loss coefficient                             \\
+		$\nu$ [Ns/m]             & Dry friction loss coefficient                           \\
+		$\omega_0$ [rad/s]       & BR natural angular frequency                            \\
+		\textbf{Indexes}         &                                                         \\
+		$\square_a$              & Active hydraulic branch                                 \\
+		$\square_b$              & \emph{Bottom} side hydraulic branch ($x <0$)            \\
+		$\square_c$              & Closed HV state              						   \\
+		$\square_i$              & \emph{Top} side hydraulic branch ($x >0$)               \\
+		$\square_o$              & Opened HV state             							   \\
+		$\square_t$              & Inactive hydraulic branch                               \\
+		$\square_{max}$          & Upper value                                             \\
+		$\square_{min}$          & Lowest value                                            \\
+	\end{tabular}
+% \end{table}
+\end{minipage}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{table*}
+		\begin{center}
+			\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
+		\end{center}
+\end{table*}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
 \section{INTRODUCTION}
-\label{INTRODUCTION} % Ltex language=en
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-
+\label{INTRODUCTION}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
 The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress on the energy consumption of mobile devices on the human body environment.
@@
 Then, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with the maximum values of $\Delta p_{ear}$ et $\Delta V_{ear}$ that have been recorded, i.e.
-$p_c=12kPa$ and $\Delta V_{ear,m}=60$mm$^3$.
+$p_c=12kPa$ and $(\Delta V_{ear})_{max}=60$mm$^3$.
 $p_c$ stands for the comfort pressure by assuming that the user could feel discomfort if $\Delta p_{ear}>p_c$.
@@
 \begin{align}
-	\text{max}(E_{hyd}) = p_c \cdot \Delta V_{ear,m} = 0.9\text{mJ}
+	\text{max}(E_{hyd}) = p_c \cdot (\Delta V_{ear})_{max} = 0.9\text{mJ}
 	\label{eq:max_hydraulic_energy}
@@
 The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment.
-The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed parts.
+The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths.
 It is in contact with the mass at the T point.
-The mass motion on the mobile part induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
+The mass motion on the mobile sheath induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
 Consequently, a pressure loss is generated through the valve in buckled position.
@@
 A dry friction model is chosen to describe the dissipation effect of the contact.
-The rubbing efforts depend on a dry friction coefficient $\nu_f$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
-The pressure $p_{ac}$ induces the HC hydraulic force and the coefficient $\mu_c$ models the viscous friction at the sealing gasket.
+The rubbing efforts depend on a dry friction coefficient $\nu$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
+The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket.
 The hydro-mechanical coupling will be detailed later.
 
-The electrical power generated by the APG is dissipated in a load resistor $R_{ch}$ calculated with an adaptive impedance matching expressed in the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
-\begin{equation}
-	R_{ch} = \dfrac{1}{C_p w_0}
+The electrical power generated by the APG is dissipated in a load resistor $R_l$ calculated with an adaptive impedance matching expressed in the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
+\begin{equation}
+	R_l = \dfrac{1}{C_p w_0}
 	\label{eq:R_ch_adaptive_imp}
@@
 \begin{equation}
-	\dfrac{U_p}{R_{ch}} = 
+	\dfrac{U_p}{R_l} = 
 	-\alpha\dfrac{d}{dt}\biggl(2\sqrt{{l_0}^2-x_m^2}\biggr)
@@
 \begin{equation}
-	P_e = \frac{{U_p}^2}{R_{ch}} 
+	P_e = \frac{{U_p}^2}{R_l} 
 	\label{eq:P_e}
@@
 				\ -2\alpha U_p \tan(\varphi)
-				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - \nu_f \text{sign}(\dot{x}_m)
-				\  - p_{ac}\ S_{hc} - \mu_{c}\ \dot{x}_m
+				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - \nu \text{sign}(\dot{x}_m)
+				\  - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m
 \label{eq:OB-GPA}
@@
 % 			 - \frac{K_{HV}(x_m)\theta(x_m)}{ma}
-% 			 - \frac{\mu+\mu_c}{m}\dot{x}_m  - \nu_f \text{sign}(\dot{x}_m)
+% 			 - \frac{\mu+\mu_{hc}}{m}\dot{x}_m  - \nu \text{sign}(\dot{x}_m)
 % 			 - \frac{2\alpha U_p\ x_m}{mL}
-% 			 - p_{ac}\ S_{hc} \\
+% 			 - p_{hc,a}\ S_{hc} \\
 % x_m = \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
 % 				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr)\\
-% \dfrac{U_p}{R_{ch}} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p 
+% \dfrac{U_p}{R_l} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p 
 % 	\end{dcases}
@@
 	\text{Active cylinder ~}& \left\{~
-	F_{br} - p_{ac}\ S_{hc} - \mu_{c}\ \dot{x}_m = 0
+	F_{br} - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m = 0
 	\right.
@@
 	\text{Inactive cylinder ~}& \left\{~
-	p_{ic}\ S_{hc} - \mu_{c}\ \dot{x}_{ic} = 0
+	p_{hc,i}\ S_{hc} - \mu_{c}\ \dot{x}_{hc,i} = 0
 	\right.
@@
 \end{align}
-Where $p_c$ is the HC chamber pressure and $x_{ic}$ the piston position of the inactive HC piston.
+Where $p_c$ is the HC chamber pressure and $x_{hc,i}$ the piston position of the inactive HC piston.
 $F_{br}$ accounts for the OB counter-reaction on the HC.
@@
 	\text{Active branch ~}& \left\{~
-	p_{ear} = \dfrac{1}{a_h}\biggl(p_{ac} + Cf_0 {q_a}^2 \biggr)
+	p_{ear} = \dfrac{1}{a_h}\biggl(p_{hc,a} + Cf_0 {q_a}^2 \biggr)
 	\right.
@@
 	\text{Inactive branch ~}& \left\{~
-	p_{ear} = \dfrac{1}{a_h}\biggl(p_{ic} + Cf(x_m) {q_i}^2 \biggr)
+	p_{ear} = \dfrac{1}{a_h}\biggl(p_{hc,i} + Cf(x_m) {q_i}^2 \biggr)
 	\right.
@@
 	\item The transducer is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
-Regarding the low forces level in the ear canal, we chose a product with low stiffness $K$.
-Subsequently, by changing the buckling level $\epsilon$, we will be able to manage the BR energy depending on $\text{max}(E_{hyd})$.
-	\item The friction in the HCs must be minimized.
-However, at the application scale, it is difficult to seal the pistons while providing low operating pressures For the experimental validations purpose, the actuation is therefore ensured by the SMC MQP4-10S HCs which admit operates at 1kPa pressure \cite{SMC2022}.
-The HC internal diameter $D_{hc}$ is $4$mm.
+	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which admit operates at 1kPa pressure \cite{SMC2022}.
 	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale. $\epsilon$ can still be adjusted with $x_0$.
@@
 \begin{equation}
-	E_{pb} = \dfrac{K x_0^4}{3L^2} = n(p_c \cdot \Delta V_{ear,m})
+	E_{pb} = \dfrac{K x_0^4}{3L^2} = n(p_c \cdot (\Delta V_{ear})_{max})
 	\label{eq:Ep_bar}
@@
 \begin{empheq}[left=\empheqlbrace]{align} 
-	\Delta V_{ear,m} = a_h\ S_{hc}\  x_{c0}
+	(\Delta V_{ear})_{max} = a_h\ S_{hc}\  x_{c0}
 	\label{eq:contrainte_course}\\
@@
 	%/////////////////////////////////////////////
-The numerical model aims to demonstrate the theoretical operation of the new concept of harvester.
 By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
 \ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
-
 $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the active HV.
@@
 
-The first phase consists on pushing on the BR mass to store potential energy, until the mass reaches $x=0$.
-During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BR counter-reaction force.
-The second phase begins after the mass crosses the $x_m=0$ position.
+During a first phase the BR mass is pushed until it reaches $x=0$.
+The fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
+The mass then crosses $x_m=0$ and the second phase begins.
 The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$).
-The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent.
-The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the resonatory mechanical energy is converted in electricity by the APG.
-The flow rate goes toward the right piston when $r_{Cf}$ is set at a minimum value of \mbox{$(r_{Cf})_{min}=26$}.
+The fluid is then guided toward the \emph{"top"} side and there is no contact between the mass and a HC.
+The mass oscillates around $x_m=x_0$and the energy is harvested by the APG.
+The adequate hydraulic actuation making the fluid flow toward the right HC is achievable when \mbox{$(r_{Cf})_{min}=26$}.
 
@@
 $x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
-$R_{ch}$			&	6.39			& [$k\Omega$] 			\\ \hline
+$R_l$			&	6.39			& [$k\Omega$] 			\\ \hline
 $\alpha$			&   0.105			& [$N/V$] 				\\ \hline
-$C_0$	   			&	0.25			& [$\mu F$]				\\ \hline
+$C_p$	   			&	0.25			& [$\mu F$]				\\ \hline
 $Q$ 				&	50				& [-] 					\\ \hline
@@
 The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$µm).
-The APG power is dissipated in the $R_{ch}$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
+The APG power is dissipated in the $R_l$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
 Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
@@
 $\eta_{ob}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
-$R_{ch}$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
+$R_l$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
 $m$	[g]						    &	\textcolor{red}{5.88}	& 9.00   					\\ \hline	

### 2022-10-17 article_system.tex
update delete blades design
update

@@
 % For subfigures
-\usepackage{graphicx}
 \usepackage{subcaption}
@@
 \usepackage{multicol}
+\usepackage{graphicx}
 
@@
 \address[symme]{Laboratoire SYMME - Université Savoie Mont Blanc, 7 Chemin de Bellevue, 74940, Annecy}
-\address[critias]{Laboratoire Critias - École de Technologie Supérieure, 1100 Rue Notre-Dame Ouest, Montréal, QC, H3C 1K3}
+\address[critias]{Université du Québec - École de technologie supérieure, 1100 Rue Notre-Dame Ouest, Montréal, QC, H3C 1K3}
 
@@
 \author[critias]{Aidin DELNAVAZ}
-\author[critias]{Jérémy VOIX}
+\author[critias]{Jérémie VOIX}
 
@@
 		HA                       & Hydraulic amplifier                                     \\
-		HC                       & Hydraulic Cylinder                                      \\
+		HC                       & Hydraulic cylinder                                      \\
 		HV                       & Hydraulic valve                                         \\
+		PFF						 & piezoelectric force factor  \\
 		\textbf{Roman letters}   &                                                         \\
-		$a$                      & HV bending lever arm                                    \\
+		$a$ [m]                  & HV bending lever arm                                    \\
 		$a_h$ [-]                & Hydraulic amplification level                           \\
-		$Cf$ [Pam$^3$/s]         & Pressure loss coefficient                               \\
-		$Cf_0$ [Pam$^3$/s]       & Opened HV pressure loss coefficient                     \\
-		$Cf_c$ [Pam$^3$/s]       & Closed HV pressure loss coefficient                     \\
+		$Cf$ [Pa.s$^2$.m$^{-6}$]         & Pressure loss coefficient                               \\
+		$Cf_0$ [Pa.s$^2$.m$^{-6}$]       & Opened HV pressure loss coefficient                     \\
+		$Cf_c$ [Pa.s$^2$.m$^{-6}$]       & Closed HV pressure loss coefficient                     \\
 		$C_p$ [F]                & APG internal capacity                                   \\
@@
 		$K_{gb}$ [N/m]           & GB stiffness                                            \\
-		$K_{HV}$ [Nm/rad]        & HV stiffness                                            \\
+		$K_{HV}$ [N.m/rad]        & HV stiffness                                            \\
 		$K_s$ [N/m]              & Spring stiffness                                        \\
-		$K_{\varphi}$ [Nm/rad]   & Single hinge stiffness                                  \\
+		$K_{\varphi}$ [N.m/rad]   & Single hinge stiffness                                  \\
 		$k^2$ [-]                & APG electromechanical coupling coefficient              \\
 		$k_{sys}^2$ [-]          & Global electromechanical coupling coefficient           \\
+		$L$ [m]                  & Distance between 2 BR adjacent hinges                   \\
+		$l_0$ [m]                & Distance between 2 BR adjacent hinges on $\vec{x}$ axis \\
 	\end{tabular}
@@
 \begin{tabular}{ c  m{6cm} }
-		$L$ [m]                  & Distance between 2 BR adjacent hinges                   \\
-		$l_0$ [m]                & Distance between 2 BR adjacent hinges on $\vec{x}$ axis \\
 		$m$ [kg]			     & BR dynamic mass 										   \\
@@
 		$P_e$ [W]                & Harvested electric power                                \\
-		$Q$                      & BR quality factor                                       \\
+		$Q$ [-]                  & BR quality factor                                       \\
 		$r_{Cf}$ [-]             & Hydraulic restriction coefficient                       \\
@@
 		$x_m$ [m]                & BR mass position                                        \\
+		$x_0$ [m]                & BR buckling height                                       \\
 		$U_p$ [V]                & APG tension                                             \\
@@
 		$\theta$ [rad]           & HV bending angle                                        \\
-		$\mu$ [Ns/m]             & Air dynamic viscosity                                   \\
-		$\mu_{hc}$ [Ns/m]        & HC viscous loss coefficient                             \\
-		$\nu$ [Ns/m]             & Dry friction loss coefficient                           \\
+		$\mu$ [N.s/m]             & Air dynamic viscosity                                   \\
+		$\mu_{hc}$ [N.s/m]        & HC viscous loss coefficient                             \\
+		$f_d$ [N.s/m]             & Dry friction loss coefficient                           \\
+		$\varphi$ [rad]			 & BR hinge rotational angle							   \\
 		$\omega_0$ [rad/s]       & BR natural angular frequency                            \\
@@
 Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion.
-The next section states on the hydraulic energy source characterization and on the harvesting strategy we adopted.
+The next section states on the hydraulic energy source characterization and on the harvesting strategy that we adopted.
 Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle.
-Section \ref{sec:SYSTEM MODELING AND SIMULATIONS} shows the global system  modeling and the numerical simulation on its behavior.
-Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS} then exposes the experimental validation performed on the harvester critical components and section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model.
-Section \ref{sec:ANALYZE AND DISCUSSION} discusses this work major contributions and the harvester potential.
+Section \ref{sec:SYSTEM MODELING} details the global system modeling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester.
+Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} then exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling.
+Then, section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work major contributions and the harvester potential.
 Finally, a conclusion is stated in the last section.
@@
 \ref{fig:HV_actuation_detail}).
+$K_{HV}$ and $K_{\varphi}$ both act the same way by making move the stable equilibrium positions of the BR toward $0$ as much as they increase.
 A dry friction model is chosen to describe the dissipation effect of the contact.
-The rubbing efforts depend on a dry friction coefficient $\nu$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
+The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
 The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket.
@@
 				\ -2\alpha U_p \tan(\varphi)
-				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - \nu \text{sign}(\dot{x}_m)
+				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - f_d \text{sign}(\dot{x}_m)
 				\  - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m
@@
 % 			 - \frac{K_{HV}(x_m)\theta(x_m)}{ma}
-% 			 - \frac{\mu+\mu_{hc}}{m}\dot{x}_m  - \nu \text{sign}(\dot{x}_m)
+% 			 - \frac{\mu+\mu_{hc}}{m}\dot{x}_m  - f_d \text{sign}(\dot{x}_m)
 % 			 - \frac{2\alpha U_p\ x_m}{mL}
@@
 \section{NUMERICAL MODEL AND SIMULATIONS}
-\label{NUMERICAL MODEL AND SIMULATIONS}
+\label{sec:NUMERICAL MODEL AND SIMULATIONS}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
-The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa here, i.e.
+The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa, i.e.
 a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
-The harvester efficiency could lead to a theoretical maximum of $684$µJ extractable from the ear canal.
+The harvester theoretical efficiency could lead to a maximum of $684$µJ extractable from the ear canal.
 
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={0cm 0cm 0cm 1cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
 	\caption{}
@@
 \begin{table}
-	\centering
-	\begin{tabular}{c|c|c}
+\begin{subtable}[b]{.42\linewidth}
+	\centering
+	\resizebox{\linewidth}{!}{%
+	\begin{tabular}{c|c}
 \toprule
-\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
+\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} \\
 \midrule
-$K$					&	0.256			& [$N/\mu m$]			\\ \hline
-$x_0$				&	0.49			& [$mm$] 				\\ \hline
-$L$					&	16.0			& [$mm$] 				\\ \hline
-$m$					&	5.88			& [$g$] 				\\ \hline
-$x_{c0}$			&	0.69			& [$mm$] 				\\ \hline
-$R_l$			&	6.39			& [$k\Omega$] 			\\ \hline
-$\alpha$			&   0.105			& [$N/V$] 				\\ \hline
-$C_p$	   			&	0.25			& [$\mu F$]				\\ \hline
-$Q$ 				&	50				& [-] 					\\ \hline
-$\eta_g$			& 	76				& [$\%$]		\\ 
+$K$	[N/µm]		&	0.256		\\	\hline
+$x_0$ [mm]			&	0.49		\\	\hline
+$L$	[mm]			&	16.0		\\	\hline
+$m$	[g]				&	5.88		\\	\hline
+$x_{c0}$ [mm]		&	0.69		\\	\hline
+$R_l$ [k$\Omega$] 	&	6.39		\\	\hline
+$\alpha$ [N/V]		&   0.105		\\	\hline
+$C_p$ [µF]	   		&	0.25		\\	\hline
+$Q$ [-]				&	50			\\	\hline
+$\eta_g$ [\%]		& 	76			\\
 \bottomrule
-	\end{tabular}
-	\caption{Electromechanical parameters}
+	\end{tabular}}
+	\caption{Electromechanical}
 	\label{tab:parametres électromécaniques}			
-\end{table}
-\begin{table}
-	\centering
-	\begin{tabular}{c|c|c}
+\end{subtable}
+\hfillx
+\begin{subtable}[b]{.55\linewidth}
+	\centering
+	\resizebox{\linewidth}{!}{%
+	\begin{tabular}{c|c}
 \toprule
-\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} & \multicolumn{1}{c}{~~\textbf{[Unit]}~~}  \\
+\multicolumn{1}{c}{~~\textbf{Parameter}~~}  & \multicolumn{1}{c}{~~\textbf{Value}~~} \\
 \midrule
-$D_{hc}$  	   			&	4				& [$mm$]			\\ \hline
-$a_h$					&	29				& [-]				\\ \hline
-$p_c$					&	1				& [$kPa$]			\\ \hline
-$\Delta V{ear,m}$		& 60				& [$mm^3$]			\\ \hline
-$Cf_0$					&	0.21e17			&[$Pa.s^2m^{-6}$]	\\ \hline
-$Cf_c$					&	5.46e17			&[$Pa.s^2m^{-6}$]	\\
+$D_{hc}$ [mm] 	   			&	4						\\ \hline
+$a_h$ [-]					&	29			 			\\ \hline
+$p_c$ [kPa]					&	1				 		\\ \hline
+$(\Delta V{ear})_{max}$ [mm$^3$]	& 60				\\ \hline
+$Cf_0$ [Pa.s$^2$/m$^6$]			&	0.21e17			\\ \hline
+$r_{Cf}$ [-]						&	26				\\ 
 \bottomrule 
-	\end{tabular}
-	\caption{Hydraulic parameters}
+	\end{tabular}}
+	\caption{Hydraulic}
 	\label{tab:parametres_hydrauliques}		
+\end{subtable}
+\caption{Simulated model theoretical parameters}
 \end{table}
@@
     %/////////////////////////////////////////////
-The device heart is the electromechanical converter composed of the BR implementing the APG and therefore, they have been designed with respect to space requirements.
-We opted for a monobloc structure with blades in order to optimize the resonator quality factor by avoiding screw assemblies.
-Figure \ref{fig:monobloc_face} shows the face view of the monobloc bistable resonator CAD that has been fabricated by electrical discharge machining (EDM).
+The device heart is the electromechanical converter composed of the BR with the APG.
+They have been designed at the application scale in order to prove their feasibility.
+The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure with blades.
+This method optimizes the resonator quality factor by avoiding screw assemblies.
+Figure \ref{fig:BDT_OB+GPA} shows the BR mounted on the experimental test bench.
 The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations.
-The efficient part composed of the blades and the central mass are $1.2$mm think.
-The external rigid $6$mm thick frame has been designed to ensure the fixed boundary conditions and also to allow the mounting of both the measurement instruments and the HCs.
-The local thickenings at the midspan of the blades are intended to facilitate the fabrication and also to maximize the BB compression stiffness that maximizes the electromechanical coupling of the harvester, as we show in the following sections.
+The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
+They also maximize the BB compression stiffness that maximizes harvester efficiency, as we show in the following section.
 The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
@@
 % Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
-Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [Nm/rad] \\
+Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [N.m/rad] \\
 Stiffness of the guide blade along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
@@
 %%%%%%%%%%%%%%%%%%%%% 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-\centering
-\captionsetup{justification=centering}
-	\includegraphics[trim={19.2cm 0cm 0cm 5cm},clip,width=.7\linewidth]{figures/monobloc_face.pdf}
-	\caption{Face transparency view of the monobloc BR CAO}
-\label{fig:monobloc_face}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     %///////////////////////////////////////////// 
@@
     %/////////////////////////////////////////////
-The harvesting occurs during the free oscillation phase.
+The harvesting happens during the free oscillation phase.
 The main issue is to maximize the energy conversion efficiency $\eta_{ob}$ of this stage.
@@
 \end{equation}
-Where $k^2_{sys}$ is the electromechanical coupling of the harvesting system.
-The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the respective blades (tab.
+$k^2_{sys}$ is the global electromechanical coupling coefficient of the harvesting system.
+The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the blades (tab.
 \ref{tab:parametres_lames}) as follows :
@@
 % \end{equation}
-
 \begin{equation}
@@
 Where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by equation \ref{eq:alpha_eq}.
-It depends on the initial PFF of the APG alone and the and ratio between the equivalent stiffness $K_{eq}$ (eq.
+It depends on the APG PFF the and ratio between the equivalent stiffness $K_{eq}$ (eq.
 \ref{eq:K_eq}) of the structure on the $\vec{x}$ axis and the equivalent stiffness of the APG mounted on the GB.
@@
 
-On the architecture presented on figure \ref{fig:monobloc_face} the deformation of the GB is similar to the standard case of a fixed-ended beam undergoing a single concentrated load applied at midspan.
-Using structural analysis formulas for this load case, we can express $K_{gb}$ as follows \cite{Leet1993} :
-\begin{equation}
-	K_{gb} = \dfrac{2EI_{gb}el_v^3}{L_v^3}
-	\label{eq:Kgb_definition}
-\end{equation}
-$I_{gb}$ is the second moment of area along $\vec{y}$ axis.
-According the material properties and GB dimensions (tab.
-\ref{tab:parametres_lames}) \mbox{$K_{gb} = 190N/m$}, which is negligible before \mbox{$K=252kN/m$}.
-
-$K_{bb}$ is for its part verified through a FEM generated with the BR CAD on ANSYS Workbench.
-Figure \ref{fig:fem_statique} presents the model and the initial and boundary conditions used for the study.
-The fixed frame is replaced by three rigid fixed points in order to minimize the number of elements and reduce the calculation time.
-The APG elastic force is modeled by the load $F_{st}$ applied at the right end of the structure and the transducer is replaced by a rigid mobile part in order to isolate the stiffness of the BBs.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-\centering
-\captionsetup{justification=centering}
-	\includegraphics[trim={21.9cm 0cm 0cm 10.2cm},clip,width=.8\linewidth]{figures/fem_statique.pdf}
-	\caption{BR finit element model with initial and boundary conditions for a static study}
-\label{fig:fem_statique}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-By imposing incrementally increasing $F_{st}$ and measuring the displacement $z_{st}$ of the moving structure in small displacement condition, we can determine $K_{bb}$ (tab.
-\ref{tab:parametres_lames}) with equation \ref{eq:Kbb_definition}.
-The stiffness of the BBs and the GB lead to a theoretical efficiency of 75\%, which is consistent with the previous simulated results (tab.
-\ref{tab:parametres électromécaniques}).
-\begin{equation}
-	K_{bb} = \dfrac{F_{st}}{z_{st}}
-	\label{eq:Kbb_definition}
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BR operation.
-Based on the precedent FEM static model (fig.
-\ref{fig:fem_statique}), a buckling study has been performed for the purpose.
-When the mass crosses the unstable \mbox{$x_m=0$} position, the compression stress on the blades is in fact at its maximum.
-With the same boundary conditions as in figure \ref{fig:fem_statique}, the buckling study imposes the force $F_{st} = F_{z,0}$ modeling the APG elastic counter reaction on $\vec{z}$ axis at $x_m = 0$.
-$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement} relying on figure \ref{fig:schema_cinematique1} :
+When the mass crosses the unstable \mbox{$x_m=0$} position, the compression force $F_{z,0}$ induces the maximum stress on the BB.
+$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement} relying on figure \ref{fig:schema_cinematique1}.
 \begin{equation}
@@
 \end{equation}
-
-The fundamental buckling mode of the BBs leads to the wanted structural buckling generating the bistable equilibrium positions $\pm x_0$ for the mass.
-The buckling study reveals that $F_{z,0}=0.61$N when the useful buckling mode appears (fig.
-\ref{fig:buckling_fundamental}).
-However, the first secondary undesirable mode illustrated on figure \ref{fig:buckling_secondary} appears for $F_{z,0}=6.4$N.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure}[!htb]
-	\begin{center}
-		\begin{subfigure}[t]{0.48\linewidth}
-			\captionsetup{justification=centering}
-			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_fundamental.pdf}
-			\caption{Fundamental = useful}
-			\label{fig:buckling_fundamental}
-		\end{subfigure}
-		\hfillx
-		\begin{subfigure}[t]{0.48\linewidth}
-			\captionsetup{justification=centering}
-			\includegraphics[trim={24.1cm 0cm 0cm 14.8cm},clip,width=\linewidth]{figures/buckling_secondary.pdf}
-			\caption{Secondary = undesirable}
-			\label{fig:buckling_secondary}
-		\end{subfigure}
-		\caption{Deformed shape of the first appearing buckling modes}
-		\label{fig:Buckling_deformed_shapes}
-	\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+The problem was treated with a FEM model and the results are summarized through the figure \ref{fig:buckling_limit}.
+It reveals that the first secondary undesirable modes appear for $F_{z,0}=6.4$N.
 The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity.
-Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BR, as presented on figure \ref{fig:buckling_limit}.
+Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BR, as presented on figure.
 The preliminary simulated case presented in the previous section is well located in the preferable domain where there is no undesirable buckling modes.
@@
     %/////////////////////////////////////////////
-The BR has been fabricated and mounted and the APG has been implemented on it.
-The experimental test bench for the electromechanical characterizations of the resultant converter is presented on figure \ref{fig:BDT_OB+GPA}.
+The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented on figure \ref{fig:BDT_OB+GPA}.
 An additional blade is mounted with the APG in order to prevent its rotation around any axis.
@@
 The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behavior.
-The test protocol consisted on recreating the operation conditions as close as possible to real-life operation.
-The mass is guided from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then it goes oscillate around the opposite stable equilibrium position.
-The experimental data was then used to identify and recalibrate the following electromechanical parameters of the harvester through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
+The mass is guided by a HC from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then oscillates around the opposite stable equilibrium position.
+The experimental data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
 \ref{tab:parametres_lacher_free}).
-The correlations were made with iterative simulations of the global model by minimizing the error between the simulated and the experimental parameters.
-The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ of the converter have also been extracted from the recalibrated model.
-The simulation with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA}.
-The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
+The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ can also be calculated.
 %%%%%%%%%%%%%%%%%
@@
 \captionsetup{justification=centering}
+\resizebox{.8\linewidth}{!}{%
 	\begin{tabular}{ c | c | c }
@@
 	\bottomrule
-	\end{tabular}
+	\end{tabular}}
 	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
@@
 %%%%%%%%%%%%%%%%%%%%%  
+    %/////////////////////////////////////////////
+
+	\subsection{Analyze and summary}	
+	\label{subsec:Analyze and summary}
+    %/////////////////////////////////////////////
+The experimental dynamic behavior of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
+However, the performances of the experimental prototype are below the theoretical expectations (tab.
+\ref{tab:parametres électromécaniques}).
+The efficiency drop is consistent with the quality factor and the electromechanical coupling coefficient drop (eq.
+\ref{eq:eta_ob}).
+
+Two major factors could have led to such results.
+First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
+Then, small undulations have been observed on the BBs after fabrication and could also have gotten worse during the manipulation.
+These undulations reduce $K_{bb}$, diminishing $k^2_{sys}$ according equations \ref{eq:k2_sys}-\ref{eq:K_eq}.
+Improvements are proposed later in order to reduce the energy losses during this stage.
+
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{EXPERIMENTAL APPROACH FOR THE HV \mbox{DESIGN}}
+\label{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+In order to validate the feasibility of the HVs we adopted an experimental approach to find the material and geometrical parameters of the tube capable to achieve $(r_{Cf})_{min}=26$ (tab.
+\ref{tab:parametres_hydrauliques}).
+A HV composed of a kapton tube \cite{Dupont2012} of initial diameter $D_t=1.05$mm and thickness $th_t=25$ µm was found to meet this hydraulic criteria.
+It will be called HV$_{T1}$ afterwards.
+    %///////////////////////////////////////////// 
+	\subsection{HV hydraulic experimental characterization}	
+	\label{subsec:HV hydraulic test bench presentation}
+    %/////////////////////////////////////////////
+Figure \ref{fig:essais_hydraulique_VH} shows the HV$_{T1}$ during the experimental characterizations on the hydraulic test bench.
+An electromechanical rotary plate is monitored on LabVIEW interface and imposes the bending angle $\theta$.
+A liquid filled syringe is emptied through the HV$_{T1}$ and its exciting flow rate $q_{ser}$ is deduced by tracking its moving piston displacement.
+The pressure loss coefficient $Cf_{T1}$ is calculated as \mbox{follows :}
+\begin{equation}
+	Cf_{T1} = \dfrac{p_1-p_2}{q_{ser}^2}
+\end{equation}
+Where $p_1$ and $p_2$ are respectively the fluid pressure monitored before entering and after exciting the HV$_{T1}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
+\begin{figure*}[!htb]
+\begin{center}
+	\captionsetup{justification=centering} 
+	\includegraphics[trim={2cm 0cm 0cm 11cm},clip,width=.8\textwidth]{figures/essais_hydraulique_VH.pdf}
+	\caption{Hydraulic characterization test bench for HVs}
+	\label{fig:essais_hydraulique_VH}
+\end{center}	
+\end{figure*}    
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+The emptying procedure was repeated 7 times for $\theta$ varying from $0^{\circ}$ to $60^{\circ}$ with $10^{\circ}$ increments.
+The experimental results are plotted on figure \ref{fig:resultats_essais_hydraulique_VH_D1mm}.
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!htbp]
+\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={15.5cm 0cm 0cm 3.6cm},clip,width=0.6\linewidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
+	\caption{Hydraulic characterization of the HV$_{T1}$.}
+	\label{fig:resultats_essais_hydraulique_VH_D1mm}
+\end{figure}
+%%%%%%%%%%%%%%%%
+The hydraulic restriction coefficient of HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
+In order to set an optimal angle operation range we must investigate the evolution $K_{HV}(\theta)$.
+This matter will not be discussed in this paper.
+The following section presents the recalibrated harvester model using the experimental data of the HV$_{T1}$ and the experimental data of the electromechanical converter.
+
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
+\label{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+	%/////////////////////////////////////////////
+	\subsubsection{Free release trials}
+	%/////////////////////////////////////////////
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
+\begin{figure}[!htbp]
+	\begin{center}
+		\captionsetup{justification=centering}
+		\includegraphics[trim={9.9cm 0cm 0cm 9cm},clip,width=0.8\linewidth]{figures/contact_M_VH_lachers.pdf}
+		\caption{Image de la HV$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,HV}$)}
+		\label{fig:contact_M_VH_lachers}
+	\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	%/////////////////////////////////////////////
+	\subsubsection{Recalibrated model}
+	%/////////////////////////////////////////////
+The simulation with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA}.
+The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    %///////////////////////////////////////////// 
-	\subsection{Analyze and summary}	
-	\label{subsec:Analyze and summary}
-    %/////////////////////////////////////////////
-
-According to figure \ref{fig:BDT_OB+GPA}, the experimental dynamics of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
-However, the performances of the experimental prototype proved to be below the values theoretically predicted (tab.
-\ref{tab:parametres électromécaniques}) even if the efficiency drop is consistent with the quality factor and the electromechanical coupling coefficient drop (eq.
-\ref{eq:eta_ob}).
-We identified two main factors that could have led to such results.
-
-First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw. 
-Then, small undulations have been observed on the BBs after fabrication, and they could also have gotten worse during the manipulation.
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{EXPERIMENTAL APPROACH FOR THE HV \mbox{DESIGN}}
-\label{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-
-    %///////////////////////////////////////////// 
-	\subsection{The HV hydraulic behavior}	
-	\label{The hydraulic valves}
-    %/////////////////////////////////////////////
-
-	%/////////////////////////////////////////////
-	\subsubsection{Test bench presentation}
-	 %/////////////////////////////////////////////
-
-	%/////////////////////////////////////////////
-	\subsubsection{Results and discussion}
-    %/////////////////////////////////////////////
-
-\begin{figure*}[!htb]
-\begin{center}
-	\captionsetup{justification=centering} 
-	\includegraphics[trim={8cm 0cm 0cm 5cm},clip,width=0.8\textwidth]{figures/BDT_hydraulique_VH.pdf}
-	\caption{Banc d'essai pour la caractérisations hydrauliques de HV}
-	\label{fig:BDT_hydraulique_VH}
-\end{center}	
-\end{figure*}    
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure*}[!htb]
-\begin{center}
-	\captionsetup{justification=centering} 
-	\includegraphics[trim={2cm 0cm 0cm 10cm},clip,width=\textwidth]{figures/essais_hydraulique_VH.pdf}
-	\caption{Essais de caractérisations hydrauliques de HV}
-	\label{fig:essais_hydraulique_VH}
-\end{center}	
-\end{figure*}    
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure}[!htb]
-\begin{center}
-	\captionsetup{justification=centering} 
-	\includegraphics[trim={2cm 0cm 0cm 4cm},clip,width=0.49\textwidth]{figures/fabrication_tube_experimental.pdf}
-	\caption{Méthode de fabrication de la HV}
-	\label{fig:fabrication_tube_experimental}
-\end{center}	
-\end{figure}    
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-\begin{center}
-	\captionsetup{justification=centering}
-	\includegraphics[trim={10cm 0cm 0cm 0cm},clip,width=0.49\textwidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
-	\caption{$Cf_{HV}$ calculé à partir des essais pour 7 incréments d'angles}
-	\label{fig:resultats_essais_hydraulique_VH_D1mm}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%
-	%/////////////////////////////////////////////
-	\subsection{The HV mechanical influence on the electromechanical converter (théorique = x0 réduit donc faut compenser)}	
-	\label{The mechanical influence of the valve on the electromechanical converter}
-	%/////////////////////////////////////////////
-Theoretically...
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
-\label{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-	%/////////////////////////////////////////////
-	\subsubsection{Free release trials}
-	%/////////////////////////////////////////////
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure}[!htbp]
-	\begin{center}
-		\captionsetup{justification=centering}
-		\includegraphics[trim={4cm 0cm 0cm 9.5cm},clip,width=0.7\textwidth]{figures/contact_M_VH_lachers.pdf}
-		\caption{Image de la HV$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,HV}$)}
-		\label{fig:contact_M_VH_lachers}
-	\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	%/////////////////////////////////////////////
-	\subsubsection{Recalibrated model}
-	%/////////////////////////////////////////////
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \midrule
-$D_g$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
+$D_r$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
 $\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& \textcolor{red}{{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
@@
 $a$ [mm]         			    & \cellcolor{ashgrey}  		&  2.24				 	 	\\ \hline
-$\mu_{fs}$ [~~] 				& \cellcolor{ashgrey}  		&  0.42  					\\ \hline
+$f_d$ [-] 				& \cellcolor{ashgrey}  		&  0.42  					\\ \hline
 $K$ [N/m] 						&	84480			  	 	&  84480  					\\ \hline
 $x_0$ [mm] 						& \textcolor{red}{0.59}		& \textcolor{red}{0.50}  	\\ \hline
-$v_0$ [mm/s] 					& \textcolor{red}{10}		& \textcolor{red}{65}  		\\ \hline
-$Q$	[~~] 						& 		24.0		 		& 5.0     					\\ \hline
+$Q$	[-] 						& 		24.0		 		& 5.0     					\\ \hline
 $k^2_{sys}$ [\%] 				& 		1.25		 		& \textcolor{red}{1.25}   	\\ \hline
-$\eta_{ob}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
+$\eta_{br}$ [\%] 				& 		11.9		 		& 2.6   					\\ \hline	
 $R_l$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{ANALYZE AND DISCUSSION}
-\label{sec:ANALYZE AND DISCUSSION}
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
 \section{CONCLUSION}

### 2022-10-20 article_system.tex
update revisions_FF part1

@@
 		APG                      & Amplified piezoelectric generator                       \\
-		BB                       & Buckled blade                                           \\
+		BB                       & Buckled beam                                           \\
 		BR                       & Bistable resonator                                      \\
-		GB                       & Guide blade                                             \\
+		GB                       & Guide beam                                             \\
 		HA                       & Hydraulic amplifier                                     \\
@@
 Then, section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work major contributions and the harvester potential.
-Finally, a conclusion is stated in the last section.
+Finally, a conclusion is stated.
 
@@
     %///////////////////////////////////////////// 
-	\subsection{The harvesting strategy}	
+	\subsection{Harvesting strategy}	
 	\label{The harvesting strategy}
@@
 Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources.
-In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
+The power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
 Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.
-Thus, piezoelectric ceramics appear like good candidates, but they can not be easily used because of their high stiffness and their high resonance frequencies (>$1.57$Hz).
-Therefore, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of piezoelectric ceramic transducers.
+
+Piezoelectric ceramics appear like good candidates for mechanical energy transduction at small scales, but their high stiffness can limit their use on soft materials as human tissues.
+Mechanical amplifiers like flextensional structures can nevertheless be used to adapt the stress/displacement levels between the energy source and the transducing stiff material \cite{Abdelnaby2016}.
+Also, the best energy conversion efficiency for piezoelectric ceramics is achieved for at the transducer resonance.
+As the mean mastication frequency is estimated to \mbox{$1.57$Hz}, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of the transducer.
 A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
 Stoppers however dissipate energy.
-Alternative solutions use mechanically bistable resonators (BR) to perform frequency-up \cite{Vocca2012}.
+Alternative solutions use mechanically bistable resonators (BR) \cite{Vocca2012}.
 Recent works led to the development and optimization of bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}.
 They show enhanced performances due to high electromechanical coupling.
-
-We can estimate the best choice maximizing the energy extraction from the hydraulic source.
-To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer.
+The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
+
 The hydraulic-mechanic interface can be a hydraulic cylinder (HC).
-It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication.
-Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$.
+It can store the energy in the frequency-up converter by actuating it at the frequency of human mastication.
+The amount of extractable energy from the hydraulic source will then depend on the mechanical stage behavior.
+Before being converted in electricity, the energy is in fact stored in a mechanical potential reservoir.
 During the low frequency actuation, the forces applied on each side of the HC piston are equal.
 Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{equation}
-	\Delta p_{ear}\ S_{hc} = K_{s}\ x_{m}
-	\label{eq:hydraulic-mechanic_interface}
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Yet, BRs usually admit non-linear elastic behavior.
-For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\% from the same energy source, which is $15$\% better than the best theoretical linear option.
+Non-linear elastic potential reservoirs can also be considered.
+This work presents the energy extraction capability of a BR governed by a Duffing equation.
+It admits 2 stable equilibrium positions \mbox{$x_m=\pm x_0$}, an unstable one in \mbox{$x_m=0$} and its stiffness depends on its structural buckling level $\epsilon$ defined later in equation \ref{eq:epsilon_def}.
+The maximum theoretical energy in the BR for a quasi-static actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$} to \mbox{$x_m=0$} (eq.
+\ref{eq:Ep_bar}).
+It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
+\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
+\begin{equation}
+	E_{pb} = \dfrac{K x_0^2\epsilon^2}{3} = n(p_c \cdot (\Delta V_{ear})_{max})
+	\label{eq:Ep_bar}
+\end{equation}
+We see later that it is inherently capable of exploiting $65$\% from the hydraulic energy source, which is $15$\% better than the best theoretical linear option.
 Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
-
-% Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behavior of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!htbp]
-% 	\centering
-% 	\captionsetup{justification=centering}
-% 	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
-% 	\caption{Hydraulic source exploitation depending on the mechanical load}
-% 	\label{fig:OB_vs_LINEAR}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \ref{fig:APG}).
-The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth.
-The HA adapts the both cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig.
+The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig.
 \ref{fig:system_presentation}).
 
-The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$x_m = -x_0$}.
+The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$-x_0$}.
 The harvester operates on two major phases.
@@
 A technological solution for the HV is to use a flexible tube buckled by bending.
-The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment.
+The figure \ref{fig:HV_actuation_detail} schematizes the integration of such a HV around the BR environment.
 The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths.
@@
 Consequently, a pressure loss is generated through the valve in buckled position.
-The HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
+The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
 This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
@@
 The HV technological choice is motivated by three major arguments.
-First, the absence of electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
+First, the absence of dedicated electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
 Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-The harvester is a multiphysic system composed of hydraulic, mechanical, and electrical components.
-This section presents the global multiphysic model describing the system theoretical operation.
+This section presents the global multiphysic model describing the system operation.
 Two coupled subsystems are considered.
 The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
-Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.
+Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier and the liquid filled earplug.
 
@@
 Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier.
-These hydraulic components will rather be considered on further work.
+These hydraulic components will rather be considered for further work.
 
@@
 The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC.
-The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
+The rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
 The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
-The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction, defined by the equation \ref{eq:k2_def}.\\
+The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by the equation \ref{eq:k2_def}.\\
 The model is based on the following hypotheses:
@@
 	\item The only mass considered is the BR mass (2).
-	\item All parts are infinitely rigid except for the APG (4).
+	\item All parts are rigid except for the APG (4).
 	\item The hinges are considered elastic: They are defined by their rotational stiffness $K_{\varphi}$
@@
 \ref{fig:HV_actuation_detail}).
-$K_{HV}$ and $K_{\varphi}$ both act the same way by making move the stable equilibrium positions of the BR toward $0$ as much as they increase.
+$K_{HV}$ and $K_{\varphi}$ both act the same way by shifting the stable equilibrium positions of the BR toward $0$ as much as they increase.
 A dry friction model is chosen to describe the dissipation effect of the contact.
 The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
-The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket.
+The coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HC.
 The hydro-mechanical coupling will be detailed later.
@@
 	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U_p}
-\end{equation}
-Consequently, the generated power $P_e$ expression is :
+	\label{eq:APG_elec}
+\end{equation}
+Consequently, the generated power $P_e$ is :
 \begin{equation}
@@
 \end{equation} 
-Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup.
-Also, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as showed in figure \ref{fig:HV_actuation_detail}.
+Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup. Where the hinges angle $\varphi$ is defined as :
+\begin{equation}
+	\varphi = \arctan\biggl(\dfrac{x_m}{L}\biggr)
+	\label{eq:phi_definition}
+\end{equation}
+Additionally, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$, as showed in figure \ref{fig:HV_actuation_detail}. 
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}
- m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
-				\ -2\alpha U_p \tan(\varphi)
+ m \ddot{x}_m =-2K_{eq}(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi(x_m)) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
+				\ -2\alpha U_p \tan(\varphi(x_m))
 				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - f_d \text{sign}(\dot{x}_m)
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{equation}
@@
 \end{equation}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align}
-	\text{Active cylinder ~}& \left\{~
-	F_{br} - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m = 0
-	\right.
-	\label{eq:equilibre_dynamique_piston_ouvert}\\
 	\text{Inactive cylinder ~}& \left\{~
@@
 \end{align}
-Where $p_c$ is the HC chamber pressure and $x_{hc,i}$ the piston position of the inactive HC piston.
-$F_{br}$ accounts for the OB counter-reaction on the HC.
-With the QS actuation assumption, it can be derived from equation \ref{eq:OB-GPA} and expressed as follows :
-\begin{align}
-	F_{br} = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr)
-	\label{eq:F_OB_xxxxxx}
-\end{align}
 The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
 \ref{fig:HV_actuation_detail}).
-$Cf$ will be as more important as $x_m$ increases.
-It is minimal when the HV is unbent and worth $Cf_0$.
-The literature does not provide the constitutive relation between $x_m$ and $Cf$, thus we preliminarily assume that it is linear and defined as follows :
+$Cf$ will be all the more important as $x_m$ increases.
+Its minimal value $Cf_0$ is obtained when the HV is unbent.
+We preliminarily assume that the relationship between $Cf$ and $x_m$ is linear and defined as follows :
 \begin{align}
-Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m 
+Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ |x_m| 
 \label{eq:Cf(x_m)_linear}
@@
 
-By the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
+Using the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
 \begin{align}
@@
 \end{align}
-Where $a_h$ is the hydraulic amplification ratio and $q$ the flow rate.
+Where $a_h$ is the hydraulic amplification ratio and $q$ the fluid flow rate.
 
@@
 	\item The transducer is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
-	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which admit operates at 1kPa pressure \cite{SMC2022}.
-	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale. $\epsilon$ can still be adjusted with $x_0$.
+	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which allow a 1kPa pressure operation \cite{SMC2022}.
+	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale.
 \end{itemize}
 
-The maximum theoretical energy in a BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ } to \mbox{$x_m=0$} (eq.
-\ref{eq:Ep_bar}).
-It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
-\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
-\begin{equation}
-	E_{pb} = \dfrac{K x_0^4}{3L^2} = n(p_c \cdot (\Delta V_{ear})_{max})
-	\label{eq:Ep_bar}
-\end{equation}
 The system is designed by setting the two coupled requirements allowing the system operation.
@@
 At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to guarantee the pressure limit.
-If not, $\epsilon$ can be decreased, diminishing the extracted energy.
+If not, $\epsilon$ (éq.
+\ref{eq:epsilon_def}) can be decreased, diminishing the extracted energy.
 \begin{empheq}[left=\empheqlbrace]{align} 
@@
 	\label{eq:contrainte_course}\\
-	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0^3}{3\sqrt{3}L^2}
+	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0\epsilon}{3\sqrt{3}}
 	\label{eq:contrainte_confort}
 \end{empheq}
+\begin{equation}
+	\epsilon = \dfrac{x_0}{L}
+	\label{eq:epsilon_def}
+\end{equation}
 Equations \ref{eq:contrainte_course} and \ref{eq:contrainte_confort} set the amplification level $a_h$ and the BR buckling level $\epsilon$.
@@
 A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. 
-The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs.
+The unknown remaining key parameter stays the hydraulic behavior $Cf(x_m)$ of the HVs. 
 The ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. 
@@
 \end{equation}
-The numerical resolution of the differential equations can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
+The numerical resolution of the coupled differential equations \ref{eq:APG_elec},\ref{eq:OB-GPA}, \ref{eq:equilibre_dynamique_piston_ferme}, \ref{eq:Bernoulli_piston_ouvert}, \ref{eq:Bernoulli_piston_ferme}, \ref{eq:conservation_masse}, \ref{eq:conservation_masse_ouvert} and \ref{eq:conservation_masse_ferme} can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
 	%///////////////////////////////////////////// 
@@
 By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
-\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
-$r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the active HV.
-The mastication cycle is identically quadrupled in order to test the system cycling robustness.
+\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled variables defining the harvester.
 The earplug is assumed to be a perfect flow rate source.
+The mastication cycle is identically used 4 times in order to test the system cycling robustness.
 The fixed, designed and resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
 
-Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
-The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), knowing that the gravity influence is not considered.
+Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results of the mass and the HC pistons positions over overlaid with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
+The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), noting that the gravity influence is not considered.
 The same figure shows a focused view on the two main phases of the harvester operation during the actuation by the \emph{"bottom"} HC.
@@
 \begin{itemize}
-	\item The mass is at the $-x_0$ equilibrium position.
+	\item The mass is at the \emph{"bottom"} equilibrium position $-x_0$.
 	\item The \emph{"top"} HV is closed ($Cf_{top} = Cf_c$) and the \emph{"bottom"} side HV is opened ($Cf_{bot} = Cf_0$).
@@
 During a first phase the BR mass is pushed until it reaches $x=0$.
-The fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
+The fluid exiting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
 The mass then crosses $x_m=0$ and the second phase begins.
 The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$).
-The fluid is then guided toward the \emph{"top"} side and there is no contact between the mass and a HC.
-The mass oscillates around $x_m=x_0$and the energy is harvested by the APG.
+The fluid is then directed toward the \emph{"top"} side and there is no contact between the mass and a HC.
+The mass oscillates around $x_m=x_0$ and energy is harvested by the APG.
 The adequate hydraulic actuation making the fluid flow toward the right HC is achievable when \mbox{$(r_{Cf})_{min}=26$}.
 
-Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with 20µJ harvested from one mastication.
+Additionally, figure \ref{fig:positions_Up_puissances_energies} presents the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
+The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with $22$µJ electrical energy harvested from one mastication.
 The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
-The energy source depends on the comfort pressure level $p_c$ that is set to 1kPa, i.e.
+The energy source is limited by the comfort pressure level $p_c$ that is set to 1kPa, i.e.
 a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
@@
 
-The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BR mass.
+The simulated model shows promising efficiency (tab.
+\ref{tab:parametres électromécaniques}) and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient (tab.
+\ref{tab:parametres_hydrauliques}) to ensure the adequate cycled actuation of the BR mass.
 Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
@@
     %/////////////////////////////////////////////
-The device heart is the electromechanical converter composed of the BR with the APG.
-They have been designed at the application scale in order to prove their feasibility.
-The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure with blades.
-This method optimizes the resonator quality factor by avoiding screw assemblies.
+The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure.
+This method optimizes the resonator quality factor by avoiding assemblies.
 Figure \ref{fig:BDT_OB+GPA} shows the BR mounted on the experimental test bench.
-The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations.
+The 8 hinges are realized by 4 buckled blades (BB) while a vertical guide beam (GB) ensures the APG mounting and avoids any of its rotations.
 The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
-They also maximize the BB compression stiffness that maximizes harvester efficiency, as we show in the following section.
+They also maximize the BB compression stiffness that maximizes harvester efficiency, as detailed in the following section.
 The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
@@
 APX4 steel elastic resistance  & $Re_{APX4}$               & 955[MPa]    \\
-Dimensions of a buckled blade  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
-Dimensions of the guide blade  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
+Dimensions of a buckled beam  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
+Dimensions of the guide beam  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
 % Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
 Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [N.m/rad] \\
-Stiffness of the guide blade along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
+Stiffness of the guide beam along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
 Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
@@
     %///////////////////////////////////////////// 
-	\subsection{BR blades design}	
+	\subsection{BR beams design}	
 	\label{subsec:BR blades design}
@@
 \end{equation}
-Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
-If the condition is respected, then $K_{eq}$ can be assimilated to $K$.
+Equations \ref{eq:eta_ob} - \ref{eq:K_eq} demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
+If the condition is respected, then $K_{eq}$ can be assimilated to $K$ and $\alpha_{eq} \approx \alpha$.
 
@@
 The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented on figure \ref{fig:BDT_OB+GPA}.
-An additional blade is mounted with the APG in order to prevent its rotation around any axis.
+An additional beam is mounted with the APG in order to prevent its rotation around any axis.
 A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$µm).
-The bearing decouples the rotation of the screw with the rotation of the blade structure in order to prevent unwanted torsional stress.
+The bearing decouples the rotation of the screw with the rotation of the beam structure in order to prevent unwanted torsional stress.
 Two symmetrically mounted masses are added on the initial central mass with a 45\degree{} machined plane.
@@
 %%%%%%%%%%%%%%%%
-The hydraulic restriction coefficient of HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
-In order to set an optimal angle operation range we must investigate the evolution $K_{HV}(\theta)$.
+The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
+Its hydraulic behavior respects the minimum criteria of \mbox{$(r_{Cf})_{min}=26$} and therefore can ensure the adequate hydraulic commutation to cycle the BR mass motion.
+In order to set an optimal angle operation range $\Delta\theta$ we must investigate the evolution $K_{HV}(\theta)$.
 This matter will not be discussed in this paper.
-The following section presents the recalibrated harvester model using the experimental data of the HV$_{T1}$ and the experimental data of the electromechanical converter.
+However, $\Delta\theta$ must be minimized in order to limit the energy needed for the HVs operation and also, $\theta_0$ must be minimized to reduce the hydraulic energy losses in the active branch.
+
+The following section presents the recalibrated harvester model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
 
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-	%/////////////////////////////////////////////
-	\subsubsection{Free release trials}
-	%/////////////////////////////////////////////
-
+
+The experimentally identified parameters have been implemented in the global multiphysic coupled model to enhance its predictability and to evaluate the harvester performances.
+The last matter is achieved by evaluating the mechanical influence of the HV$_{T1}$ through an experimental approach in order to identify the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
+
+	%/////////////////////////////////////////////
+	\subsection{Experimental evaluation of the mechanical impact of HV$_{T1}$}
+	%/////////////////////////////////////////////
+The HV$_{T1}$ has been mounted on the experimental test bench presented on figure \ref{fig:BDT_OB+GPA} and two experimental trials have been performed to identify the HV mechanical influence : free oscillations and oscillations with HV$_{T1}$ presence, during a harvesting phase.
+The mass is initially set on $x_m=x_0$ and then pushed toward $x_0$.
+The HV$_{T1}$ internal pressure is adjusted to 30kPa with an oil column, in order to be consistent with the simulated case (tab.
+\ref{tab:parametres_hydrauliques}).
+The oscillation phase begins when the mass crosses the $x_m=0$ position.
+In order to set $\theta_0$ we add an angle stopper that is shown in figure \ref{fig:contact_M_VH_lachers}.
+$\theta_c$ is then reached when the oscillations stop at $x_m=x_0$.
+The mass position and the APG tension are monitored during the tests.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 		\captionsetup{justification=centering}
-		\includegraphics[trim={9.9cm 0cm 0cm 9cm},clip,width=0.8\linewidth]{figures/contact_M_VH_lachers.pdf}
-		\caption{Image de la HV$_{T100p}$ lorsque $\theta_0$($x_m=-x_{0})$ et lorsque $\theta_f$($x_m=x_{0,HV}$)}
+		\includegraphics[trim={6.9cm 0cm 0cm 9cm},clip,width=0.9\linewidth]{figures/contact_M_VH_lachers.pdf}
+		\caption{HV$_{T1}$ picture for (a).$\theta_0(x_m=-x_{0})$ and for (b).$\theta_f(x_m=x_0$).}
 		\label{fig:contact_M_VH_lachers}
@@
 
-	%/////////////////////////////////////////////
-	\subsubsection{Recalibrated model}
-	%/////////////////////////////////////////////
-The simulation with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA}.
-The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
+The global model parameters listed in table \ref{tab:parametres lacher tube} are recalibrated for both test configurations by iterative simulations. 
+The simulations with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA} concerning the harvesting phase of both configurations.
+
+After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamics behavior of the harvester is theoretically predictable by the established model.
+The comparison between the results of the two tests reveal the mechanical impact of the HV. 
+The stiffness at $\theta_c$ is calculated with $x_0$ evolution between the two tests and equation \ref{eq:OB-GPA}. 
+The quality factor decrease is a result of the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
+The HV adds a supplementary dynamic mass in the BR.
+The electromechanical coupling coefficient is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[!htbp]	
-		\centering
-		\captionsetup{justification=centering}
-		\includegraphics[trim={17cm 0cm 0cm 6cm},clip,width=\linewidth]{figures/correlation_simu-exp_OB+GPA.pdf}
-		\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres_lacher_free}.}
-		\label{fig:BDT_OB+GPA}
+\captionsetup{justification=centering}
+	\begin{subfigure}{.49\linewidth}
+		\includegraphics[trim={9cm 0cm 0cm 0cm},clip,width=\linewidth]{figures/recalage_free.pdf}
+		\caption{Free oscillations}
+		\label{fig:recalage_free}
+	\end{subfigure}
+	\begin{subfigure}{.49\linewidth}
+		\includegraphics[trim={8.6cm 0cm 0cm 0cm},clip,width=\linewidth]{figures/recalage_tube.pdf}
+		\caption{Oscillations with HV$_{T1}$ presence}
+		\label{fig:recalage_tube}
+	\end{subfigure}
+	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres lacher tube}.}
+	\label{fig:recalage_global}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	%/////////////////////////////////////////////
+	\subsection{Recalibrated coupled model}
+	%/////////////////////////////////////////////
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \multicolumn{1}{c}{\textbf{Parameter}}	&
-\multicolumn{1}{c}{\textbf{Value OB}} 	& 
-\multicolumn{1}{c}{\textbf{Value OBVH}}  \\
+\multicolumn{1}{c}{\textbf{BR}} 	& 
+\multicolumn{1}{c}{\textbf{BR+VH$_{T1}$}}  \\
 \midrule
-$D_r$ [mm] 						& \cellcolor{ashgrey} 		& \textcolor{red}{4} 		\\ \hline
-$\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& \textcolor{red}{{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
-$K_{T100p}(\theta_f)$ [Nmm/rad] & \cellcolor{ashgrey}  		&  0.27 					\\ \hline
+$D_r$ [mm] 						& \cellcolor{ashgrey} 		& {4} 		\\ \hline
+$\Delta\theta$ [deg] 			& \cellcolor{ashgrey} 		& {{[$\approx$ 19 ; $\approx$ 36]}} \\ \hline
+$K_{T1}(\theta_c)$ [Nmm/rad]	& \cellcolor{ashgrey}  		&  0.27 		\\ \hline
 $a$ [mm]         			    & \cellcolor{ashgrey}  		&  2.24		\\ \hline
@@
 $K$ [N/m] 						&	84480			  	 	&  84480  			\\ \hline
-$x_0$ [mm] 						& \textcolor{red}{0.59}		& \textcolor{red}{0.50}  	\\ \hline
+$x_0$ [mm] 						& {0.59}					& {0.50}  	\\ \hline
 $Q$	[-] 						& 		24.0		 		& 5.0     					\\ \hline
-$k^2_{sys}$ [\%] 				& 		1.25		 		& \textcolor{red}{1.25}   	\\ \hline
+$k^2_{sys}$ [\%] 				& 		1.25		 		& {1.25}   	\\ \hline
 $\eta_{br}$ [\%] 				& 		11.9		 		& 2.6   \\ \hline	
-$R_l$ [k$\text{\ohm}$] 		&	\textcolor{red}{15.5}	& \textcolor{red}{15.5}    	\\ \hline		
-$m$	[g]						    &	\textcolor{red}{5.88}	& 9.00   					\\ \hline	
+$R_l$ [k$\text{\ohm}$] 			&	{15.5}					& {15.5}   	\\ \hline		
+$m$	[g]						    &	{5.88}					& 9.00   		\\ \hline	
 $f_0$ [Hz]						&		32.9				& 27.9   					\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

### 2022-10-21 article_system.tex
update revisions_FF part2 + lasts sections

@@
 Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
-	\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={19.7cm 0cm 0cm 13cm},clip, width=0.7\linewidth]{figures/hydraulic_mechanic_interface.pdf}
-	\caption{Hydraulic source exploitation depending on the mechanical load}
-	\label{fig:hydraulic_mechanic_interface}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
+\begin{equation}
+	\Delta p_{ear}S_{hc} = K_s x_m
+	\label{eq:hydraulic-mechanic_interface}
+\end{equation}
+Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as :
 \begin{equation}
@@
     %///////////////////////////////////////////// 
-	\subsection{The electromechanical converter presentation}	
+	\subsection{Electromechanical converter presentation}	
 	\label{The electromechanical converter presentation}
@@
 Stiffness of the guide beam along $\vec{y}$  & $K_{gb}$    & 190 [N/m] \\
-Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
-Stiffness of the APG along $\vec{z}$          & $K$        & 252  [kN/m]\\
 			\bottomrule
@@
 
-In order to preserve an adequate mechanical transmission from the mass to the APG, we must ensure that no secondary buckling mode does appear on the BBs during the BR operation.
 When the mass crosses the unstable \mbox{$x_m=0$} position, the compression force $F_{z,0}$ induces the maximum stress on the BB.
-$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement} relying on figure \ref{fig:schema_cinematique1}.
+$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement}.
+$K_{bb}$ can then be assured if the compression efforts absorbed by the BBs do not induce any secondary buckling mode during the BR operation.
 \begin{equation}
@@
 \end{equation}
-The problem was treated with a FEM model and the results are summarized through the figure \ref{fig:buckling_limit}.
-It reveals that the first secondary undesirable modes appear for $F_{z,0}=6.4$N.
-The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity.
-Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BR, as presented on figure.
-The preliminary simulated case presented in the previous section is well located in the preferable domain where there is no undesirable buckling modes.
-Moreover, the force absorbed by the APG is well under the maximal limit of 18N from which the device could be damaged.
+The beams design was obtained using a FEM model which result is summarized in the figure \ref{fig:buckling_limit}.
+It reveals that the first secondary undesirable buckling mode appears for $F_{z,0}=6.4$N.
+If it happens, the compression force is not transmitted from the mass to the APG.
+$K_{bb}$ is then not assured and therefore $k^2_{sys}$ is diminished (eq.
+\ref{eq:k2_sys}).
+We establish a buckling height domain (fig.
+\ref{fig:buckling_limit}) to avoid their appearance for the fabricated BR.
+The preliminary simulated case presented in the previous section is in the preferable domain.
+Moreover, the force absorbed by the APG is assured to be under the maximal limit of 18N from which the device could be damaged.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An additional beam is mounted with the APG in order to prevent its rotation around any axis.
-A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$µm).
-The bearing decouples the rotation of the screw with the rotation of the beam structure in order to prevent unwanted torsional stress.
-Two symmetrically mounted masses are added on the initial central mass with a 45\degree{} machined plane.
-The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$µm).
-The APG power is dissipated in the $R_l$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
+A micrometric screw sets the initial buckling level $x_0$ ($\pm 10$µm).
+The bearing decouples the rotation of the screw with the beam structure in order to prevent unwanted torsional stress.
+The central mass $\degree{45}$ place receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position.
+The APG power is dissipated in the $R_l$ resistor and the $U_p$ voltage ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
 Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
+The HV mechanical influence is not considered here in order to focus on the electromechanical converter dynamic behavior.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behavior.
-The mass is guided by a HC from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then oscillates around the opposite stable equilibrium position.
-The experimental data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
+
+The mass is pushed by a HC from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then oscillates around the opposite stable equilibrium position.
+The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
+This data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
 \ref{tab:parametres_lacher_free}).
-The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ can also be calculated.
+The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ were also calculated.
 %%%%%%%%%%%%%%%%%
@@
 	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
-	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
+	$K_{eq}$                  & 2.56e5 N/m            & 0.85e5 N/m 		\\
+	$K_{bb}$                  & 14.2e5 N/m            & 1.27 N/m 		\\
 	${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
@@
 %%%%%%%%%%%%%%%%%%%%%
-    %/////////////////////////////////////////////
-
+
+Experimental $K_{bb}\approx K/2$ can be calculated from the identified $K_{eq}$ with equation \ref{eq:K_eq}, supposing $K_{gb}$ negligible (tab. \ref{tab:parametres_lames}).
+    %///////////////////////////////////////////// 
 	\subsection{Analyze and summary}	
@@
 \ref{tab:parametres électromécaniques}).
-The efficiency drop is consistent with the quality factor and the electromechanical coupling coefficient drop (eq.
+The efficiency drop is mainly associated with the quality factor and the electromechanical coupling coefficient drop (eq.
 \ref{eq:eta_ob}).
 
-Two major factors could have led to such results.
-First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
-Then, small undulations have been observed on the BBs after fabrication and could also have gotten worse during the manipulation.
-These undulations reduce $K_{bb}$, diminishing $k^2_{sys}$ according equations \ref{eq:k2_sys}-\ref{eq:K_eq}.
+The quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
+The small undulations have been observed on the BBs after fabrication and could also have gotten worse during the manipulation.
+These undulations aid the appearance of secondary buckling modes and contribute to reduce $K_{bb}$, diminishing $k^2_{sys}$ according equations \ref{eq:k2_sys}-\ref{eq:K_eq}.
 Improvements are proposed later in order to reduce the energy losses during this stage.
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-In order to validate the feasibility of the HVs we adopted an experimental approach to find the material and geometrical parameters of the tube capable to achieve $(r_{Cf})_{min}=26$ (tab.
+In order to validate the feasibility of the HVs we adopted an experimental approach to find the material and geometrical parameters of the tube to achieve $(r_{Cf})_{min}=26$ (tab.
 \ref{tab:parametres_hydrauliques}).
-A HV composed of a kapton tube \cite{Dupont2012} of initial diameter $D_t=1.05$mm and thickness $th_t=25$ µm was found to meet this hydraulic criteria.
+A buckled kapton tube \cite{Dupont2012} of internal diameter $D_t=1.05$mm and thickness $th_t=25$ µm was found to meet this hydraulic criteria.
 It will be called HV$_{T1}$ afterwards.
@@
 Figure \ref{fig:essais_hydraulique_VH} shows the HV$_{T1}$ during the experimental characterizations on the hydraulic test bench.
-An electromechanical rotary plate is monitored on LabVIEW interface and imposes the bending angle $\theta$.
-A liquid filled syringe is emptied through the HV$_{T1}$ and its exciting flow rate $q_{ser}$ is deduced by tracking its moving piston displacement.
+An electromechanical rotary plate is monitored on LabVIEW interface and imposes a bending angle $\theta$.
+A liquid filled syringe fixes the fluid flow through the HV$_{T1}$ and $q_{ser}$ is evaluated by tracking the syringe piston displacement.
 The pressure loss coefficient $Cf_{T1}$ is calculated as \mbox{follows :}
 \begin{equation}
-	Cf_{T1} = \dfrac{p_1-p_2}{q_{ser}^2}
-\end{equation}
-Where $p_1$ and $p_2$ are respectively the fluid pressure monitored before entering and after exciting the HV$_{T1}$.
+	Cf_{T1} = \dfrac{p_1-p_2}{q_{syr}^2}
+\end{equation}
+Where $p_1$ and $p_2$ are the fluid pressure monitored before entering and after exciting the HV$_{T1}$ respectively.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-The emptying procedure was repeated 7 times for $\theta$ varying from $0^{\circ}$ to $60^{\circ}$ with $10^{\circ}$ increments.
+The tests were repeated 7 times for $\theta$ varying from $0^{\circ}$ to $60^{\circ}$ with $10^{\circ}$ increments.
 The experimental results are plotted on figure \ref{fig:resultats_essais_hydraulique_VH_D1mm}.
@@
 	\captionsetup{justification=centering}
-	\includegraphics[trim={15.5cm 0cm 0cm 3.6cm},clip,width=0.6\linewidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
+	\includegraphics[trim={15.5cm 0cm 0cm 3.6cm},clip,width=0.7\linewidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
 	\caption{Hydraulic characterization of the HV$_{T1}$.}
@@
 %%%%%%%%%%%%%%%%
-The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
+The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to $r_{Cf}60$ if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
 Its hydraulic behavior respects the minimum criteria of \mbox{$(r_{Cf})_{min}=26$} and therefore can ensure the adequate hydraulic commutation to cycle the BR mass motion.
@@
 
-The following section presents the recalibrated harvester model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
+The following section presents the harvester model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
+
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{GLOBAL MODEL RECALIBRATION WITH \mbox{EXPERIMENTAL} DATA}
 \label{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
@@
 The experimentally identified parameters have been implemented in the global multiphysic coupled model to enhance its predictability and to evaluate the harvester performances.
-The last matter is achieved by evaluating the mechanical influence of the HV$_{T1}$ through an experimental approach in order to identify the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
-
-	%/////////////////////////////////////////////
-	\subsection{Experimental evaluation of the mechanical impact of HV$_{T1}$}
+The mechanical influence of the HV$_{T1}$ is identified with an experimental approach characterizing the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
+
+	%/////////////////////////////////////////////
+	\subsection{Recalibration with release trials}
 	%/////////////////////////////////////////////
 The HV$_{T1}$ has been mounted on the experimental test bench presented on figure \ref{fig:BDT_OB+GPA} and two experimental trials have been performed to identify the HV mechanical influence : free oscillations and oscillations with HV$_{T1}$ presence, during a harvesting phase.
+Thus, the dynamics difference between the two tests focus on the HV$_{T1}$ mechanical influence.
+
 The mass is initially set on $x_m=x_0$ and then pushed toward $x_0$.
@@
 The oscillation phase begins when the mass crosses the $x_m=0$ position.
-In order to set $\theta_0$ we add an angle stopper that is shown in figure \ref{fig:contact_M_VH_lachers}.
+In order to set $\theta_0$ we add two angle stoppers illustrated on figure \ref{fig:contact_M_VH_lachers}.
 $\theta_c$ is then reached when the oscillations stop at $x_m=x_0$.
@@
 After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamics behavior of the harvester is theoretically predictable by the established model.
-The comparison between the results of the two tests reveal the mechanical impact of the HV. 
-The stiffness at $\theta_c$ is calculated with $x_0$ evolution between the two tests and equation \ref{eq:OB-GPA}. 
-The quality factor decrease is a result of the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
-The HV adds a supplementary dynamic mass in the BR.
-The electromechanical coupling coefficient is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.  
+The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and equation \ref{eq:OB-GPA}.
+The HV$_{T1}$ adds a supplementary dynamic mass in the BR and changes the oscillation frequency.
+The electromechanical coupling coefficient is not influenced by the HV presence.
+The quality factor decreases and the dry friction coefficient is calculated from the drop.
+Moreover, $a$ and $\Delta\theta$ are graphically evaluated.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	%/////////////////////////////////////////////
-	\subsection{Recalibrated coupled model}
-	%/////////////////////////////////////////////
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \multicolumn{1}{c}{\textbf{BR}} 	& 
-\multicolumn{1}{c}{\textbf{BR+VH$_{T1}$}}  \\
+\multicolumn{1}{c}{\textbf{BR+HV$_{T1}$}}  \\
 \midrule
@@
 $k^2_{sys}$ [\%] 				& 		1.25		 		& {1.25}   	\\ \hline
-$\eta_{br}$ [\%] 				& 		11.9		 		& 2.6   \\ \hline	
+$\eta_{br}$ [\%] 				& 		12.9		 		& 2.6   \\ \hline	
 $R_l$ [k$\text{\ohm}$] 			&	{15.5}					& {15.5}   	\\ \hline		
@@
 \end{table}        
+	%/////////////////////////////////////////////
+	\subsection{Analyse and discussion}
+	%/////////////////////////////////////////////
+The experimental hydraulic behavior of the HV$_{T1}$ is theoretically capable to provide \mbox{$r_{Cf}>26$} and ensure the hydraulic adequate commutation cycling the BR mass motion.
+
+The quality factor decrease results from the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
+The friction losses can be minimized by an order of magnitude by using materials with low friction coefficient like teflon \cite{Nosonovsky2013}.
+The HV-mass contact can also profit from magnetic interactions instead of direct rubbing.
+
+The global electromechanical coupling is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.
+The major part of the energy loss is due to the $k^2_{sys}$ drop as a result of the softening of the BBs from the prototype fabrication and manipulation.
+It can be minimized by using thicker BBs while taking care that the buckling domain does not reach the critical point where the APG could be damaged (fig.
+\ref{fig:buckling_limit}).
+With $200$µm thick BBs instead of $75$µm, we can expect 26\% improvement on $\eta_{br}$ (eqs.
+\ref{eq:eta_ob}-\ref{eq:K_eq}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+This work emphasizes the energy need for hearing aids and the exploitation of the mechanical deformation of the ear canal as a solution to enhance the autonomy of those devices batteries.
+
+A new energy harvester architecture maximizing the energy conversion efficiency is proposed.
+A hydraulic, mechanical and electrical coupled model is established.
+Its numerical evaluation predicts that the system can theoretically harvest 76\% of the available energy with a hydraulic extraction method.
+The dynamic behavior and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
+A new concept of HVs is proposed, based on the bending buckling of flexible tubes.
+A HV design is proposed with experimental investigation based on the theoretical needed behavior extracted from the numerical simulations.
+
+The experimental data are used to recalibrate the harvester multiphysic model and to evaluate its performances.
+The global predicted efficiency is $\eta_g=2.6\%$.
+The energy losses factors are identified and solutions are proposed in order to reduce them for a next generation of prototypes.
 

### 2022-10-31 article_system.tex
Avant collage Overleaf avec corrections de Jérémie

@@
 
-\title{Ear canal dynamic motion piezoelectric energy harvester using a bistable resonator cycled by coupled hydraulic switches made of collapsed flexible tubes.}
+\title{Toward a novel piezoelectric energy harvester for ear canal dynamic motion exploitation, using a bistable resonator cycled by coupled hydraulic valves made of collapsed flexible tubes}
 
@@
 \begin{abstract}
-%% Text of abstract
+Scavenging energy from the ear canal dynamic motion during jaw motion may be a practical way to enhance the battery autonomy of hearing aids.
+One of the main challenges is to optimize the extracted energy while coping with the constraints associated to soft human tissues and restricted ear canal volume.
+We propose a new concept of harvester made of a liquid filled earplug transferring the energy outside the ear canal to a generator.
+It is composed oa hydraulic amplifier, two hydraulic cylinders actuating a bistable resonator raising the source frequency driving an amplified piezoelectric transducer to generate electricity.
+The cycling of the resonator is achieved using two innovative flexible hydraulic valves based on the buckling of flexible tubes.\\
+A multiphysic coupled model is established in order to determine the system operation requirements and to evaluate its theoretical performance.
+It exhibits a theoretical energy conversion efficiency of 85\%.
+The electromechanical performance of the resonator couple to the piezoelectric transducer as well as the hydraulic behavior of the valves are experimentally investigated.
+The global model is updated with the experimental data to ameliorate its predictability for a further optimized design.
+The energy losses are identified, which allow an entire design proposed to improve the experimental energy conversion efficiency to 26\%.
+
 \end{abstract}
@@
 \begin{keyword}
-%% Keywords
+Energy harvesting, frequency-up, ear canal, multiphysic, hydraulic valve
 \end{keyword}
@@
 The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
-Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier and the liquid filled earplug.
+Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the HA and the liquid filled earplug.
 
@@
 In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
-Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier.
-These hydraulic components will rather be considered for further work.
+Hence, this section neglects the energy loss inside the HA and the HCs.
+These hydraulic components will rather be considered in further work.
 
@@
 Additionally, figure \ref{fig:positions_Up_puissances_energies} presents the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with $22$µJ electrical energy harvested from one mastication.
+The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\%} with $22$µJ electrical energy harvested from one mastication.
 The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
@@
 \midrule
-$K$	[N/µm]		&	0.256		\\	\hline
+$K_{eq}$	[N/µm]	&	0.256		\\	\hline
 $x_0$ [mm]			&	0.49		\\	\hline
@@
 $Q$ [-]				&	50			\\	\hline
-$\eta_g$ [\%]		& 	76			\\
+$\eta_g$ [\%]		& 	85			\\
 \bottomrule
@@
 Dimensions of the guide beam  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
-% Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
 Soft hinge stiffness		  & $K_{\varphi}$             & 0.006 [N.m/rad] \\
 Stiffness of the guide beam along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
+Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
+Stiffness of the APG along $\vec{z}$          & $K$        & 252  [kN/m]\\
 			\bottomrule
@@
 \begin{equation}
-	\eta_{ob} = \dfrac{k^2_{sys}\ Q}{k^2_{sys}\ Q + 2}
+	\eta_{br} = \dfrac{k^2_{sys}\ Q}{k^2_{sys}\ Q + 2}
 	\label{eq:eta_ob}
@@
 It depends on the APG PFF the and ratio between the equivalent stiffness $K_{eq}$ (eq.
-\ref{eq:K_eq}) of the structure on the $\vec{x}$ axis and the equivalent stiffness of the APG mounted on the GB.
+\ref{eq:K_eq}) of the structure on the $\vec{z}$ axis and the equivalent stiffness of the APG mounted on the GB.
 \begin{equation}
@@
 	$K_{eq}$                  & 2.56e5 N/m            & 0.85e5 N/m 		\\
-	$K_{bb}$                  & 14.2e5 N/m            & 1.27 N/m 		\\
+	$K_{bb}$                  & 14.2e5 N/m            & 1.27e5 N/m 		\\
 	${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
-	$\eta_{br}$               & 75 \%                 & 12.9 \%   		\\
+	$\eta_{br}$               & 85 \%                 & 12.9 \%   		\\
 	\bottomrule
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]
+\begin{figure}[!htb]
 \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure}[!htbp]
+\begin{figure}[!htb]
 	\begin{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htbp]	
+\begin{figure}[!htb]	
 \captionsetup{justification=centering}
@@
 A hydraulic, mechanical and electrical coupled model is established.
-Its numerical evaluation predicts that the system can theoretically harvest 76\% of the available energy with a hydraulic extraction method.
+Its numerical evaluation predicts that the system can theoretically harvest 85\% of the available energy with a hydraulic extraction method.
 The dynamic behavior and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
@@
 The experimental data are used to recalibrate the harvester multiphysic model and to evaluate its performances.
-The global predicted efficiency is $\eta_g=2.6\%$.
-The energy losses factors are identified and solutions are proposed in order to reduce them for a next generation of prototypes.
+The global experimental efficiency is evaluated to $2.6$\%.
+The energy losses factors are identified and solutions are proposed in order to increase the efficiency up to 26\%.
 

### 2022-10-31 article_system.tex
Après corrections Jérémie

--- 2022-10-20 article_system.tex
@@
 % For subfigures
+
 \usepackage{subcaption}
@@
 \usepackage{empheq}
-\usepackage{textcomp}
-\usepackage{multicol}
 \usepackage{graphicx}
@@
 \def \hfillx {\hspace*{ -\linewidth} \hfill} % remplir espacement horizontal entre deux sous-figures de façon à remplir toute la largeur du texte.
-% \renewcommand{\degree}[1]{${#1}^\circ$} % °
-
 %----------------------------------------------------------------------
@@
 
-\title{Ear canal dynamic motion piezoelectric energy harvester using a bistable resonator cycled by coupled hydraulic switches made of collapsed flexible tubes.}
+\title{Toward a novel piezoelectric energy harvester for earcanal dynamic motion exploitation, using a bistable resonator cycled by coupled hydraulic valves made of collapsed flexible tubes}
 
@@
 \address[symme]{Laboratoire SYMME - Université Savoie Mont Blanc, 7 Chemin de Bellevue, 74940, Annecy}
-\address[critias]{Université du Québec - École de technologie supérieure, 1100 Rue Notre-Dame Ouest, Montréal, QC, H3C 1K3}
+\address[critias]{Université du Québec - École de technologie supérieure, Montréal, QC, H3C 1K3}
 
@@
 
-\author[critias]{Michel DEMUYNCK}
+%\author[critias]{Michel DEMUYNCK}
 \author[critias]{Aidin DELNAVAZ}
@@
 \begin{abstract}
-%% Text of abstract
+Scavenging energy from the earcanal dynamic motion during jaw motion may be a practical way to enhance the battery autonomy of hearing aids.
+One of the main challenges is to optimize the extracted energy while coping with the constraints associated with soft human tissues and restricted earcanal volume.
+We propose a new concept of harvester made of a liquid filled earplug transferring the energy outside the earcanal to a generator.
+It is composed oa hydraulic amplifier, two hydraulic cylinders actuating a bistable resonator raising the source frequency driving an amplified piezoelectric transducer to generate electricity.
+The cycling of the resonator is achieved using two innovative flexible hydraulic valves based on the buckling of flexible tubes.\\
+A multiphysics coupled model is established in order to determine the system operation requirements and to evaluate its theoretical performance.
+It exhibits a theoretical energy conversion efficiency of 85\%.
+The electromechanical performance of the resonator couple to the piezoelectric transducer as well as the hydraulic behaviour of the valves are experimentally investigated.
+The global model is updated with the experimental data to ameliorate its predictability for a further optimized design.
+The energy losses are identified, which allow an entire design proposed to improve the experimental energy conversion efficiency to 26\%.
 \end{abstract}
@@
 \begin{keyword}
-%% Keywords
+Energy harvesting, frequency-up, earcanal, multiphysics, hydraulic valve
 \end{keyword}
@@
 		APG                      & Amplified piezoelectric generator                       \\
-		BB                       & Buckled beam                                           \\
+		BB                       & Buckled blade                                           \\
 		BR                       & Bistable resonator                                      \\
-		GB                       & Guide beam                                             \\
+		GB                       & Guide blade                                             \\
 		HA                       & Hydraulic amplifier                                     \\
@@
 Energy harvesting methods have been studied in order to complement their power supply and enhance the autonomy of the batteries.
-In-ear devices such as hearing aids and cochlear implants are powered by disposable cells or rechargeable batteries.
+In-ear devices such as hearing aids and cochlear implant are powered by disposable cells or rechargeable batteries.
 The energy consumption of the best integrated devices in the literature rises up to $17$J for a 10 hours daily use \cite{Scherer2019,Yip2015,Kulah2022}.
@@
 Another statistical study revealed that the majority of hearing aids and cochlear implants users prefer disposable batteries for the long autonomy, but would have liked rechargeable solutions if the battery cycle was sufficient to complete the day \cite{PracticesAudiology2016}.
-Also, the long term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable cells.
+Also, the long-term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable cells.
 These arguments motivated the development of energy harvesting systems.
 
-The common energy sources are solar or wind energy but their availability in the low size environment of the application context makes them not suitable for exploitation.
+The common energy sources are solar or wind energy but their availability in the low-size environment of the application context makes them not suitable for exploitation.
 The activities of the human body generate a considerable amount of energy of different natures.
 Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, the kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, the body heat thermal energy \cite{Kim2014}, the strain energy from the skin deformation \cite{Jin2021} could be harvested for in-ear applications.
-An interesting energy source for cochlear implants or hearing aids appears to be the ear canal mechanical deformation as it is directly located in the area of the application.
-Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes de ear canal geometry during mastication.
-Carioli \emph{et al.} then used a customized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016}.
+An interesting energy source for cochlear implants or hearing aids appears to be the earcanal mechanical deformation as it is directly located in the area of the application.
+Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes earcanal geometry during mastication.
+Carioli \emph{et al.} then used a customized earplug moulding technique with a 3D scanner to reveal a global bending movement and a local compression area in the earcanal during mastication \cite{Carioli2016}.
 These two mechanical deformations represent a potential energy source that can be exploited.
@@
 Delnavaz \emph{et al.} developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013}.
-The earplug has been molded on the subject in order to maximize the contact surface with the ear canal.
+The earplug has been moulded on the subject in order to maximize the contact surface with the earcanal.
 The harvester is capable of exploiting both the flexion and the compression energy sources.
@@
 A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
-The energy is extracted by a liquid filled earplug whose internal volume vary as a result of the radial compression of the ear canal internal walls during the jaw movements.
+The energy is extracted by a liquid filled earplug whose internal volume varies as a result of the radial compression of the earcanal internal walls during the jaw movements.
 This variation put into motion a moving magnet translating in a water column surrounded by a coil.
@@
 The prototype appeared to be less efficient than the PVDF earplug.
-This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}.
-However, the hydraulic transmission allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume.
-
-Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion.
+This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57\,Hz) and a small-scale application \cite{Kulah2008,Priya2017}.
+However, the hydraulic transmission allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small earcanal volume.
+
+Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the earcanal dynamic motion.
 The next section states on the hydraulic energy source characterization and on the harvesting strategy that we adopted.
 Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle.
-Section \ref{sec:SYSTEM MODELING} details the global system modeling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester.
+Section \ref{sec:SYSTEM MODELING} details the global system modelling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behaviour of the harvester.
 Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} then exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling.
@@
     %/////////////////////////////////////////////
-Human tissue requires soft flexible materials in order to extract the ear canal deflection energy without causing discomfort.
+Human tissue requires soft flexible materials in order to extract the earcanal deflection energy without causing discomfort.
 However, flexible transducers admit low energy conversion efficiency as a part of the extracted energy is dissipated in the elastic non-active material.
@@
 
-To date, the best solution proposed in the literature consists on using soft materials as the piezoelectric PVDF earplug previously introduced \cite{Delnavaz2013}.
+To date, the best solution proposed in the literature consists of using soft materials as the piezoelectric PVDF earplug previously introduced \cite{Delnavaz2013}.
 The low mechanical impedance of the soft tissue in fact limits the use of more effective rigid piezoelectric materials.
 
-The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but allows to transmit the energy outside the ear canal and benefit so from larger effective space.
-The latter is in fact essential as it becomes then possible to implement an impedance adaption stage and more effective transducing methods that could not fit directly inside the ear canal restricted volume.
+The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but allows to transmit the energy outside the earcanal and benefit so from larger effective space.
+The latter is in fact essential as it becomes then possible to implement an impedance adaptation stage and more effective transducing methods that could not fit directly inside the earcanal limited volume.
 In fact, Marin \emph{et al.} demonstrated that the power generated by piezoelectric or electromagnetic transducers is as much better as the effective volume of transducing material is high \cite{Marin2011}.
-The present work is then based on the exploitation of the ear canal by a liquid filled earplug.
-As energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
-In order to optimize the energy extraction, the earplug must fit the ear canal wall.
+The present work is then based on the exploitation of the earcanal by a liquid filled earplug.
+As an energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
+In order to optimize the energy extraction, the earplug must fit the earcanal wall.
 Turcot \emph{et al.} demonstrated that the initial pressurization must reach a minimum of $14$kPa to achieve a good fit \cite{TURCOT2011}.
@@
 	\includegraphics[trim={20.5cm 0cm 0cm 10.8cm},clip, width=0.4\textwidth]{figures/deltaV_ear.pdf}
-	\caption{Ear canal volume variation for one mastication cycle}
+	\caption{Earcanal volume variation for one mastication cycle}
 	\label{fig:deltaV_ear}
@@
 
-The earplug operation characteristic behavior has not been studied yet.
+The earplug operation characteristic behaviour has not been studied yet.
 Thus, the evolution of the volume variation $\Delta V_{ear}$ is not well known as a function of the pressure variation $\Delta p_{ear}$.
 Then, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with the maximum values of $\Delta p_{ear}$ et $\Delta V_{ear}$ that have been recorded, i.e.
-$p_c=12kPa$ and $(\Delta V_{ear})_{max}=60$mm$^3$.
+$p_c=12$\,kPa and $(\Delta V_{ear})_{max}=60$\,mm$^3$.
 $p_c$ stands for the comfort pressure by assuming that the user could feel discomfort if $\Delta p_{ear}>p_c$.
-The energy estimation presumes that the earplug is a perfect flow rate source, which is a theoretical hypothesis leading to $0.9$mJ available from one mastication.
-Based on 2200 mastication cycles per day, according to \cite{Goll2011}, there would be $2$mJ available per day, per ear.
-This amount of energy could theoretically enhance supply $23.5$\% of the $17$J of needed for the state of the art of cochlear implants \cite{Kulah2022}.
+The energy estimation presumes that the earplug is a perfect flow rate source, which is a theoretical hypothesis leading to $0.9$\,mJ available from one mastication.
+Based on 2200 mastication cycles per day, according to \cite{Goll2011}, there would be $2$\,mJ available per day, per ear.
+This amount of energy could theoretically enhance supply $23.5$\,\% of the $17$\,J of needed for the state of the art of cochlear implants \cite{Kulah2022}.
 Further research in both domains related to hearing aids and energy harvesting could lead to fully autonomous devices in the future.
 \begin{align}
-	\text{max}(E_{hyd}) = p_c \cdot (\Delta V_{ear})_{max} = 0.9\text{mJ}
+	\text{max}(E_{hyd}) = p_c \cdot (\Delta V_{ear})_{max} = 0.9\text{\,mJ}
 	\label{eq:max_hydraulic_energy}
@@
     %///////////////////////////////////////////// 
-	\subsection{Harvesting strategy}	
+	\subsection{The harvesting strategy}	
 	\label{The harvesting strategy}
@@
 Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources.
-The power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
+In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy sources decreases \cite{Priya2017,Kulah2008}.
 Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.
-
-Piezoelectric ceramics appear like good candidates for mechanical energy transduction at small scales, but their high stiffness can limit their use on soft materials as human tissues.
-Mechanical amplifiers like flextensional structures can nevertheless be used to adapt the stress/displacement levels between the energy source and the transducing stiff material \cite{Abdelnaby2016}.
-Also, the best energy conversion efficiency for piezoelectric ceramics is achieved for at the transducer resonance.
-As the mean mastication frequency is estimated to \mbox{$1.57$Hz}, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of the transducer.
+Thus, piezoelectric ceramics appear like good candidates, but they cannot be easily used because of their high stiffness and their high resonance frequencies (>$1.57$\,Hz).
+Therefore, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of piezoelectric ceramic transducers.
 A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
-Stoppers however dissipate energy.
-Alternative solutions use mechanically bistable resonators (BR) \cite{Vocca2012}.
+Stoppers, however, dissipate energy.
+Alternative solutions use mechanically bistable resonators (BR) to perform frequency-up \cite{Vocca2012}.
 Recent works led to the development and optimization of  bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}.
 They show enhanced performances due to high electromechanical coupling.
-The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
-
+
+We can estimate the best choice maximizing the energy extraction from the hydraulic source.
+To be harvested, the energy has to be stored in a mechanical potential reservoir at first, to be then converted in electricity by the transducer.
 The hydraulic-mechanic interface can be a hydraulic cylinder (HC).
-It can store the energy in the frequency-up converter by actuating it at the frequency of human mastication.
-The amount of extractable energy from the hydraulic source will then depend on the mechanical stage behavior.
-Before being converted in electricity, the energy is in fact stored in a mechanical potential reservoir.
+It could store then the energy in the frequency-up converter by actuating it at the frequency of human mastication.
+Figure \ref{fig:hydraulic_mechanic_interface} schematizes the mechanical interaction between the HC and the resonator assimilated to a spring of stiffness $K_s$.
 During the low frequency actuation, the forces applied on each side of the HC piston are equal.
 Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+	\Delta p_{ear}\ S_{hc} = K_{s}\ x_{m}
+	\label{eq:hydraulic-mechanic_interface}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-Thus, the linear solution can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
-
-Non-linear elastic potential reservoirs can also be considered.
-This work presents the energy extraction capability of a BR governed by a Duffing equation.
-It admits 2 stable equilibrium positions \mbox{$x_m=\pm x_0$}, an unstable one in \mbox{$x_m=0$} and its stiffness depends on its structural buckling level $\epsilon$ defined later in equation \ref{eq:epsilon_def}.
-The maximum theoretical energy in the BR for a quasi-static actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$} to \mbox{$x_m=0$} (eq.
-\ref{eq:Ep_bar}).
-It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
-\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
-\begin{equation}
-	E_{pb} = \dfrac{K x_0^2\epsilon^2}{3} = n(p_c \cdot (\Delta V_{ear})_{max})
-	\label{eq:Ep_bar}
-\end{equation}
-We see later that it is inherently capable of exploiting $65$\% from the hydraulic energy source, which is $15$\% better than the best theoretical linear option.
-Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
+Thus, the linear solution can theoretically exploit/store a maximum of $50\,\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
+
+Yet, BRs usually admit non-linear elastic behaviour.
+For example, a BR governed by a Duffing equation is inherently capable of exploiting $65$\,\% from the same energy source, which is $15$\,\% better than the best theoretical linear option.
+Section \ref{sec:SYSTEM MODELING} discusses the details of the modelling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
+
+% Figure \ref{fig:OB_vs_LINEAR} shows in blue the hydraulic behaviour of the ideal flow rate source previously introduced with the upper limit values of pressure and volume variations.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!htbp]
+% 	\centering
+% 	\captionsetup{justification=centering}
+% 	\includegraphics[trim={22.5cm 0cm 0cm 8.8cm},clip, width=0.35\textwidth]{figures/OB_vs_LINEAR.pdf}
+% 	\caption{Hydraulic source exploitation depending on the mechanical load}
+% 	\label{fig:OB_vs_LINEAR}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
-	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the ear canal geometry variation} 
+	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the earcanal geometry variation} 
 	\label{fig:system_presentation}
@@
 The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system.
-It uses a liquid filled earplug to transmit the energy outside the ear canal.
+It uses a liquid filled earplug to transmit the energy outside the earcanal.
 To maximize the efficiency, the system integrates a frequency-up conversion stage obtained by a BR.
@@
 \ref{fig:APG}).
+The electromechanical converter composed of the BR and the APG theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 
-During a mastication cycle, the TMJ compresses the ear canal wall and expels the fluid out of the earplug.
+During a mastication cycle, the TMJ compresses the earcanal wall and expels the fluid out of the earplug.
 The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth.
-The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig.
+The HA adapts both cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the earcanal (fig.
 \ref{fig:system_presentation}).
 
-The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$-x_0$}.
+The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$x_m = -x_0$}.
 The harvester operates on two major phases.
@@
 During the second phase the mass reaches and oscillates around the opposite stable equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the GPA.
-The mass will move backward when the next mastication will occur and complete the harvester cycle.
+The mass will move backward when the next mastication occurs and complete the harvester cycle.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\includegraphics[trim={20.5cm 0cm 0cm 11.5cm},clip, width=0.8\linewidth]{figures/HV_actuation_detail.pdf}
-	\caption{Contact detail between a HV and the BR mass} 
+	\caption{Details of the contact between a HV and the BR mass} 
 	\label{fig:HV_actuation_detail}
@@
 A technological solution for the HV is to use a flexible tube buckled by bending.
-The figure \ref{fig:HV_actuation_detail} schematizes the integration of such a HV around the BR environment.
+The figure \ref{fig:HV_actuation_detail} schematizes the integration of such HV around the BR environment.
 The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths.
@@
 Consequently, a pressure loss is generated through the valve in buckled position.
-The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
+The HV is considered closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
 This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
@@
 The HV technological choice is motivated by three major arguments.
-First, the absence of dedicated electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
+First, the absence of electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
 Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{SYSTEM GLOBAL MODELING}
+\section{SYSTEM GLOBAL MODELLING}
 \label{sec:SYSTEM MODELING}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-This section presents the global multiphysic model describing the system operation.
+The harvester is a multiphysics system composed of hydraulic, mechanical, and electrical components.
+This section presents the global multiphysics model describing the system theoretical operation.
 Two coupled subsystems are considered.
-The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
-Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier and the liquid filled earplug.
+The subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
+Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug.
 
 This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves.
-In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
+In fact, several miniature hydraulic solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
 Hence, this section neglects the pressure loss through the pressure separator and the energy loss inside the hydraulic amplifier.
-These hydraulic components will rather be considered for further work.
-
-    %///////////////////////////////////////////// 
-	\subsection{Modeling of the electromechanical converter}	
+These hydraulic components will rather be considered on further work.
+
+    %///////////////////////////////////////////// 
+	\subsection{Modelling of the electromechanical converter}	
 	\label{subsec:The electromechanical converter}
@@
 The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC.
-The rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
+The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
 The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
-The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by the equation \ref{eq:k2_def}.\\
+The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction, defined by the equation \ref{eq:k2_def}.\\
 The model is based on the following hypotheses:
@@
 	\item The only mass considered is the BR mass (2).
-	\item All parts are rigid except for the APG (4).
+	\item All parts are infinitely rigid except for the APG (4).
 	\item The hinges are considered elastic: They are defined by their rotational stiffness $K_{\varphi}$
@@
 
-By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium.
+By isolating the BR mass and using Newton's 2$^{nd}$ law, we can express its dynamic equilibrium.
 The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}.
 The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses.
-The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (fig.
+The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (see fig.
 \ref{fig:HV_actuation_detail}).
-$K_{HV}$ and $K_{\varphi}$ both act the same way by shifting the stable equilibrium positions of the BR toward $0$ as much as they increase.
+$K_{HV}$ and $K_{\varphi}$ both act the same way by moving the stable equilibrium positions of the BR toward $0$ as much as they increase.
 A dry friction model is chosen to describe the dissipation effect of the contact.
-The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
-The coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HC.
+The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing against each others, and by the sign of $\dot{x}_m$.
+The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket.
 The hydro-mechanical coupling will be detailed later.
@@
 	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U_p}
-	\label{eq:APG_elec}
-\end{equation}
-Consequently, the generated power $P_e$ is :
+\end{equation}
+Consequently, the generated power $P_e$ expression is :
 \begin{equation}
@@
 \end{equation} 
-Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup. Where the hinges angle $\varphi$ is defined as :
-\begin{equation}
-	\varphi = \arctan\biggl(\dfrac{x_m}{L}\biggr)
-	\label{eq:phi_definition}
-\end{equation}
-Additionally, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$, as showed in figure \ref{fig:HV_actuation_detail}. 
+Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup.
+Also, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$ and the latter will geometrically depend on the BR mass position $x_m$, as shown in figure \ref{fig:HV_actuation_detail}.
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}
- m \ddot{x}_m =-2K_{eq}(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi(x_m)) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
-				\ -2\alpha U_p \tan(\varphi(x_m))
+ m \ddot{x}_m =-2K(\sqrt{x_m^2+L^2}-l_0)\tan(\varphi) -\mu \dot{x}_m -\frac{4K_{\varphi}\varphi}{L}
+				\ -2\alpha U_p \tan(\varphi)
 				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - f_d \text{sign}(\dot{x}_m)
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{equation}
@@
 \end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     %///////////////////////////////////////////// 
-	\subsection{Modeling of the hydraulic circuit}	
+	\subsection{Modelling of the hydraulic circuit}	
 	\label{subsec:The hydraulic circuit}
@@
 
-In order to model the coupled behavior of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
+In order to model the coupled behaviour of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
 The following hypotheses will be considered :
@@
 \begin{align}
+	\text{Active cylinder ~}& \left\{~
+	F_{br} - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m = 0
+	\right.
+	\label{eq:equilibre_dynamique_piston_ouvert}\\
 	\text{Inactive cylinder ~}& \left\{~
@@
 \end{align}
+Where $p_c$ is the HC chamber pressure and $x_{hc,i}$ the piston position of the inactive HC piston.
+$F_{br}$ accounts for the OB counter-reaction on the HC.
+With the QS actuation assumption, it can be derived from equation \ref{eq:OB-GPA} and expressed as follows:
+\begin{align}
+	F_{br} = -\frac{K\ {x_0}^2}{L^2}\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr)x_m - \biggl( \frac{K_{HV}\theta}{a} \biggr)
+	\label{eq:F_OB_xxxxxx}
+\end{align}
 The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
 \ref{fig:HV_actuation_detail}).
-$Cf$ will be all the more important as $x_m$ increases.
-Its minimal value $Cf_0$ is obtained when the HV is unbent.
-We preliminarily assume that the relationship between $Cf$ and $x_m$ is linear and defined as follows :
+$Cf$ will become more important as $x_m$ increases.
+It is minimal when the HV is unbent and is worth $Cf_0$.
+The literature does not provide the constitutive relation between $x_m$ and $Cf$, thus we first assume that it is linear and defined as follows :
 \begin{align}
-Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ |x_m| 
+Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m 
 \label{eq:Cf(x_m)_linear}
@@
 
-Using the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
+By the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
 \begin{align}
@@
 \end{align}
-Where $a_h$ is the hydraulic amplification ratio and $q$ the fluid flow rate.
+Where $a_h$ is the hydraulic amplification ratio and $q$ the flow rate.
 
@@
 \begin{itemize}
-	\item The transducer is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
-	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which allow a 1kPa pressure operation \cite{SMC2022}.
-	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale.
+	\item The transducer is a APA50XS piezoelectric actuator (Cedrat Technologies, Meylan, France) exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
+	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which can operate at $1$\,kPa pressure \cite{SMC2022}.
+	\item The usual hearing aid size is $50$x$20$x$10$\,mm \cite{Quattro2019}. The \mbox{$L=16$\,mm} parameter is chosen to be consistent with this scale. $\epsilon$ can still be adjusted with $x_0$.
 \end{itemize}
 
-The system is designed by setting the two coupled requirements allowing the system operation.
+The maximum theoretical energy in a BR through a QS actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$ } to \mbox{$x_m=0$} (eq.
+\ref{eq:Ep_bar}).
+It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
+\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
+\begin{equation}
+	E_{pb} = \dfrac{K x_0^4}{3L^2} = n(p_c \cdot (\Delta V_{ear})_{max})
+	\label{eq:Ep_bar}
+\end{equation}
+The system is designed by setting the two coupled requirements to enable the system operation.
 First, the available swept volume must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
@@
 At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to guarantee the pressure limit.
-If not, $\epsilon$ (éq.
-\ref{eq:epsilon_def}) can be decreased, diminishing the extracted energy.
+If not, $\epsilon$ can be decreased, diminishing the extracted energy.
 \begin{empheq}[left=\empheqlbrace]{align} 
@@
 	\label{eq:contrainte_course}\\
-	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0\epsilon}{3\sqrt{3}}
+	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0^3}{3\sqrt{3}L^2}
 	\label{eq:contrainte_confort}
 \end{empheq}
-\begin{equation}
-	\epsilon = \dfrac{x_0}{L}
-	\label{eq:epsilon_def}
-\end{equation}
 Equations \ref{eq:contrainte_course} and \ref{eq:contrainte_confort} set the amplification level $a_h$ and the BR buckling level $\epsilon$.
@@
 	%///////////////////////////////////////////// 
-	\subsection{Targeted hydraulic behavior of the HVs}	
-	\label{subsec:HV hydraulic targeted behavior}
-	%/////////////////////////////////////////////
-A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. 
-The unknown remaining key parameter stays the hydraulic behavior $Cf(x_m)$ of the HVs. 
+	\subsection{Targeted hydraulic behaviour of the HVs}	
+	\label{subsec:HV hydraulic targeted behaviour}
+	%/////////////////////////////////////////////
+A multiphysics coupled model has been established with the equations and the preliminary dimensioning previously introduced.
+The unknown key aspect stays the hydraulic behaviour $Cf(x_m)$ of the HVs.
 The ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
@@
 \end{equation}
-The numerical resolution of the coupled differential equations \ref{eq:APG_elec},\ref{eq:OB-GPA}, \ref{eq:equilibre_dynamique_piston_ferme}, \ref{eq:Bernoulli_piston_ouvert}, \ref{eq:Bernoulli_piston_ferme}, \ref{eq:conservation_masse}, \ref{eq:conservation_masse_ouvert} and \ref{eq:conservation_masse_ferme} can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
+The numerical resolution of the differential equations can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
 	%///////////////////////////////////////////// 
@@
 By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
-\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled variables defining the harvester.
+\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.
+$r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the active HV.
+The mastication cycle is identically quadrupled in order to test the system cycling robustness.
 The earplug is assumed to be a perfect flow rate source.
-The mastication cycle is identically used 4 times in order to test the system cycling robustness.
 The fixed, designed and resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
 
-Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results of the mass and the HC pistons positions over overlaid with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
-The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), noting that the gravity influence is not considered.
+Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
+The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), knowing that the gravity influence is not considered.
 The same figure shows a focused view on the two main phases of the harvester operation during the actuation by the \emph{"bottom"} HC.
@@
 \begin{itemize}
-	\item The mass is at the \emph{"bottom"} equilibrium position $-x_0$.
+	\item The mass is at the $-x_0$ equilibrium position.
 	\item The \emph{"top"} HV is closed ($Cf_{top} = Cf_c$) and the \emph{"bottom"} side HV is opened ($Cf_{bot} = Cf_0$).
@@
 During a first phase the BR mass is pushed until it reaches $x=0$.
-The fluid exiting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
+The fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
 The mass then crosses $x_m=0$ and the second phase begins.
 The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$).
-The fluid is then directed toward the \emph{"top"} side and there is no contact between the mass and a HC.
-The mass oscillates around $x_m=x_0$ and energy is harvested by the APG.
+The fluid is then guided toward the \emph{"top"} side and there is no contact between the mass and a HC.
+The mass oscillates around $x_m=x_0$and the energy is harvested by the APG.
 The adequate hydraulic actuation making the fluid flow toward the right HC is achievable when \mbox{$(r_{Cf})_{min}=26$}.
 
-Additionally, figure \ref{fig:positions_Up_puissances_energies} presents the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=76$\%} with $22$µJ electrical energy harvested from one mastication.
+Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
+The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\,\%} with 20\,µJ harvested from one mastication.
 The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
-The energy source is limited by the comfort pressure level $p_c$ that is set to 1kPa, i.e.
-a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
-The harvester theoretical efficiency could lead to a maximum of $684$µJ extractable from the ear canal.
+The energy source depends on the comfort pressure level $p_c$ that is set to 1\,kPa, i.e.
+a fraction of the theoretical maximal value of $12$\,kPa \cite{Bouchard-Roy2020}.
+The harvester theoretical efficiency could lead to a maximum of 684\,µJ extractable from the earcanal.
 
@@
 
-The simulated model shows promising efficiency (tab.
-\ref{tab:parametres électromécaniques}) and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient (tab.
-\ref{tab:parametres_hydrauliques}) to ensure the adequate cycled actuation of the BR mass.
-Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
+The simulated model shows promising efficiency and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient $r_{Cf}$ to ensure the adequate cycled actuation of the BR mass.
+Next section will present the experimental approach to validate the theoretical behaviour of the electromechanical converter.
 
@@
     %/////////////////////////////////////////////
-The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure.
-This method optimizes the resonator quality factor by avoiding assemblies.
+The device heart is the electromechanical converter composed of the BR with the APG.
+They have been designed at the application scale in order to prove their feasibility.
+The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure with blades.
+This method optimizes the resonator quality factor by avoiding screw assemblies.
 Figure \ref{fig:BDT_OB+GPA} shows the BR mounted on the experimental test bench.
-The 8 hinges are realized by 4 buckled blades (BB) while a vertical guide beam (GB) ensures the APG mounting and avoids any of its rotations.
-The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
-They also maximize the BB compression stiffness that maximizes harvester efficiency, as detailed in the following section.
+The 8 hinges are assured by 4 buckled blades (BB) while a vertical guide blade (GB) ensures the APG mounting and avoids any of its rotations.
+The local thickening at the midspan of the blades are intended to facilitate the fabrication.
+They also maximize the BB compression stiffness that maximizes harvester efficiency, as we show in the following section.
 The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
@@
 			\toprule
-\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Valeur [Unit]} \\
+\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Value [Unit]} \\
 \midrule
 APX4 steel Young's modulus     & $E$                       & 211 [GPa]  \\
-APX4 steel elastic resistance  & $Re_{APX4}$               & 955[MPa]    \\
-Dimensions of a buckled beam  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
-Dimensions of the guide beam  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
+APX4 steel elastic resistance  & $Re_{APX4}$               & 955 [MPa]    \\
+Dimensions of a buckled blade  & $L$ x $l$ x $e$           & 16x0.07x1.2 [mm] \\
+Dimensions of the guide blade  & $L_{v}$ x $l_{v}$ x $e$   & 17.5x0.07x1.2 [mm] \\
 % Mounted GB dimensions          & $L_{v2}$ x $l_{v2}$ x $e$ & 48x0.1x1.2 [mm] \\
 Soft hinge stiffness		   & $K_{\varphi}$             & 0.006 [N.m/rad] \\
-Stiffness of the guide beam along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
+Stiffness of the guide blade along $\vec{y}$  & $K_{gb}$   & 190 [N/m] \\
 Stiffness of 4 buckled blades along $\vec{z}$ & $K_{bb}$   & 1402 [kN/m] \\  
@@
     %///////////////////////////////////////////// 
-	\subsection{BR beams design}	
+	\subsection{BR blades design}	
 	\label{subsec:BR blades design}
@@
 Where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by equation \ref{eq:alpha_eq}.
-It depends on the APG PFF the and ratio between the equivalent stiffness $K_{eq}$ (eq.
-\ref{eq:K_eq}) of the structure on the $\vec{x}$ axis and the equivalent stiffness of the APG mounted on the GB.
+It depends on the APG PFF and on the ratio between the equivalent stiffness $K_{eq}$ (eq.
+\ref{eq:K_eq}) of the structure on the $\vec{z}$ axis and the equivalent stiffness of the APG mounted on the GB.
 \begin{equation}
@@
 \end{equation}
-Equations \ref{eq:eta_ob} - \ref{eq:K_eq} demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
-If the condition is respected, then $K_{eq}$ can be assimilated to $K$ and $\alpha_{eq} \approx \alpha$.
+Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
+If the condition is respected, then $K_{eq}$ can be assimilated to $K$.
 
@@
 The problem was treated with a FEM model and the results are summarized through the figure \ref{fig:buckling_limit}.
-It reveals that the first secondary undesirable modes appear for $F_{z,0}=6.4$N.
-The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore can not be converted in electricity.
+It reveals that the first secondary undesirable modes appear for $F_{z,0}=6.4$\,N.
+The secondary buckling modes absorb mechanical energy that is not transmitted to the APG and therefore cannot be converted into electricity.
 Therefore, it is preferable to avoid them by establishing a buckling height domain for the fabricated BR, as presented on figure.
@@
 The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented on figure \ref{fig:BDT_OB+GPA}.
-An additional beam is mounted with the APG in order to prevent its rotation around any axis.
-A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$µm).
-The bearing decouples the rotation of the screw with the rotation of the beam structure in order to prevent unwanted torsional stress.
+An additional blade is mounted with the APG in order to prevent its rotation around any axis.
+A micrometric screw helps to set the initial structural buckling level $x_0$ ($\pm 10$\,µm).
+The bearing decouples the rotation of the screw with the rotation of the blade structure in order to prevent unwanted torsional stress.
 Two symmetrically mounted masses are added on the initial central mass with a 45\degree{} machined plane.
-The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$µm).
-The APG power is dissipated in the $R_l$ resistor and the $U_p$ tension ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
+The latter receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position of the mas along $\vec{x}$ axis ($\pm 10$\,µm).
+The APG power is dissipated in the $R_l$ resistor and the $U_p$ tension ($\pm 1$\,mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
 Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behavior.
+The HV mechanical influence is not considered in order to isolate the electromechanical converter dynamic behaviour.
 The mass is guided by a HC from a stable equilibrium position until it reaches \mbox{$x_m=0$}, and then oscillates around the opposite stable equilibrium position.
@@
 	$Q$                       & 50.0                  & 30.0 		  	\\  
-	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
-	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
-	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
-	${k^2_{sys}}$             & 16 \%                 & 1.25 \% 		\\
-	$\eta_{br}$               & 75 \%                 & 12.9 \%   		\\
+	$f_0$                     & 47.0\,Hz               & 27.9\,Hz  		\\
+	$x_0$                     & 0.49\,mm               & 0.50\,mm    		\\
+	$K_{eq}$                  & 2.56e5\,N/m            & 0.85e5\,N/m 		\\
+    $K_{bb}$                  & 14.02\,N/m             & 1.27e5\,N/m      \\  
+	${k^2_{sys}}$             & 16\,\%                 & 1.25\,\% 		\\
+	$\eta_{br}$               & 85\,\%                 & 12.9\,\%   		\\
 	\bottomrule
@@
     %/////////////////////////////////////////////
-The experimental dynamic behavior of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
+The experimental dynamic behaviour of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
 However, the performances of the experimental prototype are below the theoretical expectations (tab.
@@
 Two major factors could have led to such results.
-First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
+First, the quality factor decrease could be related to the general non-permanent assembly that uses non-perfect fastenings with fixation screws and a mobile micrometric screw.
 Then, small undulations have been observed on the BBs after fabrication and could also have gotten worse during the manipulation.
@@
 \ref{tab:parametres_hydrauliques}).
-A HV composed of a kapton tube \cite{Dupont2012} of initial diameter $D_t=1.05$mm and thickness $th_t=25$ µm was found to meet this hydraulic criteria.
+A HV composed of a kapton tube \cite{Dupont2012} of initial diameter $D_t=1.05$\,mm and thickness $th_t=25$\,µm was found to meet this hydraulic criteria.
 It will be called HV$_{T1}$ afterwards.
@@
 %%%%%%%%%%%%%%%%
-The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
-Its hydraulic behavior respects the minimum criteria of \mbox{$(r_{Cf})_{min}=26$} and therefore can ensure the adequate hydraulic commutation to cycle the BR mass motion.
-In order to set an optimal angle operation range $\Delta\theta$ we must investigate the evolution $K_{HV}(\theta)$.
+The hydraulic restriction coefficient of HV$_{T1}$ has been evaluated to 60 if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
+In order to set an optimal angle operation range we must investigate the evolution $K_{HV}(\theta)$.
 This matter will not be discussed in this paper.
-However, $\Delta\theta$ must be minimized in order to limit the energy needed for the HVs operation and also, $\theta_0$ must be minimized to reduce the hydraulic energy losses in the active branch.
-
-The following section presents the recalibrated harvester model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
+The following section presents the recalibrated harvester model using the experimental data of the HV$_{T1}$ and the experimental data of the electromechanical converter.
+
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{GLOBAL MODEL RECALIBRATION WITH \mbox{EXPERIMENTAL} DATA}
 \label{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA}
@@
 
-The experimentally identified parameters have been implemented in the global multiphysic coupled model to enhance its predictability and to evaluate the harvester performances.
-The last matter is achieved by evaluating the mechanical influence of the HV$_{T1}$ through an experimental approach in order to identify the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
-
-	%/////////////////////////////////////////////
-	\subsection{Experimental evaluation of the mechanical impact of HV$_{T1}$}
+The experimentally identified parameters have been implemented in the global multiphysics coupled model to enhance its predictability and to evaluate the harvester performances.
+The mechanical influence of the HV$_{T1}$ is identified with an experimental approach characterizing the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
+
+	%/////////////////////////////////////////////
+	\subsection{Recalibration with release trials}
 	%/////////////////////////////////////////////
 The HV$_{T1}$ has been mounted on the experimental test bench presented on figure \ref{fig:BDT_OB+GPA} and two experimental trials have been performed to identify the HV mechanical influence : free oscillations and oscillations with HV$_{T1}$ presence, during a harvesting phase.
+Thus, the dynamics difference between the two tests focus on the HV$_{T1}$ mechanical influence.
+
 The mass is initially set on $x_m=x_0$ and then pushed toward $x_0$.
-The HV$_{T1}$ internal pressure is adjusted to 30kPa with an oil column, in order to be consistent with the simulated case (tab.
+The HV$_{T1}$ internal pressure is adjusted to $30$\,kPa with an oil column, in order to be consistent with the simulated case (tab.
 \ref{tab:parametres_hydrauliques}).
 The oscillation phase begins when the mass crosses the $x_m=0$ position.
-In order to set $\theta_0$ we add an angle stopper that is shown in figure \ref{fig:contact_M_VH_lachers}.
+In order to set $\theta_0$ we add two angle stoppers illustrated on figure \ref{fig:contact_M_VH_lachers}.
 $\theta_c$ is then reached when the oscillations stop at $x_m=x_0$.
@@
 
-After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamics behavior of the harvester is theoretically predictable by the established model.
-The comparison between the results of the two tests reveal the mechanical impact of the HV. 
-The stiffness at $\theta_c$ is calculated with $x_0$ evolution between the two tests and equation \ref{eq:OB-GPA}. 
-The quality factor decrease is a result of the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
-The HV adds a supplementary dynamic mass in the BR.
-The electromechanical coupling coefficient is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.  
+After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamic behaviour of the harvester is theoretically predictable by the established model.
+The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and equation \ref{eq:OB-GPA}.
+The HV$_{T1}$ adds a supplementary dynamic mass in the BR and changes the oscillation frequency.
+The electromechanical coupling coefficient is not influenced by the HV presence.
+The quality factor decreases and the dry friction coefficient is calculated from the drop.
+Moreover, $a$ and $\Delta\theta$ are graphically evaluated.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{table}        
+	%/////////////////////////////////////////////
+	\subsection{Analyse and discussion}
+	%/////////////////////////////////////////////
+The experimental hydraulic behaviour of the HV$_{T1}$ is theoretically capable to provide \mbox{$r_{Cf}>26$} and ensure the hydraulic adequate commutation cycling the BR mass motion.
+
+The quality factor decrease results from the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
+The friction losses can be minimized by an order of magnitude by using materials with low friction coefficient like teflon \cite{Nosonovsky2013}.
+The HV-mass contact can also profit from magnetic interactions instead of direct rubbing.
+
+The global electromechanical coupling is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.
+The major part of the energy loss is due to the $k^2_{sys}$ drop as a result of the softening of the BBs from the prototype fabrication and manipulation.
+It can be minimized by using thicker BBs while taking care that the buckling domain does not reach the critical point where the APG could be damaged (fig.
+\ref{fig:buckling_limit}).
+With $200$\,µm thick BBs instead of $75$\,µm, we can expect 26\,\% improvement on $\eta_{br}$ (eqs.
+\ref{eq:eta_ob}-\ref{eq:K_eq}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+This work emphasizes the energy need for hearing aids and the exploitation of the mechanical deformation of the earcanal as a solution to enhance the autonomy of those devices batteries.
+
+A new energy harvester architecture maximizing the energy conversion efficiency is proposed.
+A hydraulic, mechanical and electrical coupled model is established.
+Its numerical evaluation predicts that the system can theoretically harvest 85\% of the available energy with a hydraulic extraction method.
+The dynamic behaviour and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
+A new concept of HVs is proposed, based on the bending buckling of flexible tubes.
+A HV design is proposed with experimental investigation based on the theoretical needed behaviour extracted from the numerical simulations.
+
+The experimental data are used to recalibrate the harvester multiphysics model and to evaluate its performances.
+The global predicted efficiency is $\eta_g=2.6\,\%$.
+The energy losses factors are identified and solutions are proposed in order to increase the efficiency up to 26\%.
 

### 2022-11-01 article_system.tex
Recorrection Fabien sur Overleaf...

--- 2022-10-31 article_system.tex
@@
 
-\title{Toward a novel piezoelectric energy harvester for ear canal dynamic motion exploitation, using a bistable resonator cycled by coupled hydraulic valves made of collapsed flexible tubes}
+\title{Toward a novel piezoelectric energy harvester for earcanal dynamic motion exploitation, using a bistable resonator cycled by coupled hydraulic valves made of collapsed flexible tubes}
 
@@
 \begin{abstract}
-Scavenging energy from the ear canal dynamic motion during jaw motion may be a practical way to enhance the battery autonomy of hearing aids.
-One of the main challenges is to optimize the extracted energy while coping with the constraints associated to soft human tissues and restricted ear canal volume.
-We propose a new concept of harvester made of a liquid filled earplug transferring the energy outside the ear canal to a generator.
-It is composed oa hydraulic amplifier, two hydraulic cylinders actuating a bistable resonator raising the source frequency driving an amplified piezoelectric transducer to generate electricity.
+Scavenging energy from the earcanal's dynamic motion during jaw movements may be a practical way to enhance the battery autonomy of hearing aids.
+The main challenge consists in optimizing the amount of energy extracted while working with soft human tissues and the shape of the earcanal.
+This paper proposes a new harvester concept: a liquid-filled earplug which transfers energy outside the earcanal to a generator.
+It is composed of a hydraulic amplifier, two hydraulic cylinders that actuate a bistable resonator to raise the source frequency driving an amplified piezoelectric transducer to generate electricity.
 The cycling of the resonator is achieved using two innovative flexible hydraulic valves based on the buckling of flexible tubes.\\
-A multiphysic coupled model is established in order to determine the system operation requirements and to evaluate its theoretical performance.
-It exhibits a theoretical energy conversion efficiency of 85\%.
-The electromechanical performance of the resonator couple to the piezoelectric transducer as well as the hydraulic behavior of the valves are experimentally investigated.
-The global model is updated with the experimental data to ameliorate its predictability for a further optimized design.
-The energy losses are identified, which allow an entire design proposed to improve the experimental energy conversion efficiency to 26\%.
-
+A multiphysics-coupled model is established to determine the system operation requirements and to evaluate its theoretical performance.
+This model exhibits a theoretical energy conversion efficiency of 85\%.
+The electromechanical performance of the resonator coupled to the piezoelectric transducer as well as the hydraulic behavior of the valves are experimentally investigated.
+The global model is updated with the experimental data to ameliorate its predictability to further optimize the design.
+The energy losses are identified, which will enable the enhance the entire design proposed and improve the experimental energy conversion efficiency to 26\%.
 \end{abstract}
@@
 \begin{keyword}
-Energy harvesting, frequency-up, ear canal, multiphysic, hydraulic valve
+Energy harvesting, frequency-up, earcanal, multiphysics, hydraulic valve
 \end{keyword}
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress on the energy consumption of mobile devices on the human body environment.
-Energy harvesting methods have been studied in order to complement their power supply and enhance the autonomy of the batteries.
+The growing use of wireless devices and the miniaturization of electronic circuits have led to significant progress in the energy consumption of wearable mobile devices.
+Energy harvesting methods have been studied to complement and enhance the power supply and autonomy of batteries.
 In-ear devices such as hearing aids and cochlear implants are powered by disposable cells or rechargeable batteries.
-The energy consumption of the best integrated devices in the literature rises up to $17$J for a 10 hours daily use \cite{Scherer2019,Yip2015,Kulah2022}.
+The energy consumption of the best integrated devices in the literature reaches up to $17$J for a 10 hour period of daily use \cite{Scherer2019,Yip2015,Kulah2022}.
 Woodruff \emph{et al.} underlined that patients using hearing aids sometimes struggle to change and select batteries for their devices \cite{Woodruff2021}.
-Another statistical study revealed that the majority of hearing aids and cochlear implants users prefer disposable batteries for the long autonomy, but would have liked rechargeable solutions if the battery cycle was sufficient to complete the day \cite{PracticesAudiology2016}.
-Also, the long term use makes the rechargeable solutions a more economical and more ecological choice compared to the disposable cells.
-These arguments motivated the development of energy harvesting systems.
-
-The common energy sources are solar or wind energy but their availability in the low size environment of the application context makes them not suitable for exploitation.
-The activities of the human body generate a considerable amount of energy of different natures.
-Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, the kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, the body heat thermal energy \cite{Kim2014}, the strain energy from the skin deformation \cite{Jin2021} could be harvested for in-ear applications.
-An interesting energy source for cochlear implants or hearing aids appears to be the ear canal mechanical deformation as it is directly located in the area of the application.
-Delnavaz \emph{et al.} first showed in 2012 that the jaw movements changes de ear canal geometry during mastication.
-Carioli \emph{et al.} then used a customized earplug molding technic with a 3D scanner to reveal a global bending movement and a local compression area in the ear canal during mastication \cite{Carioli2016}.
-These two mechanical deformations represent a potential energy source that can be exploited.
+Another statistical study revealed that the majority of hearing aid and cochlear implant users prefer disposable batteries for their length of autonomy, but would prefer rechargeable solutions if these were able to last the entire day \cite{PracticesAudiology2016}.
+Indeed, the long-term of rechargeable solutions makes them more economical and ecological compared to disposable cells.
+Such considerations have spurred the development of energy-harvesting systems.
+
+The common sources of renewable energy are solar or wind but their use is unfeasible for the scale of this application.
+Another avenue comes from the fact that the human body generates a considerable amount of energy from various types of movements or conditions.
+Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, thermal energy from body heat \cite{Kim2014}, and strain energy from skin deformation \cite{Jin2021} could be harvested for in-ear applications.
+An interesting energy source for cochlear implants or hearing aids appears to be the earcanal's mechanical deformation.
+Delnavaz \emph{et al.} first showed in 2012 that the jaw movements change the earcanal's geometry during mastication.
+Carioli \emph{et al.} then used a customized earplug molding technique with a 3D scanner to characterize the global bending movement and local compression area in the earcanal during mastication \cite{Carioli2016}.
+These two mechanical deformations could potentially be exploited as an energy source.
 
 Delnavaz \emph{et al.} developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013}.
-The earplug has been molded on the subject in order to maximize the contact surface with the ear canal.
-The harvester is capable of exploiting both the flexion and the compression energy sources.
-The experimental prototype was able to extract $44$µJ from a mastication cycle.
-The soft materials facilitate the bio-integration of the harvester but the PVDF low electromechanical coupling coefficient could have led to poor energy conversion efficiency.
+The earplug was molded to the subject's earcanal to maximize surface contact.
+The aim of the harvester was to exploit both the flexion and compression energies.
+The experimental prototype was able to extract $44$\,µJ from a mastication cycle.
+The soft materials facilitated the bio-integration of the harvester, but the PVDF's low electromechanicalcoupling coefficient may have been the cause of poor energy conversion efficiency.
 A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
-The energy is extracted by a liquid filled earplug whose internal volume vary as a result of the radial compression of the ear canal internal walls during the jaw movements.
-This variation put into motion a moving magnet translating in a water column surrounded by a coil.
-The generated energy experimentally amounts to 0.2µJ per mastication cycle.
+The energy was extracted using a liquid-filled earplug whose internal volume varied as a result of the radial compression of the earcanal during jaw movements.
+The earplug was equipped with a magnet in a water column surrounded by a coil.
+When the volume varied, the magnet would shift, generating energy.
+The generated energy experimentally amounted to 0.2µJ per mastication cycle.
 The prototype appeared to be less efficient than the PVDF earplug.
-This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57Hz) and a small scale application \cite{Kulah2008,Priya2017}.
-However, the hydraulic transmission allows the use of more complex and voluminous technological solutions since the energy becomes available outside the small ear canal volume.
-
-Based on the analysis of the literature, we propose a new solution optimizing the energy conversion efficiency to maximize the harvested energy from the ear canal dynamic motion.
-The next section states on the hydraulic energy source characterization and on the harvesting strategy that we adopted.
+This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57\,Hz) and a small-scale application \cite{Kulah2008,Priya2017}.
+However, in this proposed model, the hydraulic transmission will enable the use of more complex and voluminous technological solutions since the energy will be made available outside, in other words, it will not be constricted by the earcanal's volume.
+
+Based on the analysis of the literature, we propose a new solution to optimize the energy conversion efficiency and maximize the harvested energy from the earcanal's dynamic motion.
+The next section states the hydraulic energy source characterization and harvesting strategy that was adopted.
 Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle.
-Section \ref{sec:SYSTEM MODELING} details the global system modeling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester.
-Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} then exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling.
-Then, section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work major contributions and the harvester potential.
-Finally, a conclusion is stated.
+Section \ref{sec:SYSTEM MODELING} details the global system modelling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester.
+Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling.
+Section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work's major contributions and the potential of the harvester.
+This is followed by the conclusion.
 
@@
     %/////////////////////////////////////////////
-Human tissue requires soft flexible materials in order to extract the ear canal deflection energy without causing discomfort.
-However, flexible transducers admit low energy conversion efficiency as a part of the extracted energy is dissipated in the elastic non-active material.
+Extracting energy from the mechanical deformations of human tissue requires soft flexible materials so that the earcanal deflection energy can be harvested without causing discomfort.
+However, flexible transducers have a low energy-conversion efficiency because part of the extracted energy is dissipated in the elastic non-active material.
 Additionally, the low frequency of mastication makes it difficult to use resonant structures that generally admit better conversion efficiencies than low frequency solutions \cite{Ashraf2011}.
-Thus, the traditional transducing methods are not suitable enough for the application.
-
-To date, the best solution proposed in the literature consists on using soft materials as the piezoelectric PVDF earplug previously introduced \cite{Delnavaz2013}.
-The low mechanical impedance of the soft tissue in fact limits the use of more effective rigid piezoelectric materials.
-
-The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but allows to transmit the energy outside the ear canal and benefit so from larger effective space.
-The latter is in fact essential as it becomes then possible to implement an impedance adaption stage and more effective transducing methods that could not fit directly inside the ear canal restricted volume.
-In fact, Marin \emph{et al.} demonstrated that the power generated by piezoelectric or electromagnetic transducers is as much better as the effective volume of transducing material is high \cite{Marin2011}.
-The present work is then based on the exploitation of the ear canal by a liquid filled earplug.
-As energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
-In order to optimize the energy extraction, the earplug must fit the ear canal wall.
+Thus, the traditional transducing methods are unsuitable for this application.
+
+To date, the best solution proposed in the literature consists of using soft materials, such as the piezoelectric PVDF earplug previously introduced \cite{Delnavaz2013}.
+In fact, the low mechanical impedance of the soft tissue limits the use of more effective rigid piezoelectric materials.
+
+The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but energy can be transmitted outside the earcanal which could benefit from larger effective space.
+The latter is essential to be able to implement an impedance adaptation stage and more effective transducing methods that could not otherwise fit directly inside the earcanal's limited volume.
+In fact, Marin \emph{et al.} demonstrated that the power generated by piezoelectric or electromagnetic transducers is proportionally greater as the effective volume of the transducing material is greater \cite{Marin2011}.
+Thus, the present work is based on the exploitation of the earcanal deformation using a liquid-filled earplug.
+As an energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
+In order to optimize the energy extraction, the earplug must fit the earcanal wall snugly.
 Turcot \emph{et al.} demonstrated that the initial pressurization must reach a minimum of $14$kPa to achieve a good fit \cite{TURCOT2011}.
@@
 Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources.
-The power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy source decrease \cite{Priya2017,Kulah2008}.
+In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy sources decreases \cite{Priya2017,Kulah2008}.
 Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.
@@
 Equation \ref{eq:hydraulic-mechanic_interface} models the hydraulic-mechanic interface with $x_{m}$ and $ S_{hc}$ being respectively the dynamic mass position on the $\vec{x}$ axis and the HC internal section.
-\begin{equation}
-	\Delta p_{ear}S_{hc} = K_s x_m
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+	\Delta p_{ear}\ S_{hc} = K_{s}\ x_{m}
 	\label{eq:hydraulic-mechanic_interface}
 \end{equation}
-Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as :
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
 \begin{equation}
@@
 \end{equation}
-Thus, the linear solution can theoretically exploit/store a maximum of $50\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
+Thus, the linear solution can theoretically exploit/store a maximum of $50\,\%$ from the maximum available hydraulic energy ($\text{max}(E_{hyd})$).
 
@@
 \end{equation}
-We see later that it is inherently capable of exploiting $65$\% from the hydraulic energy source, which is $15$\% better than the best theoretical linear option.
+We see later that it is inherently capable of exploiting $65$\,\% from the hydraulic energy source, which is $15$\,\% better than the best theoretical linear option.
 Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
@@
 
-During a mastication cycle, the TMJ compresses the ear canal wall and expels the fluid out of the earplug.
+During a mastication cycle, the TMJ compresses the earcanal wall and expels the fluid out of the earplug.
 The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth.
-The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the ear canal (fig.
+The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the earcanal (fig.
 \ref{fig:system_presentation}).
@@
 Finally, it seems well adapted for integration purpose for millimetric application scale.
-
-%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{SYSTEM GLOBAL MODELING}
+%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
+\section{SYSTEM GLOBAL MODELLING}
 \label{sec:SYSTEM MODELING}
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-This section presents the global multiphysic model describing the system operation.
+The harvester is a multiphysics system composed of hydraulic, mechanical, and electrical components.
+This section presents the global multiphysics model describing the system theoretical operation.
 Two coupled subsystems are considered.
-The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
+The subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
 Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the HA and the liquid filled earplug.
@@
 This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves.
-In fact several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
+In fact, several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
 Hence, this section neglects the energy loss inside the HA and the HCs.
-These hydraulic components will rather be considered in further work.
-
-    %///////////////////////////////////////////// 
-	\subsection{Modeling of the electromechanical converter}	
+These hydraulic components will rather be considered on further work.
+    %///////////////////////////////////////////// 
+	\subsection{Modelling of the electromechanical converter}	
 	\label{subsec:The electromechanical converter}
@@
 The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC.
-The rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
+The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
 The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
+the hinges angle $\varphi$ is defined as follows :
+\begin{equation}
+	\varphi = \arctan\biggl(\dfrac{x_m}{L}\biggr)
+	\label{eq:phi_definition}
+\end{equation}
 The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by the equation \ref{eq:k2_def}.\\
@@
 
-By isolating the BR mass and using the Newtons 2$^{nd}$ law, we can express its dynamic equilibrium.
+By isolating the BR mass and using Newton's 2$^{nd}$ law, we can express its dynamic equilibrium.
 The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}.
 The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses.
-The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (fig.
+The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (see fig.
 \ref{fig:HV_actuation_detail}).
@@
 A dry friction model is chosen to describe the dissipation effect of the contact.
-The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing, and the sign of $\dot{x}_m$.
-The coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HC.
+The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing against each others, and by the sign of $\dot{x}_m$.
+The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HCs.
 The hydro-mechanical coupling will be detailed later.
@@
 \end{equation}
-Consequently, the generated power $P_e$ is :
+Consequently, the generated power $P_e$ expression is :
 \begin{equation}
@@
 \end{equation} 
-Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup. Where the hinges angle $\varphi$ is defined as :
-\begin{equation}
-	\varphi = \arctan\biggl(\dfrac{x_m}{L}\biggr)
-	\label{eq:phi_definition}
-\end{equation}
+Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup.
 Additionally, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$, as showed in figure \ref{fig:HV_actuation_detail}.
@@
 \end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure*}
-% \begin{equation}
-% % \begin{small}
-% 	\begin{dcases}
-% \ddot{x}_m = - \frac{2K{x_0}^2}{mL^2}\Biggl[\biggl(\frac{x_m^2}{{x_0}^2} -1\biggr )+ \dfrac{8K_{\varphi}}{L^2}\Biggr]x_m 
-% 			 - \frac{K_{HV}(x_m)\theta(x_m)}{ma}
-% 			 - \frac{\mu+\mu_{hc}}{m}\dot{x}_m  - f_d \text{sign}(\dot{x}_m)
-% 			 - \frac{2\alpha U_p\ x_m}{mL}
-% 			 - p_{hc,a}\ S_{hc} \\
-% x_m = \dfrac{D_r(1-\cos(\theta))+2a\sin(\theta)}{2\cos(\theta)}\text{,}
-% 				~~ \theta\leq\arctan\biggl(\dfrac{2a}{D_r}\biggr)\\
-% \dfrac{U_p}{R_l} = \frac{2\alpha x_m \dot{x}_m}{L} - C_p\dot{U}_p 
-% 	\end{dcases}
-% 	\label{eq:OB+GPA+VH+piston}	
-% % \end{small}
-% \end{equation}
-% \end{figure*}
-% % \FloatBarrier
-% %%%%%%%%%%%%%%%%%%%%%%%
-    %///////////////////////////////////////////// 
-	\subsection{Modeling of the hydraulic circuit}	
+    %///////////////////////////////////////////// 
+	\subsection{Modelling of the hydraulic circuit}	
 	\label{subsec:The hydraulic circuit}
     %/////////////////////////////////////////////
-
-In order to model the coupled behavior of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
+In order to model the coupled behaviour of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
 The following hypotheses will be considered :
@@
 Its minimal value $Cf_0$ is obtained when the HV is unbent.
-We preliminarily assume that the relationship between $Cf$ and $x_m$ is linear and defined as follows :
+We assume at first that the relationship between $Cf$ and $x_m$ is linear and defined as follows :
 \begin{align}
 Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ |x_m| 
+\label{eq:Cf(x_m)_linear}
+\end{align}
+The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
+\ref{fig:HV_actuation_detail}).
+$Cf$ will become more important as $x_m$ increases.
+It is minimal when the HV is unbent and is worth $Cf_0$.
+The literature does not provide the constitutive relation between $x_m$ and $Cf$, thus we first assume that it is linear and defined as follows :
+\begin{align}
+Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m 
 \label{eq:Cf(x_m)_linear}
@@
 \begin{itemize}
-	\item The transducer is a APA50XS piezoelectric actuator, from Cedrat Technologies, exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
-	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which allow a 1kPa pressure operation \cite{SMC2022}.
-	\item The usual hearing aid size is $50$x$20$x$10$mm \cite{Quattro2019}. The \mbox{$L=16mm$} parameter is chosen to be consistent with this scale.
+	\item The transducer is a APA50XS piezoelectric actuator (Cedrat Technologies, Meylan, France) exploited as a generator \cite{CEDRATTECHNOLOGIES2022}.
+	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which can operate at $1$\,kPa pressure \cite{SMC2022}.
+	\item The usual hearing aid size is $50$x$20$x$10$\,mm \cite{Quattro2019}. The \mbox{$L=16$\,mm} parameter is chosen to be consistent with this scale.
 \end{itemize}
-
-The system is designed by setting the two coupled requirements allowing the system operation.
+The system is designed by setting the two coupled requirements to enable the system operation.
 First, the available swept volume must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
@@
 	%///////////////////////////////////////////// 
-	\subsection{Targeted hydraulic behavior of the HVs}	
-	\label{subsec:HV hydraulic targeted behavior}
-	%/////////////////////////////////////////////
-A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. 
-The unknown remaining key parameter stays the hydraulic behavior $Cf(x_m)$ of the HVs. 
+	\subsection{Targeted hydraulic behaviour of the HVs}	
+	\label{subsec:HV hydraulic targeted behaviour}
+	%/////////////////////////////////////////////
+A multiphysics coupled model has been established with the equations and the preliminary dimensioning previously introduced.
+The unknown remaining key parameter stays the hydraulic behaviour $Cf(x_m)$ of the HVs.
 The ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
@@
 During a first phase the BR mass is pushed until it reaches $x=0$.
-The fluid exiting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
+The fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
 The mass then crosses $x_m=0$ and the second phase begins.
@@
 
-Additionally, figure \ref{fig:positions_Up_puissances_energies} presents the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\%} with $22$µJ electrical energy harvested from one mastication.
+Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
+The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\,\%} with 22\,µJ electrical energy harvested from one mastication.
 The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
-The energy source is limited by the comfort pressure level $p_c$ that is set to 1kPa, i.e.
-a fraction of the theoretical maximal value of $12$kPa \cite{Bouchard-Roy2020}.
-The harvester theoretical efficiency could lead to a maximum of $684$µJ extractable from the ear canal.
+The energy source depends on the comfort pressure level $p_c$ that is set to 1\,kPa, i.e.
+a fraction of the theoretical maximal value of $12$\,kPa \cite{Bouchard-Roy2020}.
+The harvester theoretical efficiency could lead to a maximum of 684\,µJ extractable from the earcanal.
 
@@
     %///////////////////////////////////////////// 
-	\subsection{Electromechanical converter presentation}	
+	\subsection{The electromechanical converter presentation}	
 	\label{The electromechanical converter presentation}
@@
 The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
-They also maximize the BB compression stiffness that maximizes harvester efficiency, as detailed in the following section.
+They also maximize the BB compression stiffness that maximizes harvester efficiency, as we show in the following section.
 The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
@@
 	\subsection{BR beams design}	
-	\label{subsec:BR blades design}
+	\label{subsec:BR beams design}
     %/////////////////////////////////////////////
@@
 $k^2_{sys}$ is the global electromechanical coupling coefficient of the harvesting system.
-The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the blades (tab.
+The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the beams (tab.
 \ref{tab:parametres_lames}) as follows :
-% \begin{equation}
-% 	k^2_{sys} = \dfrac{ K_{bb}^2 \alpha^2 }
-% 					  { \biggr(Cp(K+K_{bb} + 
-% 						\dfrac{K_{bb}^2 \alpha^2}{K_{bb} + K_{gb} + K} \biggl)
-% 						 (K_{bb} + K_{gb} + K)^2}
-% 	\label{eq:k2_sys}
-% \end{equation}
 \begin{equation}
@@
 Where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by equation \ref{eq:alpha_eq}.
-It depends on the APG PFF the and ratio between the equivalent stiffness $K_{eq}$ (eq.
+It depends on the APG PFF and on the ratio between the equivalent stiffness $K_{eq}$ (eq.
 \ref{eq:K_eq}) of the structure on the $\vec{z}$ axis and the equivalent stiffness of the APG mounted on the GB.
@@
 \end{equation}
-Equations \ref{eq:eta_ob} - \ref{eq:K_eq} demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
+Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
 If the condition is respected, then $K_{eq}$ can be assimilated to $K$ and $\alpha_{eq} \approx \alpha$.
@@
 The beams design was obtained using a FEM model which result is summarized in the figure \ref{fig:buckling_limit}.
-It reveals that the first secondary undesirable buckling mode appears for $F_{z,0}=6.4$N.
+It reveals that the first secondary undesirable buckling mode appears for $F_{z,0}=6.4$\,N.
 If it happens, the compression force is not transmitted from the mass to the APG.
@@
 The preliminary simulated case presented in the previous section is in the preferable domain.
-Moreover, the force absorbed by the APG is assured to be under the maximal limit of 18N from which the device could be damaged.
+Moreover, the force absorbed by the APG is assured to be under the maximal limit of $18$\,N from which the device could be damaged.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An additional beam is mounted with the APG in order to prevent its rotation around any axis.
-A micrometric screw sets the initial buckling level $x_0$ ($\pm 10$µm).
+A micrometric screw sets the initial buckling level $x_0$ ($\pm 10$\,µm).
 The bearing decouples the rotation of the screw with the beam structure in order to prevent unwanted torsional stress.
 The central mass $\degree{45}$ place receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position.
-The APG power is dissipated in the $R_l$ resistor and the $U_p$ voltage ($\pm 1$mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
+The APG power is dissipated in the $R_l$ resistor and the $U_p$ voltage ($\pm 1$\,mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
 Finally, the two HC plungers actuate the mass from one stable equilibrium position to the other.
@@
 \ref{tab:parametres_hydrauliques}).
-A buckled kapton tube \cite{Dupont2012} of internal diameter $D_t=1.05$mm and thickness $th_t=25$ µm was found to meet this hydraulic criteria.
+A buckled kapton tube \cite{Dupont2012} of internal diameter $D_t=1.05$\,mm and thickness $th_t=25$\,µm was found to meet this hydraulic criteria.
 It will be called HV$_{T1}$ afterwards.
@@
 An electromechanical rotary plate is monitored on LabVIEW interface and imposes a bending angle $\theta$.
-A liquid filled syringe fixes the fluid flow through the HV$_{T1}$ and $q_{ser}$ is evaluated by tracking the syringe piston displacement.
+A liquid filled syringe fixes the fluid flow through the HV$_{T1}$ and $q_{syr}$ is evaluated by tracking the syringe piston displacement.
 The pressure loss coefficient $Cf_{T1}$ is calculated as \mbox{follows :}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htb]
-\centering
-	\captionsetup{justification=centering}
-	\includegraphics[trim={15.5cm 0cm 0cm 3.6cm},clip,width=0.7\linewidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
+\begin{figure}[!htbp]
+\centering
+	\captionsetup{justification=centering}
+	\includegraphics[trim={15.5cm 0cm 0cm 3.6cm},clip,width=0.6\linewidth]{figures/resultats_essais_hydraulique_VH_D1mm.pdf}
 	\caption{Hydraulic characterization of the HV$_{T1}$.}
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-
-The experimentally identified parameters have been implemented in the global multiphysic coupled model to enhance its predictability and to evaluate the harvester performances.
+The experimentally identified parameters have been implemented in the global multiphysics coupled model to enhance its predictability and to evaluate the harvester performances.
 The mechanical influence of the HV$_{T1}$ is identified with an experimental approach characterizing the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
-
 	%/////////////////////////////////////////////
@@
 The mass is initially set on $x_m=x_0$ and then pushed toward $x_0$.
-The HV$_{T1}$ internal pressure is adjusted to 30kPa with an oil column, in order to be consistent with the simulated case (tab.
+The HV$_{T1}$ internal pressure is adjusted to $30$\,kPa with an oil column, in order to be consistent with the simulated case (tab.
 \ref{tab:parametres_hydrauliques}).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\begin{figure}[!htb]
+\begin{figure}[!htbp]
 	\begin{center}
@@
 
-After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamics behavior of the harvester is theoretically predictable by the established model.
+After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamic behaviour of the harvester is theoretically predictable by the established model.
 The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and equation \ref{eq:OB-GPA}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!htb]	
+\begin{figure}[!htbp]	
 \captionsetup{justification=centering}
@@
 	%/////////////////////////////////////////////
-The experimental hydraulic behavior of the HV$_{T1}$ is theoretically capable to provide \mbox{$r_{Cf}>26$} and ensure the hydraulic adequate commutation cycling the BR mass motion.
+The experimental hydraulic behaviour of the HV$_{T1}$ is theoretically capable to provide \mbox{$r_{Cf}>26$} and ensure the hydraulic adequate commutation cycling the BR mass motion.
 
@@
 \ref{fig:buckling_limit}).
-With $200$µm thick BBs instead of $75$µm, we can expect 26\% improvement on $\eta_{br}$ (eqs.
+With $200$\,µm thick BBs instead of $75$\,µm, we can expect 26\,\% improvement on $\eta_{br}$ (eqs.
 \ref{eq:eta_ob}-\ref{eq:K_eq}).
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-This work emphasizes the energy need for hearing aids and the exploitation of the mechanical deformation of the ear canal as a solution to enhance the autonomy of those devices batteries.
+This work emphasizes the energy need for hearing aids and the exploitation of the mechanical deformation of the earcanal as a solution to enhance the autonomy of those devices batteries.
 
@@
 Its numerical evaluation predicts that the system can theoretically harvest 85\% of the available energy with a hydraulic extraction method.
-The dynamic behavior and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
+The dynamic behaviour and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
 A new concept of HVs is proposed, based on the bending buckling of flexible tubes.
-A HV design is proposed with experimental investigation based on the theoretical needed behavior extracted from the numerical simulations.
-
-The experimental data are used to recalibrate the harvester multiphysic model and to evaluate its performances.
-The global experimental efficiency is evaluated to $2.6$\%.
+A HV design is proposed with experimental investigation based on the theoretical needed behaviour extracted from the numerical simulations.
+
+The experimental data are used to recalibrate the harvester multiphysics model and to evaluate its performances.
+The global predicted efficiency is $\eta_g=2.6\,\%$.
 The energy losses factors are identified and solutions are proposed in order to increase the efficiency up to 26\%.
+
+\section{Acknowledgments}
+The authors would like to thank Jacob Bouchard-Roy for the data on jaw-joint hydraulic source as well as Michel Demuynck for the constructive exchanges on earcanal deformation.
+This work was made possible via funding from the NSERC Discovery program (RGPIN-2017-06192) held by last author, the technical support from the ÉTS-EERS Industrial Research Chair in In-Ear Technologies (CRITIAS), as well as the laboratory infrastructures of the SYMME.
+The first author acknowledges the financial support received from the USMB through its doctoral scholarship program.
 

### 2022-11-03 article_system.tex
Après correction anglais ETS

@@
 \usepackage{graphicx}
+\usepackage{siunitx}
 
@@
 Scavenging energy from the earcanal's dynamic motion during jaw movements may be a practical way to enhance the battery autonomy of hearing aids.
-The main challenge consists in optimizing the amount of energy extracted while working with soft human tissues and the shape of the earcanal.
+The main challenge consists in optimizing the amount of energy extracted while working with soft human tissues and the earcanal restricted volume.
 This paper proposes a new harvester concept: a liquid-filled earplug which transfers energy outside the earcanal to a generator.
-It is composed of a hydraulic amplifier, two hydraulic cylinders that actuate a bistable resonator to raise the source frequency driving an amplified piezoelectric transducer to generate electricity.
+The latter is composed of a hydraulic amplifier, two hydraulic cylinders that actuate a bistable resonator to raise the source frequency while driving an amplified piezoelectric transducer to generate electricity.
 The cycling of the resonator is achieved using two innovative flexible hydraulic valves based on the buckling of flexible tubes.\\
-A multiphysics-coupled model is established to determine the system operation requirements and to evaluate its theoretical performance.
+A multiphysics-coupled model is established to determine the system operation requirements and to evaluate its theoretical performances.
 This model exhibits a theoretical energy conversion efficiency of 85\%.
-The electromechanical performance of the resonator coupled to the piezoelectric transducer as well as the hydraulic behavior of the valves are experimentally investigated.
-The global model is updated with the experimental data to ameliorate its predictability to further optimize the design.
-The energy losses are identified, which will enable the enhance the entire design proposed and improve the experimental energy conversion efficiency to 26\%.
+The electromechanical performance of the resonator coupled to the piezoelectric transducer, as well as the hydraulic behavior of the valves are experimentally investigated.
+The global model was updated using the experimental data to improve its predictability toward further optimization of the design.
+Moreover, the energy losses are identified to enhance the entire proposed design and improve the experimental energy conversion efficiency to 26\%.
 \end{abstract}
@@
 In-ear devices such as hearing aids and cochlear implants are powered by disposable cells or rechargeable batteries.
-The energy consumption of the best integrated devices in the literature reaches up to $17$J for a 10 hour period of daily use \cite{Scherer2019,Yip2015,Kulah2022}.
-Woodruff \emph{et al.} underlined that patients using hearing aids sometimes struggle to change and select batteries for their devices \cite{Woodruff2021}.
+The energy consumption of the best integrated devices in the literature reaches up to $17$\,J for a 10-hour period of daily use \cite{Scherer2019,Yip2015,Kulah2022}.
+Woodruff \emph{et al.} underlined that patients using hearing aids sometimes struggle to change and select disposable batteries for their devices \cite{Woodruff2021}.
 Another statistical study revealed that the majority of hearing aid and cochlear implant users prefer disposable batteries for their length of autonomy, but would prefer rechargeable solutions if these were able to last the entire day \cite{PracticesAudiology2016}.
-Indeed, the long-term of rechargeable solutions makes them more economical and ecological compared to disposable cells.
+Indeed, the long-term lifespan of rechargeable solutions makes them more economical and ecological compared to disposable cells.
 Such considerations have spurred the development of energy-harvesting systems.
@@
 Another avenue comes from the fact that the human body generates a considerable amount of energy from various types of movements or conditions.
-Among them, the electrochemical energy from the inner ear \cite{Mercier2012}, kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, thermal energy from body heat \cite{Kim2014}, and strain energy from skin deformation \cite{Jin2021} could be harvested for in-ear applications.
+Any of these, the electrochemical energy from the inner ear \cite{Mercier2012}, kinetic energy from walking or head movements \cite{Azimi2021,Smilek2016}, thermal energy from body heat \cite{Kim2014}, and strain energy from skin deformation \cite{Jin2021} could be harvested for in-ear applications.
 An interesting energy source for cochlear implants or hearing aids appears to be the earcanal's mechanical deformation.
-Delnavaz \emph{et al.} first showed in 2012 that the jaw movements change the earcanal's geometry during mastication.
+Delnavaz \emph{et al.} first studied in 2012 the power capability of the earcanal's geometry variation resulting from the jaw movements \cite{Delnavaz2012}.
 Carioli \emph{et al.} then used a customized earplug molding technique with a 3D scanner to characterize the global bending movement and local compression area in the earcanal during mastication \cite{Carioli2016}.
@@
 The experimental prototype was able to extract $44$\,µJ from a mastication cycle.
-The soft materials facilitated the bio-integration of the harvester, but the PVDF's low electromechanicalcoupling coefficient may have been the cause of poor energy conversion efficiency.
+The soft materials facilitated the bio-integration of the harvester, but the PVDF's low electromechanical coupling coefficient may have been the cause of poor energy conversion efficiency.
 A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
@@
 The earplug was equipped with a magnet in a water column surrounded by a coil.
-When the volume varied, the magnet would shift, generating energy.
-The generated energy experimentally amounted to 0.2µJ per mastication cycle.
+When the volume varied, the magnet would shift, generating energy by electromagnetic induction.
+The generated energy experimentally amounted to $0.2$\,µJ per mastication cycle.
 The prototype appeared to be less efficient than the PVDF earplug.
 This could be explained by the poor power generation of the electromagnetic transduction for a low frequency energy source (1.57\,Hz) and a small-scale application \cite{Kulah2008,Priya2017}.
-However, in this proposed model, the hydraulic transmission will enable the use of more complex and voluminous technological solutions since the energy will be made available outside, in other words, it will not be constricted by the earcanal's volume.
+However, in this proposed strategy, the hydraulic transmission will enable the use of more complex and voluminous technological solutions since the energy will be made available outside the earcanal.
 
@@
 
-The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but energy can be transmitted outside the earcanal which could benefit from larger effective space.
-The latter is essential to be able to implement an impedance adaptation stage and more effective transducing methods that could not otherwise fit directly inside the earcanal's limited volume.
+The hydraulic extraction strategy proposed in \cite{Delnavaz2012} is less effective than the piezoelectric earplug but if energy can be transmitted outside the earcanal the device could benefit from a larger effective space.
+The latter is essential to the implementation of an impedance adaptation stage and more effective transducing methods that could not otherwise fit directly inside the earcanal's limited volume.
 In fact, Marin \emph{et al.} demonstrated that the power generated by piezoelectric or electromagnetic transducers is proportionally greater as the effective volume of the transducing material is greater \cite{Marin2011}.
-Thus, the present work is based on the exploitation of the earcanal deformation using a liquid-filled earplug.
-As an energy source, it can be assimilated to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
-In order to optimize the energy extraction, the earplug must fit the earcanal wall snugly.
-Turcot \emph{et al.} demonstrated that the initial pressurization must reach a minimum of $14$kPa to achieve a good fit \cite{TURCOT2011}.
+Thus, the present work is based on exploiting the earcanal's deformation using a liquid-filled earplug.
+As an energy source, it is akin to a micro pump characterized by its volume variation $V_{ear}$ and pressure variation $p_{ear}$.
+To optimize energy extraction, the earplug must fit the earcanal wall snugly.
+Turcot \emph{et al.} demonstrated that the initial pressurization must reach a minimum of $14$\,kPa to achieve a good fit \cite{TURCOT2011}.
 Bouchard-Roy \emph{et al.} studied the dynamic pressure variation inside the earplug for different initial pressurization levels \cite{Bouchard-Roy2020}.
-A maximum of $\text{max}(\Delta p_{ear})=12$kPa of dynamic pressure variation, with a $28$kPa of initial pressurization, has been noted during the mastication for seven subjects.
-Besides, the temporal evolution of the volume variation $\Delta V_{ear}$ has been estimated in \cite{Delnavaz2012} and the result for a mastication cycle is presented on figure \ref{fig:deltaV_ear}.
+A maximum of $\text{max}(\Delta p_{ear})=12$\,kPa of dynamic pressure variation, with a $28$\,kPa of initial pressurization, was noted during mastication for seven subjects.
+Furthermore, the temporal evolution of the volume variation $\Delta V_{ear}$ has been estimated in \cite{Delnavaz2012} and the result for a mastication cycle is presented in Figure \ref{fig:deltaV_ear}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The earplug operation characteristic behaviour has not been studied yet.
+The characteristics of the liquid filled earplug's operating behavior have not been studied yet.
 Thus, the evolution of the volume variation $\Delta V_{ear}$ is not well known as a function of the pressure variation $\Delta p_{ear}$.
-Then, considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, the equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with the maximum values of $\Delta p_{ear}$ et $\Delta V_{ear}$ that have been recorded, i.e.
+Considering the pressure and volume variation levels from \cite{Delnavaz2012} and \cite{Bouchard-Roy2020}, equation \ref{eq:max_hydraulic_energy} approximates an upper limit for the extractable hydraulic energy with the maximum values of $\Delta p_{ear}$ and $\Delta V_{ear}$ that have been recorded, i.e.
 $p_c=12$\,kPa and $(\Delta V_{ear})_{max}=60$\,mm$^3$.
-$p_c$ stands for the comfort pressure by assuming that the user could feel discomfort if $\Delta p_{ear}>p_c$.
-The energy estimation presumes that the earplug is a perfect flow rate source, which is a theoretical hypothesis leading to $0.9$\,mJ available from one mastication.
-Based on 2200 mastication cycles per day, according to \cite{Goll2011}, there would be $2$\,mJ available per day, per ear.
-This amount of energy could theoretically enhance supply $23.5$\,\% of the $17$\,J of needed for the state of the art of cochlear implants \cite{Kulah2022}.
+$p_c$ stands for the comfort pressure by assuming that the user feels discomfort if $\Delta p_{ear}>p_c$.
+The energy estimation presumes that the earplug is a perfect flow rate source, which is a theoretical hypothesis leading to $0.72$\,mJ available from one mastication.
+If a person masticates 2200 cycles per day, which is the average according to \cite{Goll2011}, there would be $1.6$\,J available per day, per ear.
+This amount of energy could theoretically enhance the supply some $19$\,\% of the $17$\,J needed for the state of the art of cochlear implants \cite{Kulah2022}.
 Further research in both domains related to hearing aids and energy harvesting could lead to fully autonomous devices in the future.
 \begin{align}
-	\text{max}(E_{hyd}) = p_c \cdot (\Delta V_{ear})_{max} = 0.9\text{\,mJ}
+	\text{max}(E_{hyd}) = p_c \cdot (\Delta V_{ear})_{max} = 0.72\text{\,mJ}
 	\label{eq:max_hydraulic_energy}
@@
 Electromagnetic transducers are usually used to harvest energy from kinetic (vibration) energy sources.
-In fact, the power density of electromagnetic transducers decreases as much as the effective volume of transducing material and the frequency of the energy sources decreases \cite{Priya2017,Kulah2008}.
-Also, the fabrication and the integration of the coil and the moving magnet can come out to be difficult as the gap between the two components has to be carefully managed to prevent non-linear unpredicted responses \cite{Caruntu2001}.
-
-Piezoelectric ceramics appear like good candidates for mechanical energy transduction at small scales, but their high stiffness can limit their use on soft materials as human tissues.
-Mechanical amplifiers like flextensional structures can nevertheless be used to adapt the stress/displacement levels between the energy source and the transducing stiff material \cite{Abdelnaby2016}.
-Also, the best energy conversion efficiency for piezoelectric ceramics is achieved for at the transducer resonance.
-As the mean mastication frequency is estimated to \mbox{$1.57$Hz}, the harvesting system could benefit from a frequency-up conversion stage \cite{Ashraf2011,Peng2021} to increase the frequency of the energy source and so the energy conversion efficiency of the transducer.
-A majority of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
-Stoppers however dissipate energy.
+In fact, the power density of electromagnetic transducers decreases proportionately to the effective volume of the transducing material and the frequency of the energy sources decreases \cite{Priya2017,Kulah2008}.
+Also, the fabrication and integration of the coil and moving magnet may be a source of difficulty as the gap between the two components must be carefully managed to prevent non-linear and unpredicted responses \cite{Caruntu2001}.
+
+Piezoelectric ceramics appear to be good candidates for small-scale mechanical energy transduction, but their rigid structure limits their use with soft materials, such as human tissue.
+Mechanical amplifiers, like flextensional structures, can nevertheless be used to adapt the stress/displacement levels between the energy source and the stiff transducing material \cite{Abdelnaby2016}.
+Also, the best energy conversion efficiency for piezoelectric ceramics is achieved at the transducer's resonance.
+As the mean mastication frequency is estimated to \mbox{$1.57$\,Hz}, the harvesting system could benefit from a frequency-up conversion stage to increase the frequency of the energy source, which in turn increases the energy conversion efficiency of the transducer \cite{Ashraf2011,Peng2021}.
+Most of the frequency-up systems with piezoelectric transducers use mechanical stops with piezoelectric ceramic cantilevers to reach high frequencies with a good mechanical coupling \cite{Edwards2013,Gu2011,Lee2007}.
+However, stoppers dissipate energy.
 Alternative solutions use mechanically bistable resonators (BR) \cite{Vocca2012}.
-Recent works led to the development and optimization of bistable structures integrating stacked piezoelectric ceramics inside flextensional elastic structures \cite{Huguet2017}.
+Recent works led to the development and optimization of bistable structures integrating stacked piezoelectric ceramics within flextensional elastic structures \cite{Huguet2017}.
 They show enhanced performances due to high electromechanical coupling.
-The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers higher energy conversion efficiency compared to low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
+The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers a higher energy conversion efficiency than do low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
 
@@
 It can store the energy in the frequency-up converter by actuating it at the frequency of human mastication.
-The amount of extractable energy from the hydraulic source will then depend on the mechanical stage behavior.
-Before being converted in electricity, the energy is in fact stored in a mechanical potential reservoir.
+The amount of extractable energy from the hydraulic source will then depend on the harvester mechanical behavior.
+Before being converted into electricity, the energy is in fact stored in a mechanical potential reservoir.
 During the low frequency actuation, the forces applied on each side of the HC piston are equal.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows :
+Therefore, the potential energy stored in a linear resonator from the ideal hydraulic source previously described can be expressed as follows:
 \begin{equation}
@@
 It admits 2 stable equilibrium positions \mbox{$x_m=\pm x_0$}, an unstable one in \mbox{$x_m=0$} and its stiffness depends on its structural buckling level $\epsilon$ defined later in equation \ref{eq:epsilon_def}.
-The maximum theoretical energy in the BR for a quasi-static actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$} to \mbox{$x_m=0$} (eq.
+The maximum theoretical energy in the BR for a quasi-static actuation is equal to the height of the potential energy barrier $E_{pb}$ when the mass position varies from \mbox{$x_m=\pm x_0$} to \mbox{$x_m=0$} (Eq.
 \ref{eq:Ep_bar}).
-It will be a fraction $n$ of the upper limit of the available hydraulic energy (eq.
-\ref{eq:max_hydraulic_energy}) where $n$ has to be maximized.
+It will be a fraction $n$ of the upper limit of the available hydraulic energy (Eq.
+\ref{eq:max_hydraulic_energy}), where $n$ has to be maximized.
 \begin{equation}
@@
 \end{equation}
-We see later that it is inherently capable of exploiting $65$\,\% from the hydraulic energy source, which is $15$\,\% better than the best theoretical linear option.
-Section \ref{sec:SYSTEM MODELING} discusses the details of the modeling and design of the harvester that implements such a non-linear BR as it appeared to be a better solution than the linear approach.
+Hence, we see that it is inherently capable of exploiting $65$\,\% from the hydraulic energy source, which is $15$\,\% better than the best theoretical linear option.
+Section \ref{sec:SYSTEM MODELING} will discuss the modeling and design of a non-linear BR harvester, as this appears to be a better solution than the linear approach.
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
-	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the earcanal geometry variation} 
+	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the earcanal's geometry variation} 
 	\label{fig:system_presentation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The figure \ref{fig:system_presentation} presents a schematic view of the energy harvesting system.
-It uses a liquid filled earplug to transmit the energy outside the earcanal.
-To maximize the efficiency, the system integrates a frequency-up conversion stage obtained by a BR.
-The latter is associated with an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure containing stacked lead zirconate titanate (PZT) ceramics (fig.
+Figure \ref{fig:system_presentation} is a schematic view of the energy harvesting system.
+In this system, a liquid-filled earplug transmits the energy beyond the earcanal.
+To maximize its efficiency, the system has a frequency-up conversion stage that is obtained by a BR.
+The BR is connected to an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure that contains stacked lead zirconate titanate (PZT) ceramics (Fig.
 \ref{fig:APG}).
@@
 
-The electromechanical converter is actuated, by two hydraulic cylinders (HC), with the hydraulic energy transmitted from the liquid filled earplug, through a hydraulic amplifier (HA) and two hydraulic valves (HV).
-
-During a mastication cycle, the TMJ compresses the earcanal wall and expels the fluid out of the earplug.
-The HVs led the fluid alternatively to each HC in order to actuate the BR mass back and forth.
-The HA adapts both the cylinders stroke to the available earplug swept volume and the actuation force of the BR to the comfort pressure of the earcanal (fig.
+The electromechanical converter is actuated by two hydraulic cylinders (HC), the hydraulic energy being transmitted from the liquid-filled earplug trough a hydraulic amplifier (HA) and two hydraulic valves (HV).
+
+During a mastication cycle, the TMJ compresses the earcanal wall which expels the fluid out of the earplug.
+The HVs lead the fluid alternatively to each HC to actuate the BR mass back and forth.
+The HA adapts both the cylinders' stroke to the available earplug swept volume, and the actuation force of the BR to the comfort pressure of the earcanal (Fig.
 \ref{fig:system_presentation}).
 
-The BR mass has two stable equilibrium positions, \mbox{$x_m = x_0$ }and \mbox{$-x_0$}.
-The harvester operates on two major phases.
-The first consists on the BR mass actuation, by a HC, from one stable equilibrium position toward the unstable position at $x_m = 0$.
-During the second phase the mass reaches and oscillates around the opposite stable equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the GPA.
-The mass will move backward when the next mastication occurs and complete the harvester cycle.
+The BR mass has two equilibrium positions, \mbox{$x_m = x_0$ } and \mbox{$-x_0$}.
+The harvester operates during two major phases.
+The first is when the BR mass is actuated by a HC, from one equilibrium position toward the unstable position at $x_m = 0$.
+During the second phase the mass reaches and oscillates around the opposite equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the APG.
+The mass will move backward when the next mastication action occurs and this completes one harvester cycle.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 A technological solution for the HV is to use a flexible tube buckled by bending.
-The figure \ref{fig:HV_actuation_detail} schematizes the integration of such a HV around the BR environment.
-The HV is composed of a flexible tube connected to the hydraulic circuit between a rigid mobile and rigid fixed sheaths.
-It is in contact with the mass at the T point.
-The mass motion on the mobile sheath induces a bending angle $\theta$ around the rotational point $O$ located at the buckled section of the flexible tube.
-Consequently, a pressure loss is generated through the valve in buckled position.
+Figure \ref{fig:HV_actuation_detail} illustrates such a HV integrated on the BR.
+The HV is made of a flexible tube connected to the hydraulic circuit by rigid mobile and rigid fixed sheaths.
+The HV is in contact with the mass at point T.
+The mass motion on the mobile sheath induces a bending angle $\theta$ around rotational point $O$ located at the buckled section of the flexible tube.
+Consequently, a pressure loss is generated through the valve in its buckled position.
 The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
 This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
-Two HVs symmetrically placed on each side of the $\vec{z}$ axis set up an opened hydraulic circuit on one side and a closed one on the other side, depending on the BR mass position.
-The HV technological choice is motivated by three major arguments.
-First, the absence of dedicated electromechanical transduction compared to a more usual actuated valve minimizes the energy losses for the valve operation.
-Then, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
-Finally, it seems well adapted for integration purpose for millimetric application scale.
+Two HVs symmetrically placed on either side of the $\vec{z}$ axis set up an open hydraulic circuit on one side and a closed one on the other, depending on the BR mass's position.
+This technological choice for the HV is motivated by three main arguments.
+First, the absence of dedicated electromechanical transduction compared to a more commonly used actuated valve minimizes the energy losses during the valve's operation.
+Second, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
+Finally, it seems well adapted for applications that are on a  millimetric scale.
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 The harvester is a multiphysics system composed of hydraulic, mechanical, and electrical components.
-This section presents the global multiphysics model describing the system theoretical operation.
+This section presents the global multiphysics model and describes the system's theoretical basis of operation.
 Two coupled subsystems are considered.
-The subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
-Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the HA and the liquid filled earplug.
-
-This work challenges are focused on the experimental validation of the electromechanical converter cycled by two hydraulic valves.
-In fact, several hydraulic miniature solutions are introduced by the literature for both of the components \cite{Wang2020,Xu2021,Zhu2013}.
-Hence, this section neglects the energy loss inside the HA and the HCs.
-These hydraulic components will rather be considered on further work.
+Subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
+Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, two HCs, HA and liquid-filled earplug.
+
+The challenge of this work lies in the experimental validation of the electromechanical converter cycled by two HVs and two HCs.
+Several hydraulic miniature solutions have been introduced in the literature for HAs and HCs \cite{Wang2020,Xu2021,Zhu2013}.
+Hence, this section neglects the energy loss of both of the components.
+Rather, these hydraulic components will be considered in further work.
     %///////////////////////////////////////////// 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip, width=0.9\textwidth]{figures/schema_cinematique1.pdf}
-	\caption{Kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC}
+	\caption{Kinematic scheme of the electromechanical converter under the mechanical influence of a HV and HC}
 	\label{fig:schema_cinematique1}
@@
 
-The figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical influence of a HV and a HC.
-The different rigid bodies are defined in the table \ref{tab:Designation of rigid bodies}.
-The BR is represented by 4 identical arms articulated by 8 hinges and a central mass.
-the hinges angle $\varphi$ is defined as follows :
+Figure \ref{fig:schema_cinematique1} shows the kinematic scheme of the electromechanical converter under the mechanical forces of the HV and HC.
+The various rigid bodies are defined in Table \ref{tab:Designation of rigid bodies}.
+The BR is shown as 4 identical arms articulated by 8 hinges and a central mass.
+The hinge's angle $\varphi$ is defined by:
 \begin{equation}
@@
 \end{equation}
-The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by the equation \ref{eq:k2_def}.\\
+The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by Equation \ref{eq:k2_def}.\\
 The model is based on the following hypotheses:
@@
 By isolating the BR mass and using Newton's 2$^{nd}$ law, we can express its dynamic equilibrium.
-The projection on the $\vec{x}$ axis of the resulting expression is given by the equation \ref{eq:OB-GPA}.
+The projection on the $\vec{x}$ axis of the resulting expression is given by Equation \ref{eq:OB-GPA}.
 The BR mechanical equilibrium has a mass inertial term, a non-linear stiffness depending on $x_m$, the stiffness of the hinge $K_{\varphi}$ and viscous losses.
-The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at the contact point $T$ (see fig.
+The first term introduced by the HV is related to its rotational stiffness $K_{HV}$ and the second term is related to the friction losses at contact point $T$ (see fig.
 \ref{fig:HV_actuation_detail}).
-$K_{HV}$ and $K_{\varphi}$ both act the same way by shifting the stable equilibrium positions of the BR toward $0$ as much as they increase.
+$K_{HV}$ and $K_{\varphi}$ both act in the same way by shifting the stable equilibrium positions of the BR toward $0$ as much as they increase.
 A dry friction model is chosen to describe the dissipation effect of the contact.
-The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the material that are rubbing against each others, and by the sign of $\dot{x}_m$.
-The pressure $p_{hc,a}$ induces the HC hydraulic force and the coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HCs.
+The rubbing efforts depend on a dry friction coefficient $f_d$, related to the nature of the materials that are rubbing together, and by the sign of $\dot{x}_m$.
+Pressure $p_{hc,a}$ induces the HC hydraulic force, and coefficient $\mu_{hc}$ models the viscous friction at the sealing gasket of the HCs.
 The hydro-mechanical coupling will be detailed later.
 
-The electrical power generated by the APG is dissipated in a load resistor $R_l$ calculated with an adaptive impedance matching expressed in the equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
+The electrical power generated by the APG is dissipated in a load resistor $R_l$, calculated using adaptive impedance matching, as expressed in Equation \ref{eq:R_ch_adaptive_imp} \cite{Liu2013}. 
 \begin{equation}
@@
 \end{equation}
-Thus, the electrical equation of the APG is :
+Thus, the electrical equation of the APG is:
 \begin{equation}
@@
 \end{equation}
-Consequently, the generated power $P_e$ expression is :
+Consequently, the generated power $P_e$ expression is:
 \begin{equation}
@@
 Equation \ref{eq:theta_fonction_de_xm} defines the implicit relation between $\theta$, $x_m$ and the geometrical parameters of the setup.
-Additionally, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$, as showed in figure \ref{fig:HV_actuation_detail}.
+Additionally, the HV stiffness $K_{HV}$ will depend on its bending angle $\theta$, as showed in Figure \ref{fig:HV_actuation_detail}.
 %%%%%%%%%%%%%%%%%%%%%%%
@@
     %/////////////////////////////////////////////
-In order to model the coupled behaviour of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
-The following hypotheses will be considered :
+In order to model the coupled behavior of the two hydraulic branches, we will use the index "$a$" for the active branch where the fluid flows and the index "$i$" for the inactive one. \\
+The following hypotheses will be considered:
 \begin{itemize}
@@
 \end{itemize}
-The mechanical equilibrium is :
+The mechanical equilibrium is:
 \begin{align}
@@
 \end{align}
-The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
+The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and on the BR mass's position $x_m$ (Fig.
 \ref{fig:HV_actuation_detail}).
@@
 Its minimal value $Cf_0$ is obtained when the HV is unbent.
-We assume at first that the relationship between $Cf$ and $x_m$ is linear and defined as follows :
+We assume at first that the relationship between $Cf$ and $x_m$ is linear and defined as follows:
 \begin{align}
@@
 \end{align}
-The pressure loss coefficient $Cf$ for a buckled flexible tube will depend on the HV bending angle $\theta$ and therefore on the BR mass position $x_m$ (fig.
-\ref{fig:HV_actuation_detail}).
-$Cf$ will become more important as $x_m$ increases.
-It is minimal when the HV is unbent and is worth $Cf_0$.
-The literature does not provide the constitutive relation between $x_m$ and $Cf$, thus we first assume that it is linear and defined as follows :
-\begin{align}
-Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m 
-\label{eq:Cf(x_m)_linear}
-\end{align}
-Where $Cf_c=Cf(\pm x_0)$. Regarding the BR symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.
-
-Using the Bernoulli's equation for a current line, we can express the earplug inside pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with the equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
+where $Cf_c=Cf(\pm x_0)$. Regarding the BR symmetry, the relation between $Cf$ and $x_m$ must be an even function to enable the system cycling, i.e., $Cf(x_m) = Cf(-x_m)$.
+
+Using Bernoulli's equation for a current line, we can express the earplug's internal pressure $p_{ear}$ as a function of the hydraulic resistance in the two parallel branches with Equations \ref{eq:Bernoulli_piston_ouvert} and \ref{eq:Bernoulli_piston_ferme}.
 \begin{align}
@@
 \end{align}
-Where $a_h$ is the hydraulic amplification ratio and $q$ the fluid flow rate.
-
-The no leakage assumption imposes that all the fluid exiting the earplug is contained in the two hydraulic branches (eq. \ref{eq:conservation_masse}).
+where $a_h$ is the hydraulic amplification ratio and $q$ the fluid flow rate.
+
+The no-leakage assumption means that any fluid exciting the earplug flows into the two hydraulic branches (Eq. \ref{eq:conservation_masse}).
 \begin{equation}
@@
 \end{equation}
-Moreover, the fluid entering the HC necessarily results on a piston displacement (eqs. \ref{eq:conservation_masse_ouvert},\ref{eq:conservation_masse_ferme}).
+Moreover, the fluid entering the HC necessarily results in a piston displacement (Eqs. \ref{eq:conservation_masse_ouvert},\ref{eq:conservation_masse_ferme}).
 \begin{align}
@@
     %///////////////////////////////////////////// 
-	\subsection{The harvester parameters setting}	
+	\subsection{Setting the harvester parameters}	
 	\label{subsec:The harvester setting}
     %/////////////////////////////////////////////
-The energy system combines many variable parameters. In order to determine them, it is first necessary to identify the fixed technological elements: 
+The energy system combines several variable parameters. To determine these, we first need to identify the fixed technological elements: 
 \begin{itemize}
@@
 \end{itemize}
-The system is designed by setting the two coupled requirements to enable the system operation.
-First, the available swept volume must be enough to ensure the HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (eq.
+The system was designed by first setting the two coupled requirements so as to enable the system to work.
+First, the available swept volume must produce a large enough HC stroke from its equilibrium position until the BR mass reaches \mbox{$x_m=0$} (Eq.
 \ref{eq:contrainte_course}).
-Then, the BR mechanical force on $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
-At this point, a maximum pressure is induced in the earplug and so the equation \ref{eq:contrainte_confort} has to be verified to guarantee the pressure limit.
-If not, $\epsilon$ can be decreased, diminishing the extracted energy.
+The BR mechanical force on the $\vec{x}$ axis reaches a maximum value $F_c$ when \mbox{$ x_m = x_c = \dfrac{x_0}{\sqrt{3}}$}.
+At this point, a maximum pressure is induced in the earplug and Equation \ref{eq:contrainte_confort} needs to be verified to remain within the pressure limit.
+If it exceeds the limit, $\epsilon$ can be decreased, diminishing the extracted energy.
 \begin{empheq}[left=\empheqlbrace]{align} 
@@
 	\label{eq:contrainte_course}\\
-	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with}~~~~ F_c = \dfrac{4Kx_0\epsilon}{3\sqrt{3}}
+	p_c > \frac{1}{a_h} \frac{F_c}{S_{hc}} ~~~~ \text{with} ~~~~ 
+	        F_c = \dfrac{4Kx_0\epsilon}{3\sqrt{3}}
 	\label{eq:contrainte_confort}
@@
 Regarding the technological choices and the system operation requirements, we can evaluate $n=65\%$.
-This value can be compared to the best theoretical linear energy extraction solution described in \ref{eq:best_linear_soution}.
-	%///////////////////////////////////////////// 
-	\subsection{Targeted hydraulic behaviour of the HVs}	
+This value can be compared to the best theoretical linear energy extraction solution described in Section \ref{eq:best_linear_soution}.
+	%///////////////////////////////////////////// 
+	\subsection{Targeted hydraulic behavior of the HVs}	
 	\label{subsec:HV hydraulic targeted behaviour}
@@
 A multiphysics coupled model has been established with the equations and the preliminary dimensioning previously introduced.
-The unknown remaining key parameter stays the hydraulic behaviour $Cf(x_m)$ of the HVs.
-The ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch.
-So we introduce the hydraulic restriction coefficient $r_{Cf}$ defined as follows :
+The key parameter that remains unknown is the hydraulic behavior $Cf(x_m)$ of the HVs.
+The ratio between the pressure loss coefficient of the closed HV and that of the opened HV must be sufficient to force the flow through the opened branch.
+Thus, we introduced a hydraulic restriction coefficient $r_{Cf}$, defined as follows:
 \begin{equation}
@@
 \end{equation}
-The numerical resolution of the coupled differential equations \ref{eq:APG_elec},\ref{eq:OB-GPA}, \ref{eq:equilibre_dynamique_piston_ferme}, \ref{eq:Bernoulli_piston_ouvert}, \ref{eq:Bernoulli_piston_ferme}, \ref{eq:conservation_masse}, \ref{eq:conservation_masse_ouvert} and \ref{eq:conservation_masse_ferme} can provide the minimum value $(r_{Cf})_{min}$ to reach in order to perform the adequate hydraulic commutation.
+The numerical resolution of the coupled differential equations \ref{eq:APG_elec},\ref{eq:OB-GPA}, \ref{eq:equilibre_dynamique_piston_ferme}, \ref{eq:Bernoulli_piston_ouvert}, \ref{eq:Bernoulli_piston_ferme}, \ref{eq:conservation_masse}, \ref{eq:conservation_masse_ouvert} and \ref{eq:conservation_masse_ferme} can provide the minimum value $(r_{Cf})_{min}$ that needs to be reached to achieve an adequate hydraulic commutation.
 	%///////////////////////////////////////////// 
@@
 	%/////////////////////////////////////////////
-By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig.
-\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanic and electric coupled variables defining the harvester.
+By imposing a volume variation of $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (Fig.
+\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanical and electrical coupled variables defining the harvester.
 The earplug is assumed to be a perfect flow rate source.
-The mastication cycle is identically used 4 times in order to test the system cycling robustness.
-The fixed, designed and resulting theoretical parameters of the simulated global model are presented in tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
-
-Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results of the mass and the HC pistons positions over overlaid with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
-The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), noting that the gravity influence is not considered.
-The same figure shows a focused view on the two main phases of the harvester operation during the actuation by the \emph{"bottom"} HC.
+The mastication cycle is identically applied 4 times to test the system's cycling robustness.
+The fixed, designed and resulting theoretical parameters of the simulated global model are presented in Tables \ref{tab:parametres électromécaniques} and \ref{tab:parametres_hydrauliques}.
+
+Figure \ref{fig:positions+DeltaV_debits_pear} shows the simulation results of the mass and HC piston positions overlaid with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure.
+The two different sides are identified on the curves by indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), noting that the effects of gravity are not considered.
+The same figure shows a focused view on the two main phases of the harvester operation during the actuation of the \emph{"bottom"} HC.
 The simulation begins with the following initial conditions:
@@
 	\item There is no contact between the mass and the HCs.
-	\item A mastication occurs.
+	\item A mastication cycle is initiating.
 \end{itemize}
 
-During a first phase the BR mass is pushed until it reaches $x=0$.
-The fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
+During a first phase, the BR mass is pushed until it reaches $x=0$.
+The fluid exiting the earplug is mostly guided toward the \emph{"bottom"} HC and a pressure is induced in the earplug by the BR counter-reaction force.
 The mass then crosses $x_m=0$ and the second phase begins.
 The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$).
-The fluid is then directed toward the \emph{"top"} side and there is no contact between the mass and a HC.
+The fluid is then directed toward the \emph{"top"} side and there is no contact between the mass and an HC.
 The mass oscillates around $x_m=x_0$ and energy is harvested by the APG.
@@
 
-Figure \ref{fig:positions_Up_puissances_energies} additionally presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
+Figure \ref{fig:positions_Up_puissances_energies} also presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
 The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\,\%} with 22\,µJ electrical energy harvested from one mastication.
-The energy losses are mostly located in the BR stage and depend on the quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
-The energy source depends on the comfort pressure level $p_c$ that is set to 1\,kPa, i.e.
-a fraction of the theoretical maximal value of $12$\,kPa \cite{Bouchard-Roy2020}.
-The harvester theoretical efficiency could lead to a maximum of 684\,µJ extractable from the earcanal.
+The energy losses are mostly located in the BR stage and depend on quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
+The energy source depends on comfort pressure level $p_c$ that is set to 1\,kPa, i.e., a fraction of the theoretical maximal value of $12$\,kPa \cite{Bouchard-Roy2020}.
+The harvester's theoretical efficiency could reach a maximum extractable energy of 612\,µJ.
 
@@
     %///////////////////////////////////////////// 
-	\subsection{The electromechanical converter presentation}	
-	\label{The electromechanical converter presentation}
+	\subsection{Description of the electromechanical converter}	
+	\label{Description of the electromechanical converter}
     %/////////////////////////////////////////////
 The BR is fabricated by electrical discharge machining (EDM) in a monobloc structure.
-This method optimizes the resonator quality factor by avoiding assemblies.
+This method provides better resonator quality factor than when there are assemblies.
 Figure \ref{fig:BDT_OB+GPA} shows the BR mounted on the experimental test bench.
-The 8 hinges are realized by 4 buckled blades (BB) while a vertical guide beam (GB) ensures the APG mounting and avoids any of its rotations.
+The 8 hinges are ensured using 4 buckled blades (BB) while a vertical guide beam (GB) ensures the APG mounting and prevents any rotations.
 The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
-They also maximize the BB compression stiffness that maximizes harvester efficiency, as we show in the following section.
-The geometrical and mechanical parameters of the BR are referenced in table \ref{tab:parametres_lames}.
-The following sections describe the design method that led to the dimensions of the blades that depend on our needs.
+They also maximize the BB compression stiffness that maximizes harvester efficiency, as we will explain in the following section.
+The geometrical and mechanical parameters of the BR are referenced in Table \ref{tab:parametres_lames}.
+The following sections describe the design method that led to the dimensions of the blades, based on the needs of the application.
 %%%%%%%%%%%%%%%%%
@@
     %///////////////////////////////////////////// 
-	\subsection{BR beams design}	
+	\subsection{Designing the BR beams}	
 	\label{subsec:BR beams design}
     %/////////////////////////////////////////////
-The harvesting happens during the free oscillation phase.
-The main issue is to maximize the energy conversion efficiency $\eta_{ob}$ of this stage.
-Richards \emph{et al.} demonstrated that for the piezoelectric transduction at the resonance frequency, it can be approximated with the equation \ref{eq:eta_ob} \cite{Richards2004}.
+In the proposed system, energy harvesting occurs at the oscillation phase.
+The main issue is to maximize the energy conversion efficiency $\eta_{br}$ of this stage.
+Richards \emph{et al.} demonstrated that for the piezoelectric transduction at the resonance frequency, it can be approximated with Equation \ref{eq:eta_ob} \cite{Richards2004}.
 This expression is valid for an electric extraction based on the adaptive impedance matching strategy.
@@
 \end{equation}
-$k^2_{sys}$ is the global electromechanical coupling coefficient of the harvesting system.
-The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the beams (tab.
-\ref{tab:parametres_lames}) as follows :
+where $k^2_{sys}$ is the global electromechanical coupling coefficient of the harvesting system.
+The latter can be expressed with the electromechanical parameters of the APG and the stiffness of the beams (Table \ref{tab:parametres_lames}) as follows :
 \begin{equation}
@@
 \end{equation}
-Where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by equation \ref{eq:alpha_eq}.
-It depends on the APG PFF and on the ratio between the equivalent stiffness $K_{eq}$ (eq.
+where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by Equation \ref{eq:alpha_eq}.
+It depends on the APG PFF and on the ratio between the equivalent stiffness $K_{eq}$ (Eq.
 \ref{eq:K_eq}) of the structure on the $\vec{z}$ axis and the equivalent stiffness of the APG mounted on the GB.
@@
 \end{equation}
-Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{ob}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
+Equations \ref{eq:eta_ob} - \ref{eq:K_eq} combined demonstrate that in order to maximize $\eta_{br}$ we must make sure that $K_{bb} \gg K \gg K_{gb}$.
 If the condition is respected, then $K_{eq}$ can be assimilated to $K$ and $\alpha_{eq} \approx \alpha$.
@@
 When the mass crosses the unstable \mbox{$x_m=0$} position, the compression force $F_{z,0}$ induces the maximum stress on the BB.
-$F_{z,0}$ can be expressed by equation \ref{eq:Fz0_flambement}.
+$F_{z,0}$ can be expressed by Equation \ref{eq:Fz0_flambement}.
 $K_{bb}$ can then be assured if the compression efforts absorbed by the BBs do not induce any secondary buckling mode during the BR operation.
@@
 \end{equation}
-The beams design was obtained using a FEM model which result is summarized in the figure \ref{fig:buckling_limit}.
+The beams design was obtained using a FEM model whose results are summarized in Figure \ref{fig:buckling_limit}.
 It reveals that the first secondary undesirable buckling mode appears for $F_{z,0}=6.4$\,N.
-If it happens, the compression force is not transmitted from the mass to the APG.
-$K_{bb}$ is then not assured and therefore $k^2_{sys}$ is diminished (eq.
+If this happens, the compression force is not transmitted from the mass to the APG, $K_{bb}$ is not assured and $k^2_{sys}$ is diminished (Eq.
 \ref{eq:k2_sys}).
-We establish a buckling height domain (fig.
-\ref{fig:buckling_limit}) to avoid their appearance for the fabricated BR.
+Thus, we establish a buckling height domain (Fig.
+\ref{fig:buckling_limit}) to avoid the secondary buckling for the fabricated BR.
 The preliminary simulated case presented in the previous section is in the preferable domain.
-Moreover, the force absorbed by the APG is assured to be under the maximal limit of $18$\,N from which the device could be damaged.
+Moreover, the force absorbed by the APG must be under the maximal limit of $18$\,N above which the device could become damaged.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     %/////////////////////////////////////////////
-The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented on figure \ref{fig:BDT_OB+GPA}.
-An additional beam is mounted with the APG in order to prevent its rotation around any axis.
-A micrometric screw sets the initial buckling level $x_0$ ($\pm 10$\,µm).
-The bearing decouples the rotation of the screw with the beam structure in order to prevent unwanted torsional stress.
-The central mass $\degree{45}$ place receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and allows to get the $x_m$ position.
+The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented in Figure \ref{fig:BDT_OB+GPA}.
+An additional beam is mounted with the APG to prevent any rotation whatsoever.
+A micrometric screw sets the initial buckling level to $x_0$ ($\pm 10$\,µm).
+The bearing decouples the rotation of the screw with the beam structure to prevent unwanted torsional stress.
+The central mass at $\degree{45}$ receives and reflects the displacement sensor emitted laser along the $\vec{z}$ axis and captures the $x_m$ position.
 The APG power is dissipated in the $R_l$ resistor and the $U_p$ voltage ($\pm 1$\,mV), along with $x_m$, are monitored through a data acquisition card NI-USB 6212 and a LabVIEW interface.
@@
 The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
-This data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (tab.
-\ref{tab:parametres_lacher_free}).
+This data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (Table \ref{tab:parametres_lacher_free}).
 The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ were also calculated.
@@
 	\end{tabular}}
-	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
+	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter's parameters.}
 	\label{tab:parametres_lacher_free}
@@
 
-Experimental $K_{bb}\approx K/2$ can be calculated from the identified $K_{eq}$ with equation \ref{eq:K_eq}, supposing $K_{gb}$ negligible (tab. \ref{tab:parametres_lames}).
-    %///////////////////////////////////////////// 
-	\subsection{Analyze and summary}	
+Experimental $K_{bb}\approx K/2$ can be calculated from the identified $K_{eq}$ with Equation \ref{eq:K_eq}, supposing $K_{gb}$ is negligible (Table \ref{tab:parametres_lames}).
+    %///////////////////////////////////////////// 
+	\subsection{Analysis and summary}	
 	\label{subsec:Analyze and summary}
     %/////////////////////////////////////////////
-The experimental dynamic behaviour of the converter is predictable by the equations established after identification of the system parameters listed in table \ref{tab:parametres_lacher_free}.
-However, the performances of the experimental prototype are below the theoretical expectations (tab.
-\ref{tab:parametres électromécaniques}).
-The efficiency drop is mainly associated with the quality factor and the electromechanical coupling coefficient drop (eq.
+The experimental dynamic behavior of the converter is predictable using the equations established once the system parameters, listed in Table \ref{tab:parametres_lacher_free} had been identified.
+However, the performances of the experimental prototype are below the theoretical expectations (Table \ref{tab:parametres électromécaniques}).
+This efficiency discrepancy is mainly associated with the quality factor and the electromechanical coupling coefficient drop (Eq.
 \ref{eq:eta_ob}).
 
-The quality factor decrease could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
-The small undulations have been observed on the BBs after fabrication and could also have gotten worse during the manipulation.
-These undulations aid the appearance of secondary buckling modes and contribute to reduce $K_{bb}$, diminishing $k^2_{sys}$ according equations \ref{eq:k2_sys}-\ref{eq:K_eq}.
-Improvements are proposed later in order to reduce the energy losses during this stage.
+The decrease in quality could be related to the general non-permanent assembly that uses non-perfect embeddings with fixation screws and a mobile micrometric screw.
+Small undulations were observed on the BBs after fabrication and may also have gotten worse during the manipulation.
+These undulations increase the probability of secondary buckling which contribute to reducing $K_{bb}$ and diminishing $k^2_{sys}$, according to Equations \ref{eq:k2_sys}-\ref{eq:K_eq}.
+Improvements are proposed further on to resolve this issue and reduce the energy losses during this stage.
 
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-In order to validate the feasibility of the HVs we adopted an experimental approach to find the material and geometrical parameters of the tube to achieve $(r_{Cf})_{min}=26$ (tab.
+To validate the feasibility of the HVs, we adopted an experimental approach to find the material and geometrical parameters of the tube to achieve $(r_{Cf})_{min}=26$ (Tab.
 \ref{tab:parametres_hydrauliques}).
 A buckled kapton tube \cite{Dupont2012} of internal diameter $D_t=1.05$\,mm and thickness $th_t=25$\,µm was found to meet this hydraulic criteria.
-It will be called HV$_{T1}$ afterwards.
+It will be referred to as HV$_{T1}$.
     %///////////////////////////////////////////// 
@@
 Figure \ref{fig:essais_hydraulique_VH} shows the HV$_{T1}$ during the experimental characterizations on the hydraulic test bench.
-An electromechanical rotary plate is monitored on LabVIEW interface and imposes a bending angle $\theta$.
-A liquid filled syringe fixes the fluid flow through the HV$_{T1}$ and $q_{syr}$ is evaluated by tracking the syringe piston displacement.
-The pressure loss coefficient $Cf_{T1}$ is calculated as \mbox{follows :}
+An electromechanical rotary plate is monitored on the LabVIEW interface and imposes a bending angle $\theta$.
+A liquid-filled syringe sets the fluid flow through the HV$_{T1}$ and $q_{syr}$ is evaluated by tracking the syringe piston displacement.
+The pressure loss coefficient $Cf_{T1}$ is calculated as \mbox{follows:}
 \begin{equation}
@@
 \end{equation}
-Where $p_1$ and $p_2$ are the fluid pressure monitored before entering and after exciting the HV$_{T1}$ respectively.
+where $p_1$ and $p_2$ are the fluid pressures monitored before entering and after exiting the HV$_{T1}$ respectively.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 The tests were repeated 7 times for $\theta$ varying from $0^{\circ}$ to $60^{\circ}$ with $10^{\circ}$ increments.
-The experimental results are plotted on figure \ref{fig:resultats_essais_hydraulique_VH_D1mm}.
+The experimental results are plotted on Figure \ref{fig:resultats_essais_hydraulique_VH_D1mm}.
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%
-The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to $r_{Cf}60$ if the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
+The hydraulic restriction coefficient of the HV$_{T1}$ has been evaluated to $r_{Cf}60$ if we consider the opened angle $\theta_0=20^{\circ}$ and the closed angle $\theta_c = 60^{\circ}$.
 Its hydraulic behavior respects the minimum criteria of \mbox{$(r_{Cf})_{min}=26$} and therefore can ensure the adequate hydraulic commutation to cycle the BR mass motion.
-In order to set an optimal angle operation range $\Delta\theta$ we must investigate the evolution $K_{HV}(\theta)$.
-This matter will not be discussed in this paper.
-However, $\Delta\theta$ must be minimized in order to limit the energy needed for the HVs operation and also, $\theta_0$ must be minimized to reduce the hydraulic energy losses in the active branch.
+In order to set an optimal angle operation range $\Delta\theta$, we must investigate the evolution $K_{HV}(\theta)$.
+This will not be discussed in this paper.
+However, $\Delta\theta$ must be minimized in order to limit the energy needed for the HV's operation and also, $\theta_0$ must be minimized to reduce the hydraulic energy losses in the active branch.
 
@@
 The experimentally identified parameters have been implemented in the global multiphysics coupled model to enhance its predictability and to evaluate the harvester performances.
-The mechanical influence of the HV$_{T1}$ is identified with an experimental approach characterizing the energy losses at the HV-mass contact point (T on figure \ref{fig:HV_actuation_detail}).
+The mechanical influence of the HV$_{T1}$ is identified with an experimental approach, characterizing the energy losses at the HV-mass contact point (T on Figure \ref{fig:HV_actuation_detail}).
 	%/////////////////////////////////////////////
@@
 	%/////////////////////////////////////////////
-The HV$_{T1}$ has been mounted on the experimental test bench presented on figure \ref{fig:BDT_OB+GPA} and two experimental trials have been performed to identify the HV mechanical influence : free oscillations and oscillations with HV$_{T1}$ presence, during a harvesting phase.
-Thus, the dynamics difference between the two tests focus on the HV$_{T1}$ mechanical influence.
-
-The mass is initially set on $x_m=x_0$ and then pushed toward $x_0$.
-The HV$_{T1}$ internal pressure is adjusted to $30$\,kPa with an oil column, in order to be consistent with the simulated case (tab.
+The HV$_{T1}$ was mounted onto the experimental test bench presented in Figure \ref{fig:BDT_OB+GPA} and two experimental trials were performed to identify the HV mechanical influence: free oscillations and oscillations with the presence of the HV$_{T1}$, during a harvesting phase.
+Thus, the difference in the dynamics between the two tests focuses on the HV$_{T1}$'s mechanical influence.
+
+The mass is initially set to $x_m=x_0$ and then pushed toward $x_0$.
+The HV$_{T1}$'s internal pressure is adjusted to $30$\,kPa with an oil column, in order to be consistent with the simulated case (Tab.
 \ref{tab:parametres_hydrauliques}).
 The oscillation phase begins when the mass crosses the $x_m=0$ position.
-In order to set $\theta_0$ we add two angle stoppers illustrated on figure \ref{fig:contact_M_VH_lachers}.
+In order to set $\theta_0$, we added two angle stoppers, illustrated in Figure \ref{fig:contact_M_VH_lachers}.
 $\theta_c$ is then reached when the oscillations stop at $x_m=x_0$.
-The mass position and the APG tension are monitored during the tests.
+The mass position and the APG tension were monitored during the tests.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
@@
 
-The global model parameters listed in table \ref{tab:parametres lacher tube} are recalibrated for both test configurations by iterative simulations.
-The simulations with the recalibrated parameters and the experimental data are superposed on figure \ref{fig:BDT_OB+GPA} concerning the harvesting phase of both configurations.
-
-After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamic behaviour of the harvester is theoretically predictable by the established model.
-The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and equation \ref{eq:OB-GPA}.
+The global model parameters listed in Table \ref{tab:parametres lacher tube} are recalibrated for both test configurations by iterative simulations.
+The simulations with the recalibrated parameters and the experimental data are superimposed on Figure \ref{fig:BDT_OB+GPA} concerning the harvesting phase of both configurations.
+
+After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamic behavior of the harvester is theoretically predictable by the established model.
+The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and Equation \ref{eq:OB-GPA}.
 The HV$_{T1}$ adds a supplementary dynamic mass in the BR and changes the oscillation frequency.
-The electromechanical coupling coefficient is not influenced by the HV presence.
+The electromechanical coupling coefficient is not influenced by the presence of the HV.
 The quality factor decreases and the dry friction coefficient is calculated from the drop.
@@
 	\end{subfigure}
-	\caption{Experimental measurements and global system simulation with the identified parameters of table \ref{tab:parametres lacher tube}.}
+	\caption{Experimental measurements and global system simulation with the identified parameters of Table \ref{tab:parametres lacher tube}.}
 	\label{fig:recalage_global}
@@
 	\end{tabular}
-        \caption{Value des paramètres de l'OB et de l'ensemble OBVH implémentant le tube T100p suite au essais de lâchers expérimentaux}
+        \caption{Experimentally recalibrated values of the harvester parameters with and without the presence of the HV$_{T1}$.}
         \label{tab:parametres lacher tube}
@@
 	%/////////////////////////////////////////////
-	\subsection{Analyse and discussion}
-	%/////////////////////////////////////////////
-The experimental hydraulic behaviour of the HV$_{T1}$ is theoretically capable to provide \mbox{$r_{Cf}>26$} and ensure the hydraulic adequate commutation cycling the BR mass motion.
-
-The quality factor decrease results from the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
-The friction losses can be minimized by an order of magnitude by using materials with low friction coefficient like teflon \cite{Nosonovsky2013}.
+	\subsection{Analysis and discussion}
+	%/////////////////////////////////////////////
+The experimental hydraulic behavior of the HV$_{T1}$ is theoretically capable of providing \mbox{$r_{Cf}>26$} and ensuring an adequate hydraulic commutation cycling for the BR mass's motion.
+
+The quality factor decrease is due to the rubbing between the mass and the HV and diminishes the BR energy conversion efficiency.
+The friction losses can be minimized by an order of magnitude by using materials with low friction coefficient, like teflon \cite{Nosonovsky2013}.
 The HV-mass contact can also profit from magnetic interactions instead of direct rubbing.
 
-The global electromechanical coupling is not influenced by the HV presence, which is consistent with equation \ref{eq:k2_sys}.
-The major part of the energy loss is due to the $k^2_{sys}$ drop as a result of the softening of the BBs from the prototype fabrication and manipulation.
-It can be minimized by using thicker BBs while taking care that the buckling domain does not reach the critical point where the APG could be damaged (fig.
+The global electromechanical coupling is not influenced by the presence of the HV, which is consistent with Equation \ref{eq:k2_sys}.
+Most of the energy loss is due to the $k^2_{sys}$ drop as a result of the softening of the BBs from the prototype fabrication and manipulation.
+It can be minimized by using thicker BBs while taking care that the buckling domain does not reach the critical point where the APG could be damaged (Fig.
 \ref{fig:buckling_limit}).
-With $200$\,µm thick BBs instead of $75$\,µm, we can expect 26\,\% improvement on $\eta_{br}$ (eqs.
+With BBs having a thickness of $200$\,µm instead of $75$\,µm, we can expect 26\,\% improvement on $\eta_{br}$ (Eqs.
 \ref{eq:eta_ob}-\ref{eq:K_eq}).
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-This work emphasizes the energy need for hearing aids and the exploitation of the mechanical deformation of the earcanal as a solution to enhance the autonomy of those devices batteries.
+This work emphasizes the need to enhance the autonomy of the batteries of devices such as hearing aids and the exploitation of the mechanical deformation of the earcanal as a solution.
 
@@
 Its numerical evaluation predicts that the system can theoretically harvest 85\% of the available energy with a hydraulic extraction method.
-The dynamic behaviour and the performances of the fabricated electromechanical converter composed of the BR and the APG are evaluated.
-A new concept of HVs is proposed, based on the bending buckling of flexible tubes.
-A HV design is proposed with experimental investigation based on the theoretical needed behaviour extracted from the numerical simulations.
-
-The experimental data are used to recalibrate the harvester multiphysics model and to evaluate its performances.
+The dynamic behavior and the performances of the fabricated electromechanical converter composed of a BR and APG are evaluated.
+A new concept of HVs is proposed, based on the buckling of flexible tubes.
+A HV design is proposed with experimental investigation based on the theoretical needed behavior extracted from the numerical simulations.
+
+The experimental data was used to recalibrate the harvester multiphysics model and to evaluate its performances.
 The global predicted efficiency is $\eta_g=2.6\,\%$.
-The energy losses factors are identified and solutions are proposed in order to increase the efficiency up to 26\%.
+The energy losses factors are identified and solutions are proposed to increase the efficiency to 26\%.
 
@@
 The authors would like to thank Jacob Bouchard-Roy for the data on jaw-joint hydraulic source as well as Michel Demuynck for the constructive exchanges on earcanal deformation.
-This work was made possible via funding from the NSERC Discovery program (RGPIN-2017-06192) held by last author, the technical support from the ÉTS-EERS Industrial Research Chair in In-Ear Technologies (CRITIAS), as well as the laboratory infrastructures of the SYMME.
+This work was made possible via funding from the NSERC Discovery program (RGPIN-2017-06192) held by the last author, the technical support from the ÉTS-EERS Industrial Research Chair in In-Ear Technologies (CRITIAS), as well as the laboratory infrastructures of the SYMME.
 The first author acknowledges the financial support received from the USMB through its doctoral scholarship program.

### 2022-11-15 article_system.tex
final version

@@
 \usepackage{graphicx}
-\usepackage{siunitx}
+%\usepackage{siunitx}
 
@@
 
-\tableofcontents
+% \tableofcontents
 
@@
 The main challenge consists in optimizing the amount of energy extracted while working with soft human tissues and the earcanal restricted volume.
-This paper proposes a new harvester concept: a liquid-filled earplug which transfers energy outside the earcanal to a generator.
+This paper proposes a new energy harvester concept: a liquid-filled earplug which transfers energy outside the earcanal to a generator.
 The latter is composed of a hydraulic amplifier, two hydraulic cylinders that actuate a bistable resonator to raise the source frequency while driving an amplified piezoelectric transducer to generate electricity.
@@
 		GB                       & Guide beam                                             \\
+		EH                       & Energy harvester                                        \\
 		HA                       & Hydraulic amplifier                                     \\
@@
 		$f_0$ [Hz]				 &	BR natural resonance frequency						   \\
+		$f_d$ [-]                & Dry friction loss coefficient                           \\
 		$K$ [N/m]                & APG stiffness                                           \\
@@
 		$k_{sys}^2$ [-]          & Global electromechanical coupling coefficient           \\
-		$L$ [m]                  & Distance between 2 BR adjacent hinges                   \\
-		$l_0$ [m]                & Distance between 2 BR adjacent hinges on $\vec{x}$ axis \\
+		$L$ [m]                  & Distance between 2 BR adjacent hinges on $\vec{x}$ axis \\
+		$l_0$ [m]                & Distance between 2 BR adjacent hinges \\
 	\end{tabular}
@@
 		$\eta_{br}$ [-]          & BR energy conversion efficiency                         \\
-		$\eta_g$ [-]             & Harvester energy conversion efficiency                  \\
+		$\eta_g$ [-]             & EH energy conversion efficiency                      \\
 		$\theta$ [rad]           & HV bending angle                                        \\
@@
 		$\mu_{hc}$ [N.s/m]        & HC viscous loss coefficient                             \\
-		$f_d$ [N.s/m]             & Dry friction loss coefficient                           \\
 		$\varphi$ [rad]			 & BR hinge rotational angle							   \\
@@
 
-Delnavaz \emph{et al.} developed a flexible piezoelectric harvester made of a silicon earplug with a PVDF layer \cite{Delnavaz2013}.
+Delnavaz \emph{et al.} developed a flexible piezoelectric Energy Harvester (EH) made of a silicon earplug with a PVDF layer \cite{Delnavaz2013}.
 The earplug was molded to the subject's earcanal to maximize surface contact.
-The aim of the harvester was to exploit both the flexion and compression energies.
+The aim of the EH was to exploit both the flexion and compression energies.
 The experimental prototype was able to extract $44$\,µJ from a mastication cycle.
-The soft materials facilitated the bio-integration of the harvester, but the PVDF's low electromechanical coupling coefficient may have been the cause of poor energy conversion efficiency.
-A hydro-electromagnetic energy harvester was also developed by the same researchers \cite{Delnavaz2012}.
+The soft materials facilitated the bio-integration of the EH, but the PVDF's low electromechanical coupling coefficient may have been the cause of poor energy conversion efficiency.
+A hydro-electromagnetic energy EH was also developed by the same researchers \cite{Delnavaz2012}.
 The energy was extracted using a liquid-filled earplug whose internal volume varied as a result of the radial compression of the earcanal during jaw movements.
@@
 The next section states the hydraulic energy source characterization and harvesting strategy that was adopted.
-Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the harvester and describes its operation principle.
-Section \ref{sec:SYSTEM MODELING} details the global system modelling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the harvester.
+Section \ref{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE} presents the EH and describes its operation principle.
+Section \ref{sec:SYSTEM MODELING} details the global system modelling and section \ref{sec:NUMERICAL MODEL AND SIMULATIONS} presents the numerical simulation of the theoretical behavior of the EH.
 Then section \ref{sec:EXPERIMENTAL CHARACTERIZATIONS OF THE ELECTROMECHANICAL CONVERTER} exposes the experimental validation performed on the electromechanical converter stage and section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN} shows the experimental approach for the design of the hydraulic valves for the system cycling.
-Section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global harvester model and discusses this work's major contributions and the potential of the harvester.
+Section \ref{sec:MODEL RECALIBRATION WITH EXPERIMENTAL DATA} presents the experimentally adjusted global EH model and discusses this work's major contributions and the potential of the EH.
 This is followed by the conclusion.
@@
 In fact, the power density of electromagnetic transducers decreases proportionately to the effective volume of the transducing material and the frequency of the energy sources decreases \cite{Priya2017,Kulah2008}.
-Also, the fabrication and integration of the coil and moving magnet may be a source of difficulty as the gap between the two components must be carefully managed to prevent non-linear and unpredicted responses \cite{Caruntu2001}.
-
-Piezoelectric ceramics appear to be good candidates for small-scale mechanical energy transduction, but their rigid structure limits their use with soft materials, such as human tissue.
+Also, the fabrication and integration of the coil and moving magnet may be a source of difficulty as their gap should be carefully managed to prevent non-linear and unpredicted responses \cite{Caruntu2001}.
+
+Piezoelectric ceramics appear to be good candidates for small-scale mechanical energy transduction, but their rigid structure limits their use with soft materials, such as human tissues.
 Mechanical amplifiers, like flextensional structures, can nevertheless be used to adapt the stress/displacement levels between the energy source and the stiff transducing material \cite{Abdelnaby2016}.
@@
 However, stoppers dissipate energy.
-Alternative solutions use mechanically bistable resonators (BR) \cite{Vocca2012}.
+Alternative solutions use mechanical Bistable Resonators (BR) \cite{Vocca2012}.
 Recent works led to the development and optimization of bistable structures integrating stacked piezoelectric ceramics within flextensional elastic structures \cite{Huguet2017}.
 They show enhanced performances due to high electromechanical coupling.
-The electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure, theoretically offers a higher energy conversion efficiency than do low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
+Theoretically, the electromechanical converter, composed of a BR with piezoelectric ceramics in a flextensional structure offers a higher energy conversion efficiency than low frequency solutions and/or flexible electromechanical transducers \cite{Abdelnaby2016,Peng2021}.
 
@@
 It can store the energy in the frequency-up converter by actuating it at the frequency of human mastication.
-The amount of extractable energy from the hydraulic source will then depend on the harvester mechanical behavior.
+The amount of extractable energy from the hydraulic source will then depend on the EH mechanical behavior.
 Before being converted into electricity, the energy is in fact stored in a mechanical potential reservoir.
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-\section{HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
+\section{ENERGY HARVESTER PRESENTATION AND OPERATION \mbox{PRINCIPLE}}
 \label{sec:HARVESTER PRESENTATION AND OPERATION PRINCIPLE}
@@
 	\includegraphics[trim={3.2cm 0cm 0cm 4.3cm},clip, width=0.7\textwidth]{figures/system_presentation.pdf}
-	\caption{Schematic presentation of the frequency-up piezoelectric harvester exploiting the earcanal's geometry variation} 
+	\caption{Schematic presentation of the frequency-up piezoelectric EH exploiting the earcanal's geometry variation} 
 	\label{fig:system_presentation}
@@
 In this system, a liquid-filled earplug transmits the energy beyond the earcanal.
-To maximize its efficiency, the system has a frequency-up conversion stage that is obtained by a BR.
-The BR is connected to an amplified piezoelectric generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure that contains stacked lead zirconate titanate (PZT) ceramics (Fig.
+To maximize its efficiency, the system is equipped with a BR frequency-up conversion mechanism.
+The BR is connected to an Amplified Piezoelectric Generator (APG) \cite{CEDRATTECHNOLOGIES2022} made of a flextensional elastic APX4 steel \cite{AUBERT&DUVAL2022} structure that contains stacked lead zirconate titanate (PZT) ceramics (Fig.
 \ref{fig:APG}).
@@
 		\end{subfigure}
-		\caption{The APG presentation}
+		\caption{Amplified Piezoelectric Generator (APG)}
 		\label{fig:APG}
@@
 
-The electromechanical converter is actuated by two hydraulic cylinders (HC), the hydraulic energy being transmitted from the liquid-filled earplug trough a hydraulic amplifier (HA) and two hydraulic valves (HV).
-
+The APG is actuated by two hydraulic cylinders (HC) using the hydraulic energy transmitted from the liquid-filled earplug trough a hydraulic amplifier (HA) and two hydraulic valves (HVs).
 During a mastication cycle, the TMJ compresses the earcanal wall which expels the fluid out of the earplug.
 The HVs lead the fluid alternatively to each HC to actuate the BR mass back and forth.
-The HA adapts both the cylinders' stroke to the available earplug swept volume, and the actuation force of the BR to the comfort pressure of the earcanal (Fig.
+The HA can simultaneously adapt the cylinders' stroke to the available earplug swept volume, and the actuation force of the BR to the comfort pressure of the earcanal (Fig.
 \ref{fig:system_presentation}).
@@
 The BR mass has two equilibrium positions, \mbox{$x_m = x_0$ } and \mbox{$-x_0$}.
-The harvester operates during two major phases.
-The first is when the BR mass is actuated by a HC, from one equilibrium position toward the unstable position at $x_m = 0$.
+The EH operates during two major phases.
+The first is when the BR mass is actuated by the HC, from one equilibrium position toward the unstable position at $x_m = 0$.
 During the second phase the mass reaches and oscillates around the opposite equilibrium position until it stops, while a portion of the vibration energy is converted into electricity by the APG.
-The mass will move backward when the next mastication action occurs and this completes one harvester cycle.
+The mass will move backward when the next mastication action occurs and this completes one energy harvesting cycle.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Consequently, a pressure loss is generated through the valve in its buckled position.
-The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and opened when the mass is at $x_m=0$.
-This last point will be validated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
+The HV is to be closed when the BR mass is at a stable equilibrium position ($x_m=\pm x_0$) and to be opened when the mass is at $x_m=0$.
+This sequence of the valve opening and closing will be investigated experimentally in section \ref{sec:EXPERIMENTAL APPROACH FOR THE HV DESIGN}.
 Two HVs symmetrically placed on either side of the $\vec{z}$ axis set up an open hydraulic circuit on one side and a closed one on the other, depending on the BR mass's position.
 This technological choice for the HV is motivated by three main arguments.
-First, the absence of dedicated electromechanical transduction compared to a more commonly used actuated valve minimizes the energy losses during the valve's operation.
+First, the absence of dedicated electromechanical transduction compared to the more commonly used actuated valve minimizes the energy losses during the valve's operation.
 Second, the post-buckling softening effect of the bent tube minimizes the mechanical impact on the BR mass dynamic operation.
-Finally, it seems well adapted for applications that are on a  millimetric scale.
+Finally, it seems to be well adapted for applications on millimetric scales.
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-The harvester is a multiphysics system composed of hydraulic, mechanical, and electrical components.
+The EH is a multiphysics system composed of hydraulic, mechanical, and electrical components.
 This section presents the global multiphysics model and describes the system's theoretical basis of operation.
 Two coupled subsystems are considered.
-Subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of a HV and a HC.
+Subsection \ref{subsec:The electromechanical converter} shows the modelling of the electromechanical frequency-up converter (BR + APG) under the mechanical influence of the HV and HC.
 Subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, two HCs, HA and liquid-filled earplug.
@@
 The challenge of this work lies in the experimental validation of the electromechanical converter cycled by two HVs and two HCs.
-Several hydraulic miniature solutions have been introduced in the literature for HAs and HCs \cite{Wang2020,Xu2021,Zhu2013}.
-Hence, this section neglects the energy loss of both of the components.
-Rather, these hydraulic components will be considered in further work.
+Several hydraulic miniature solutions for HAs and HCs have already been presented in the literature \cite{Wang2020,Xu2021,Zhu2013}.
+The energy loss associated with these components has been neglected in this paper and will be considered in our further works.
     %///////////////////////////////////////////// 
@@
 The APG is considered as a spring of stiffness $K$ with an electromechanical coupling $k^2$, standing for the piezoelectric transduction and defined by Equation \ref{eq:k2_def}.\\
+\begin{equation}
+	k^2 = \dfrac{\alpha^2}{\alpha^2 +  K C_p}
+	\label{eq:k2_def}
+\end{equation}
 The model is based on the following hypotheses:
@@
 \end{itemize}
-\begin{equation}
-	k^2 = \dfrac{\alpha^2}{\alpha^2 +  K C_p}
-	\label{eq:k2_def}
-\end{equation}
+
 %%%%%%%%%%%%%%%%%
@@
 	-\alpha\dfrac{d}{dt}\biggl(2\sqrt{{l_0}^2-x_m^2}\biggr)
-	- C_p\dot{U_p}
-	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U_p}
+	- C_p\dot{U}_p
+	= \frac{2\alpha x_m\dot{x}_m}{\sqrt{L^2+x_m^2}} - C_p\dot{U}_p
 \label{eq:APG_elec}
@@
 				\ -2\alpha U_p \tan(\varphi(x_m))
-				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a} - f_d \text{sign}(\dot{x}_m)
+				\ -\dfrac{K_{HV}(x_m)\theta(x_m)}{a}\biggl(1 - f_d \text{sign}(\dot{x}_m)\biggr)
 				\  - p_{hc,a}\ S_{hc} - \mu_{c}\ \dot{x}_m
@@
     %///////////////////////////////////////////// 
-	\subsection{Setting the harvester parameters}	
+	\subsection{Setting the EH parameters}	
 	\label{subsec:The harvester setting}
@@
 	\item The hydraulic actuation is ensured by the SMC MQP4-10S HCs which can operate at $1$\,kPa pressure \cite{SMC2022}.
-	\item The usual hearing aid size is $50$x$20$x$10$\,mm \cite{Quattro2019}. The \mbox{$L=16$\,mm} parameter is chosen to be consistent with this scale.
+	\item The usual size of a hearing aid case is $50$x$20$x$10$\,mm \cite{Quattro2019}. The \mbox{$L=16$\,mm} parameter is chosen to be consistent with this scale.
 \end{itemize}
@@
 Equations \ref{eq:contrainte_course} and \ref{eq:contrainte_confort} set the amplification level $a_h$ and the BR buckling level $\epsilon$.
-Regarding the technological choices and the system operation requirements, we can evaluate $n=65\%$.
+Regarding the technological choices and the system operation requirements, we can evaluate $n=65\%$ (Eq.
+\ref{eq:Ep_bar}).
 This value can be compared to the best theoretical linear energy extraction solution described in Section \ref{eq:best_linear_soution}.
@@
 By imposing a volume variation of $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (Fig.
-\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanical and electrical coupled variables defining the harvester.
+\ref{fig:deltaV_ear}), the numerical model gives the theoretical temporal evolution of the hydraulic, mechanical and electrical coupled variables defining the EH.
 The earplug is assumed to be a perfect flow rate source.
@@
 The two different sides are identified on the curves by indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), noting that the effects of gravity are not considered.
-The same figure shows a focused view on the two main phases of the harvester operation during the actuation of the \emph{"bottom"} HC.
-The simulation begins with the following initial conditions:
+The same figure shows a focused view on the two main phases of the EH operation during the actuation of the \emph{"bottom"} HC.
+The simulation begins by the mastication cycle with the following initial conditions:
 \begin{itemize}
@@
 	\item There is no contact between the mass and the HCs.
-	\item A mastication cycle is initiating.
 \end{itemize}
@@
 Figure \ref{fig:positions_Up_puissances_energies} also presents the different positions of the moving components, the APG voltage, the source and harvested powers and the different energies entering and exciting the system.
-The theoretical global efficiency of the harvester is evaluated at \mbox{$\eta_g=85$\,\%} with 22\,µJ electrical energy harvested from one mastication.
+The theoretical global efficiency of the EH is evaluated at \mbox{$\eta_g=85$\,\%} with 22\,µJ electrical energy harvested from one mastication.
 The energy losses are mostly located in the BR stage and depend on quality factor $Q$ that has been set in accordance with previous work results on similar BR architectures \cite{Liu2013}.
 The energy source depends on comfort pressure level $p_c$ that is set to 1\,kPa, i.e., a fraction of the theoretical maximal value of $12$\,kPa \cite{Bouchard-Roy2020}.
-The harvester's theoretical efficiency could reach a maximum extractable energy of 612\,µJ.
+The EH's theoretical efficiency could reach a maximum extractable energy of 398\,µJ from one mastication cycle (Eq.
+\ref{eq:Ep_bar}).
 
@@
 The simulated model shows promising efficiency (tab.
-\ref{tab:parametres électromécaniques}) and demonstrates that a minimum value of 26 is required on the hydraulic restriction coefficient (tab.
-\ref{tab:parametres_hydrauliques}) to ensure the adequate cycled actuation of the BR mass.
-Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
+\ref{tab:parametres électromécaniques}) and  Next section will present the experimental approach to validate the theoretical behavior of the electromechanical converter.
 
@@
 The local thickenings at the midspan of the blades are intended to facilitate the fabrication.
-They also maximize the BB compression stiffness that maximizes harvester efficiency, as we will explain in the following section.
+They also maximize the BB compression stiffness that maximizes EH efficiency, as we will explain in the following section.
 The geometrical and mechanical parameters of the BR are referenced in Table \ref{tab:parametres_lames}.
@@
 			\toprule
-\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Valeur [Unit]} \\
+\textbf{Parameter definition} & \textbf{Symbol}    & \textbf{Value [Unit]} \\
 \midrule
@@
 \end{equation}
-where $\alpha_{eq}$ is the equivalent piezoelectric force factor (PFF) given by Equation \ref{eq:alpha_eq}.
+where $\alpha_{eq}$ is the equivalent Piezoelectric Force Factor (PFF) given by Equation \ref{eq:alpha_eq}.
 It depends on the APG PFF and on the ratio between the equivalent stiffness $K_{eq}$ (Eq.
@@
     %/////////////////////////////////////////////
-The experimental test bench for the electromechanical characterizations of the electromechanical converter is presented in Figure \ref{fig:BDT_OB+GPA}.
+The experimental test bench for the characterizations of the electromechanical converter is presented in Figure \ref{fig:BDT_OB+GPA}.
 An additional beam is mounted with the APG to prevent any rotation whatsoever.
@@
 The experimental data have been fitted on the oscillation phase of the simulated global model as the test bench does not reproduce the hydraulic circuit behavior yet.
-This data was used to identify and recalibrate the following electromechanical parameters of the harvester, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (Table \ref{tab:parametres_lacher_free}).
+This data was used to identify and recalibrate the following electromechanical parameters of the EH, through iterative simulations of the global \mbox{model :} $Q$, $f_0$, $K$ and $k_{sys}^2$ (Table \ref{tab:parametres_lacher_free}).
 The experimental oscillation frequency $f_0$ and energy conversion efficiency $\eta_{br}$ were also calculated.
@@
 
-The following section presents the harvester model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
+The following section presents the EH model using the hydraulic characterization data of the HV$_{T1}$ and the electromechanical experimental data of the BR with the APG.
 
@@
 %/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
-The experimentally identified parameters have been implemented in the global multiphysics coupled model to enhance its predictability and to evaluate the harvester performances.
+The experimentally identified parameters have been implemented in the global multiphysics coupled model to enhance its predictability and to evaluate the EH performances.
 The mechanical influence of the HV$_{T1}$ is identified with an experimental approach, characterizing the energy losses at the HV-mass contact point (T on Figure \ref{fig:HV_actuation_detail}).
@@
 The global model parameters listed in Table \ref{tab:parametres lacher tube} are recalibrated for both test configurations by iterative simulations.
-The simulations with the recalibrated parameters and the experimental data are superimposed on Figure \ref{fig:BDT_OB+GPA} concerning the harvesting phase of both configurations.
-
-After recalibration, the low error between the simulated and the experimental data verify that the electromechanical dynamic behavior of the harvester is theoretically predictable by the established model.
+The simulations with the recalibrated parameters and the experimental data are superimposed on Figure \ref{fig:recalage_global} concerning the harvesting phase of both configurations.
+
+After recalibration, the good match between the simulated and the experimental data verify that the electromechanical dynamic behavior of the EH is theoretically predictable by the established model.
 The HV$_{T1}$ stiffness shifts $x_0$ toward $0$ and its value at $\theta_c$ is evaluated with the shift gap and Equation \ref{eq:OB-GPA}.
@@
 	\end{tabular}
-        \caption{Experimentally recalibrated values of the harvester parameters with and without the presence of the HV$_{T1}$.}
+        \caption{Experimentally recalibrated values of the EH parameters with and without the presence of the HV$_{T1}$.}
         \label{tab:parametres lacher tube}
@@
 
-A new energy harvester architecture maximizing the energy conversion efficiency is proposed.
+A new EH architecture maximizing the energy conversion efficiency is proposed.
 A hydraulic, mechanical and electrical coupled model is established.
@@
 A new concept of HVs is proposed, based on the buckling of flexible tubes.
-A HV design is proposed with experimental investigation based on the theoretical needed behavior extracted from the numerical simulations.
-
-The experimental data was used to recalibrate the harvester multiphysics model and to evaluate its performances.
+The proposed HV design is further investigated experimentally to verify if the required theoretical behavior extracted from the numerical simulations is achieved.
+
+The experimental data was used to recalibrate the EH multiphysics model and to evaluate its performances.
 The global predicted efficiency is $\eta_g=2.6\,\%$.
